### 2019-04-20 presentation/paper.tex
add in template for paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% ML Presentation Paper 
% Jeremy Lao/John Reynolds
% JJL359, JR4716
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}

% AMS packages:
\usepackage{amsmath, amsthm, amsfonts}

%-----------------------------------------------------------------
\title{Predicting FOMC Actions using ML and NLP}
\author{
        Jeremy Lao - jjl359 \\
        NYU Computer Science \\
            \and
        John Reynolds - jr4716 \\
        NYU Computer Science \\
}

\begin{document}
\maketitle

\abstract{Add abstract text here }

\section{Introduction}
In this work we attempt to predict Federal Open Market Committee Rate actions (hold or change) using
text the Federal Reservre Meeting Minutes, speeches and statements from Federal Reserve Officials.

\subsection{Subsection}\label{sec:nothing}

To add

\subsubsection{Subsubsection}\label{sec:nothing2}

To add

% Bibliography
%-----------------------------------------------------------------
\begin{thebibliography}{99}

\bibitem{Cd94} Hansen,Stephen, McMachon, Michael  \emph{Transparency and Deliberation with the FOMC:a Computational Linquistics Approach}, CEPR Discussion Paper, (2014)

\end{thebibliography}

\end{document}

### 2019-04-20 presentation/paper.tex
paper adds

@@
 \section{Introduction}
-In this work we attempt to predict Federal Open Market Committee Rate actions (hold or change) using
-text the Federal Reservre Meeting Minutes, speeches and statements from Federal Reserve Officials.
+In this paper we methods in Natural Language Processing and Machine Learning to predict Federal Open Market 
+Committee Rate actions (hold or change) using text from Federal Reserve Meeting Minutes, speeches and statements 
+from Federal Reserve Officials.  Since this is work in sentimite analysis we created a simulator to 
+gain insight into the sensitiviy of detecting sentimite by randomly generating words with from a mix
+of distributions containing positive words, negative words and commonly used words.  That simulator
+showed accuracy could hit levels of 1.0 given enough training data and high percentage of sentimite words
+to overall text.
 

### 2019-04-20 src/model3_neuralNet.py
add fc neural net

@@ -1,0 +1,60 @@
+#
+#
+#
+from __future__ import print_function
+import sys
+import os
+import time
+import datetime
+import numpy as np
+import argparse
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.utils.data as data 
+from torch.autograd import Variable
+
+
+#
+# Neural Net1 Fully Connected
+#
+class FCNet1(nn.Module):
+
+    def __init__(self, N):
+        super(FCNet1, self).__init__()
+
+        # 2 hidden layer NN
+
+        # layer1 x->
+        self.fc1 = nn.Sequential(nn.Linear(N, N), nn.ReLU())
+
+        #layer2 
+        n2 = int(N/2)
+        
+        self.fc2 = nn.Sequential(nn.Linear(N, n2), nn.ReLU())
+
+        #output could do three to predict if raise, lower or hold
+        self.fc3 = nn.Sequential(nn.Linear(n2, 2), nn.Sigmoid())
+
+    def forward(self, X):
+        
+        xo = self.fc1(X)
+        xo = self.fc2(xo)
+        return self.fc2(xo)
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
+    parser.add_argument('--minutes', default="../text/minutes")
+    parser.add_argument('--speeches', default="../text/speeches")
+    parser.add_argument('--statements', default="../text/statements")
+    parser.add_argument('--pctTrain', default=0.75, type=float)
+    parser.add_argument('--Niter', default=10, type=int)
+    parser.add_argument('--cleanAlgo', default="complex")
+    parser.add_argument('--ngram', nargs='+', default=['1,1'])
+    args = parser.parse_args()
+
+    net = FCNet1(100)
+    
+

### 2019-04-21 presentation/paper.tex
paper
adding beamer

--- 2019-04-20 presentation/paper.tex
@@
 \usepackage{amsmath, amsthm, amsfonts}
+
+% Document Formatting Packages:
+\usepackage{hyperref}
 
@@
 
-\abstract{Add abstract text here }
+\abstract{abstract text }
 
 \section{Introduction}
-In this work we attempt to predict Federal Open Market Committee Rate actions (hold or change) using
-text the Federal Reservre Meeting Minutes, speeches and statements from Federal Reserve Officials.
+In this paper we methods in Natural Language Processing and Machine Learning to predict Federal Open Market Committee (FOMC) rate actions (hold or change) using text from FOMC meeting minutes, Board of Governors speeches, and FOMC post-meeting statements.
+Since this is work in sentiment analysis we created a simulator to gain insight into the sensitiviy of detecting sentiment by randomly generating words with from a mix of distributions containing hawkish or dovish(positive) words, negative words, and commonly used words.
+That simulator showed accuracy could hit levels of 100 percent given enough training data and high percentage of sentiment (i.e., positive)  words to overall text.
 
@@
 To add
+
+\section{Methodology}
+
+\subsection{Data}
+
+The time frame of our study covered 2000 to 2019.
+The primary source of our textual data were FOMC statements, FOMC meeting minutes, and Board of Governors speeches from \url{www.federalreserve.gov}.
+For FOMC statements between 2000 and 2008 we utilized Stanford's FOMC corpus.
+The Stanford FOMC corpus only has text prior to 2008 and it does not have Board of Governor speeches.
+\vspace{5mm}
+
+The data for the Federal Funds target rate and target range (post 2009) is from FRED St.
+Louis.
+FRED offers a wealth of economic data and information to promote economic education and enhance economic research.
+FRED is updated regularly and allows 24/7 access to regional and national financial and economic data.
+\vspace{5mm}
 

### 2019-04-21 presentation/presentation.tex
adding beamer

%% LaTeX Beamer presentation template (requires beamer package)
%% see http://bitbucket.org/rivanvx/beamer/wiki/Home
%% idea contributed by H. Turgut Uyar
%% template based on a template by Till Tantau
%% this template is still evolving - it might differ in future releases!

\documentclass{beamer}

\mode<presentation>
{
\usetheme{NYU}

\setbeamercovered{transparent}
}

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}

% font definitions, try \usepackage{ae} instead of the following
% three lines if you don't like this look
\usepackage{mathptmx}
\usepackage[scaled=.90]{helvet}
\usepackage{courier}

\usepackage[T1]{fontenc}

\usepackage{comment}
%usepackage{appendixnumberbeamer}
%\usepackage{amsmath}
\usepackage{pgfpages}
% citations
\usepackage{natbib}
\bibpunct{(}{)}{;}{a}{,}{,}
\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}
\renewcommand{\bibsection}{\subsubsection*{\bibname } }

\title{Modelling Federal Open Market Committee Decisions Using ML and NLP}

%\subtitle{}

% - Use the \inst{?} command only if the authors have different
%   affiliation.
%\author{F.~Author\inst{1} \and S.~Another\inst{2}}
\author{Jeremy Lao \& John Reynolds}

% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.
\institute[NYU]
{
Department of Computer Science\\
Courant Institute of Mathematical Sciences, NYU\\
  \texttt{}
}

\date{Date}

% This is only inserted into the PDF information catalog. Can be left
% out.
\subject{Subject}

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

\pgfdeclareimage[height=0.5cm]{university-logo}{nyu_long_color}
\logo{\pgfuseimage{university-logo}}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}

\frametitle{Introduction}
test intro
\end{frame}

\begin{frame}

\frametitle{Introduction}
test 2

\end{frame}

\begin{frame}
\frametitle{Data}
TEST
\end{frame}

\begin{frame}
\frametitle{Summary}

\begin{itemize}
  \item The \alert{first main message} of your talk in one or two lines.
\end{itemize}
\end{frame}

\end{document}

### 2019-04-21 presentation/paper.tex
updates to paper

@@
 
-\documentclass{article}
+\documentclass[11pt]{article}
 
@@
 \usepackage{hyperref}
-
+\usepackage[margin=1in]{geometry}
 %-----------------------------------------------------------------
@@
 
-\abstract{abstract text }
+\abstract{\textit{The Federal Open Market Committee (FOMC) meets throughout the year to set the target Federal Funds rate.
+The Federal Funds rate is one of the primary monetary policy tools, and it impacts the cost of borrowing money globally.
+This paper explores ML and NLP methods to predict the potential outcome of an upcoming FOMC using past FOMC statements and meeting minutes to train ML and NLP models.}}
 
@@
 
-\subsection{Subsection}\label{sec:nothing}
+\subsection{What is the FOMC}
 
-To add
+The FOMC sets the Federal Funds target range (target rate prior to 2009).
+The permanent members are the Board of Governors of the Federal Reserve System, President of the Federal Reserve Bank of New York, and the rest of the seats are rotated through the Presidents of the other Federal Reserve Banks.
+There are twelve Reserve Banks and the Board of Governors oversees the activity, operations, and policies of the Federal Reserve System.
 
-\subsubsection{Subsubsection}\label{sec:nothing2}
+\subsection{Why Does the Federal Funds Target Range Matter?}
 
-To add
+The Federal Funds Target Range is set by the FOMC.
+The Federal Funds Target Range is the range where the Federal Funds Effective rate (calculated as the volumn weighted median of eligible transactions reported on FR 2420) is exepected to fix on a daily basis.
+The Federal Funds rate is the primary monetary policy instrument of the Federal Reserve System, and it influces the level of interest rates domestically and globally.
+For example, if the Federal Funds effective rate were 5 percent, then the interest rate on a 30 year mortgage would be 5 percent or greater.
 
@@
 \subsection{Data}
+
+We primarily utilized three sources for our data, they are outlined below. \vspace{5mm}
 
@@
 
+\subsection{Scraping and Text Pre-Processing}
+
+We collected data from the Federal Reserve website and pre-processed the data for the document-term matrix. \vspace{5mm}
+
+We utilized Python packages \textit{beautifulsoup4}, \textit{re}, and \textit{urllib} to scrape contextual data from the Federal Reserve website.
+Our scraping algorithm used regular expressions to handle and remove extraneous \textit{html} and \textit{javascript} text collected by the page scraper.
+We had to handle non UTF-8 characters upfront and remove them at this stage altogether.
+We collected nearly one-thousand documents from the Federal Reserve website.
+\vspace{5mm}
+
+After scraping the data, we pre-processed the text by removing all punctuation, ensuring proper spacing between words, setting all words to lower case, and making all numbers \textit{d} to reduce the dimensionality document-term matrix.
+We also used Regex to detect direct references to the Federal Funds target rate/range and transformed those references (a mixture of numbers, punctuation, and the word 'percent') to \textit{ddpercentrate}.
+Since we were modeling the sentiment of FOMC rate action, this was one of our strategies to directly capture the target rate in the document-term matrix.
+\vspace{5mm}
+
+This formed the bulk of our text pre-processing and it allowed us to essentially utilize the stored text in the document-term matrix for NLP and ML models.
+
 % Bibliography

### 2019-04-22 src/modelutils.py
modelutils

@@ -1,0 +1,37 @@
+import pandas as pd
+
+"""
+put repeated stuff here that is used in building the models
+"""
+
+class modelutils:
+
+    
+    def decisionDF(decisionFile):
+        names = ["minutes_date",
+                 "publish_date",
+                 "before",
+                 "after",
+                 "decision",
+                 "flag",
+                 "change"]
+        usecols = [0,1,2,3,4,5,6]
+        dtypes={"minutes_date":'str',
+                "publish_date":'str',
+                "before":'float',
+                "after":'float',
+                "decision":'str',
+                "flag":'float',
+                "change":'float'}
+        df = pd.read_csv(decisionFile, 
+                         usecols=usecols,
+                         header=None, 
+                         names=names,
+                         dtype=dtypes,
+                         sep=",")
+        # done outside of df construction as dateimte conversion can be extremely 
+        # slow without a format hint as data size grows
+        df['minutes_date'] = pd.to_datetime(df['minutes_date'],format="%Y%m%d")
+        df['publish_date'] = pd.to_datetime(df['publish_date'],format="%Y%m%d")
+    return df
+

### 2019-04-22 src/modelutils.py
fix

@@ -33,5 +33,5 @@ class modelutils:
         # slow without a format hint as data size grows
         df['minutes_date'] = pd.to_datetime(df['minutes_date'],format="%Y%m%d")
         df['publish_date'] = pd.to_datetime(df['publish_date'],format="%Y%m%d")
-    return df
+        return df
 

### 2019-04-22 src/modelutils.py
add staements,minutes modelutiles

@@ -1,4 +1,6 @@
 import pandas as pd
+import os
+import datetime
 
 """
 put repeated stuff here that is used in building the models
@@ -34,4 +36,39 @@ class modelutils:
         df['minutes_date'] = pd.to_datetime(df['minutes_date'],format="%Y%m%d")
         df['publish_date'] = pd.to_datetime(df['publish_date'],format="%Y%m%d")
         return df
+
+
+    def getMinutes(minutesDir, df, clean_algo, abortOnFail=False):
+        minutes, publish , data = [], [], []
+        for files in sorted(os.listdir(minutesDir)):
+            f, ext = os.path.splitext(files)
+            minutes.append(datetime.datetime.strptime(f.split("_")[0],"%Y%m%d"))
+            publish.append(datetime.datetime.strptime(f.split("_")[-1],"%Y%m%d"))
+            try:
+                text = clean_algo(open(os.path.join(minutesDir, files)).read().strip())
+                dec = df[df["publish_date"] == publish[-1]].iloc[0]["flag"]
+                data.append([text, dec])
+            except Exception as e:
+                print("exception reading minutes, file %s" % files)
+                print(e)
+                if abortOnFail:
+                    quit()
+            return data, publish
+
+
+    def getStatements(statementsDir, df, clean_algo, abortOnFail=False):
+        statements, data = [], []
+        for files in sorted(os.listdir(statementsDir)):
+            f, ext = os.path.splitext(files)
+            statements.append(datetime.datetime.strptime(f.split(".")[0],'%Y%m%d'))
+            try:
+                text = clean_algo(open(os.path.join(statementsDir,files),encoding='utf-8',errors='ignore').read().strip())
+                dec = df[df["publish_date"] == statements[-1]].iloc[0]["flag"]
+                data.append([text,dec])
+            except Exception as e:
+                print("exception reading statements, file %s" % files)
+                print(e)
+                if abortOnFail:
+                    quit()
+        return data
 

### 2019-04-22 src/model3_neuralNet.py
added modelutils to model3

@@ -13,7 +13,12 @@ import torch.nn as nn
 import torch.nn.functional as F
 import torch.utils.data as data 
 from torch.autograd import Variable
+from clean import simple_clean
+from clean import complex_clean
+from modelutils import modelutils
 
+# to install pytorch
+# conda install pytorch torchvision -c soumith
 
 #
 # Neural Net1 Fully Connected
@@ -37,7 +42,6 @@ class FCNet1(nn.Module):
         self.fc3 = nn.Sequential(nn.Linear(n2, 2), nn.Sigmoid())
 
     def forward(self, X):
-        
         xo = self.fc1(X)
         xo = self.fc2(xo)
         return self.fc2(xo)
@@ -55,6 +59,13 @@ if __name__ == '__main__':
     parser.add_argument('--ngram', nargs='+', default=['1,1'])
     args = parser.parse_args()
 
-    net = FCNet1(100)
     
+    clean_algo = complex_clean if args.cleanAlgo == "complex" else simple_clean
+    df = modelutils.decisionDF(args.decision)
+    data, publish = modelutils.getMinutes(args.minutes, df, clean_algo)
+    #data_statements = modelutils.getStatements(args.statements, df, clean_algo)
+
+    net = FCNet1(100)
+
+
 

### 2019-04-23 src/documentMetadata.py
adding metadata calculator

@@ -1,0 +1,77 @@
+import os
+import glob
+import os
+import sys
+import argparse
+import numpy as np
+import pandas as pd
+import datetime
+import datetime as dt
+import bisect
+import re
+import csv
+import statistics
+
+def minutesWordCount(minutesDir):
+  totalWords, totalDoc = 0, 0
+  words = 0
+  docVec = []
+  for files in sorted(os.listdir(minutesDir)):
+    with open(minutesDir+'/'+files, 'r') as f:
+      totalDoc += 1
+      for line in f:
+        line = line.split()
+        totalWords += len(line)
+        words += len(line)
+      docVec.append(words)
+      words = 0
+  return totalWords, totalDoc, docVec
+
+def statementsWordCount(direc):
+  totalWords, totalDoc = 0, 0
+  words = 0
+  docVec = []
+  for files in sorted(os.listdir(direc)):
+    with open(direc+'/'+files, 'r',encoding='utf-8',errors='ignore') as f:
+      totalDoc += 1
+      for line in f:
+        line = line.split()
+        totalWords += len(line)
+        words += len(line)
+      docVec.append(words)
+      words = 0
+  return totalWords, totalDoc, docVec
+
+def speechesWordCount(direc):
+  totalWords, totalDoc = 0, 0
+  words = 0
+  docVec = []
+  for files in sorted(os.listdir(direc)):
+    with open(direc+'/'+files, 'r',encoding='utf-8',errors='ignore') as f:
+      totalDoc += 1
+      for line in f:
+        line = line.split()
+        totalWords += len(line)
+        words += len(line)
+      docVec.append(words)
+      words = 0
+  return totalWords, totalDoc, docVec
+
+def printMetaData(docType,numWords,numDocs,wordVec):
+  print('Total Words in '+docType+ ': '+str(numWords) + '\nTotal Docs: '+str(numDocs) + '\nAvg Words Per Doc: ' + str(numWords/numDocs) + '\nStDev: ' + str(statistics.stdev(wordVec, numWords/numDocs))+ '\n')
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser.add_argument('--minutes', default="../text/minutes")
+    parser.add_argument('--speeches', default="../text/speeches")
+    parser.add_argument('--statements', default="../text/statements")
+    args = parser.parse_args()
+    
[…]

### 2019-04-23 src/model2_1-speeches.py

@@ -129,6 +129,7 @@ if __name__ == '__main__':
     parser.add_argument('--Niter', default=10, type=int)
     parser.add_argument('--cleanAlgo', default="complex")
     parser.add_argument('--ngram', nargs='+', default=['2,2'])
+    parser.add_argument('--SpeechYear', default=2018, type=int)
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -138,7 +139,7 @@ if __name__ == '__main__':
     df = decisionDF(args.decision)
     data, publish = getMinutes(args.minutes, df, clean_algo)
     data_statements = getStatements(args.statements, df, clean_algo)
-    data_speeches = getSpeeches(2018)
+    data_speeches = getSpeeches(args.SpeechYear)
     N = len(data)
     # Train on current minutes
     models=[("svm",LinearSVC()),
@@ -148,7 +149,7 @@ if __name__ == '__main__':
 
     print("Determining Fed Action from minutes")
     print("%-20s %5s %5s %10s %10s %5s %8s %6s %10s %10s" % ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end"))
-    N = N + int(len(data_statements))
+    N = N + int(len(data_statements)) + int(len(data_speeches))
     for ngram in ngrams:
         results= runModels(models, data, data_statements, data_speeches, Niter, pctTrain, ngram)
         #pctTrain = (int(len(data)*0.75) + int(len(data_statements))) / (int(len(data)) + int(len(data_statements)))

### 2019-04-23 presentation/paper.tex
update

@@
 \usepackage[margin=1in]{geometry}
+
+\newcommand{\vertSpace}[1]{\vspace{3mm}}
+
 %-----------------------------------------------------------------
@@
 \section{Introduction}
-In this paper we methods in Natural Language Processing and Machine Learning to predict Federal Open Market Committee (FOMC) rate actions (hold or change) using text from FOMC meeting minutes, Board of Governors speeches, and FOMC post-meeting statements.
+In this paper we methods in Natural Language Processing (NLP) and Machine Learning (ML) to predict Federal Open Market Committee (FOMC) rate actions (hold or change) using text from FOMC meeting minutes, Board of Governors speeches, and FOMC post-meeting statements.
 Since this is work in sentiment analysis we created a simulator to gain insight into the sensitiviy of detecting sentiment by randomly generating words with from a mix of distributions containing hawkish or dovish(positive) words, negative words, and commonly used words.
@@
 
+\section{Objective}
+
+The aim of our research is to determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate).  Our models approached this question in two steps:
+
+\begin{enumerate}
+
+ \item We test the accuracy of ML models trained on FOMC statements and a percentage of FOMC minutes on a test set of FOMC minutes
+ \item We create a predictive model that is trained on documents that are temporally released before the test document.
+Typically we will test with FOMC minutes releases or Board of Governor speeches.
+\end{enumerate}
+
 \section{Methodology}
@@
 
-We primarily utilized three sources for our data, they are outlined below. \vspace{5mm}
+We primarily utilized three sources for our data, they are outlined below. \vertSpace
 
-The time frame of our study covered 2000 to 2019.
+The time frame of our study covered 2000 to 2018.
 The primary source of our textual data were FOMC statements, FOMC meeting minutes, and Board of Governors speeches from \url{www.federalreserve.gov}.
@@
 The Stanford FOMC corpus only has text prior to 2008 and it does not have Board of Governor speeches.
-\vspace{5mm}
+\vertSpace
 
@@
 
+\noindent Below is a table of the FOMC document metadata:
+
+\vertSpace
+
+\noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
+ \hline
+ \multicolumn{6}{|c|}{FOMC Documents} \\
+ \hline
+ Document Type& Years & Num Documents & Total Words & Avg Words Per Document & StDev\\
+ \hline
+ Minutes   & 2000-2018    & 149 & 738,656 & 4,957 & 1,284\\
+ Statements &   2000-2018  & 160   & 62,350 & 389 & 185\\
+ Speeches & 2011-2018 & 403 & 915,359 & 2,271 & 1,539\\
+ \hline
+\end{tabular}
+
+\vertSpace
+
+Statements are post-meeting communiqu\'e and are generally short, but contains a summary of the committee's reasoning for the decision.
+Minutes are longer and contain the Staff and Committee member current economic assessments and outlooks.
+The speeches in the corpus are from the Board of Governors and may contain clues of their thoughts on their current economic outlook.
+\vertSpace
+
+When we train the model with statements and minutes, ten statements will be considered one document because of the magnitude of minute size to statement size.
+
 \subsection{Scraping and Text Pre-Processing}
 
-We collected data from the Federal Reserve website and pre-processed the data for the document-term matrix. \vspace{5mm}
+We collected data from the Federal Reserve website and pre-processed the data for the document-term matrix. \vertSpace
 
@@
 We had to handle non UTF-8 characters upfront and remove them at this stage altogether.
-We collected nearly one-thousand documents from the Federal Reserve website.
-\vspace{5mm}
+We collected over six hundred documents from the Federal Reserve website.
+\vertSpace
 
@@
 Since we were modeling the sentiment of FOMC rate action, this was one of our strategies to directly capture the target rate in the document-term matrix.
-\vspace{5mm}
+\vertSpace
 
 This formed the bulk of our text pre-processing and it allowed us to essentially utilize the stored text in the document-term matrix for NLP and ML models.
+
+\subsection{Models}
+
+We will provide an overview of how we utilized the following models in our research
 

### 2019-04-23 src/modelutils.py
added more into modelutils.py

@@ -1,6 +1,11 @@
 import pandas as pd
 import os
 import datetime
+import numpy as np
+import bisect
+from sklearn.feature_extraction.text import CountVectorizer
+from sklearn.feature_extraction.text import TfidfVectorizer
+
 
 """
 put repeated stuff here that is used in building the models
@@ -39,36 +44,83 @@ class modelutils:
 
 
     def getMinutes(minutesDir, df, clean_algo, abortOnFail=False):
-        minutes, publish , data = [], [], []
+        publish , data = [], []
         for files in sorted(os.listdir(minutesDir)):
             f, ext = os.path.splitext(files)
-            minutes.append(datetime.datetime.strptime(f.split("_")[0],"%Y%m%d"))
-            publish.append(datetime.datetime.strptime(f.split("_")[-1],"%Y%m%d"))
             try:
+                # commented out for now as its not used 
+                #minutes_date = datetime.datetime.strptime(f.split("_")[0],"%Y%m%d")
+                publish_date = datetime.datetime.strptime(f.split("_")[-1],"%Y%m%d")
                 text = clean_algo(open(os.path.join(minutesDir, files)).read().strip())
-                dec = df[df["publish_date"] == publish[-1]].iloc[0]["flag"]
+                dec = df[df["publish_date"] == publish_date].iloc[0]["flag"]
                 data.append([text, dec])
+                publish.append(publish_date)
             except Exception as e:
                 print("exception reading minutes, file %s" % files)
                 print(e)
                 if abortOnFail:
                     quit()
-            return data, publish
+        return data, publish
 
 
-    def getStatements(statementsDir, df, clean_algo, abortOnFail=False):
-        statements, data = [], []
+    def getStatements(statementsDir, df, clean_algo, abortOnFail=False, debug=False):
+        cleanedStatementV, dateV = [], df["publish_date"].values
         for files in sorted(os.listdir(statementsDir)):
             f, ext = os.path.splitext(files)
-            statements.append(datetime.datetime.strptime(f.split(".")[0],'%Y%m%d'))
             try:
+                statement_date = datetime.datetime.strptime(f.split(".")[0],'%Y%m%d') 
+                dt64 = modelutils.to_np64(statement_date)
+                ix = modelutils.get_ge(dateV, dt64)
+                decision = df.loc[ix]["flag"]
+                if debug :
+                    print("getStatements debug", df.loc[ix]["publish_date"], ix, statement_date, decision)
[…]

### 2019-04-23 src/model2_0.py
fix bugs in model2_0 one in getStatements one in getTrainTest

@@ -16,6 +16,7 @@ from sklearn.linear_model import LogisticRegression
 from sklearn.naive_bayes import MultinomialNB
 import matplotlib.pyplot as plt
 import csv
+from modelutils import modelutils
 
 # this version allows for multiple fit methods (SVM, Logistic, Logistic Lasso)
 # this method also computes the mean and std deviation of the accuracy by
@@ -25,72 +26,16 @@ import csv
 
 # python ./model2_0.py --ngram 1,1 2,2 3,3 1,3 2,3 --Niter 50 --pctTrain .8
 
-def decisionDF(decisionFile):
-    names = ["minutes_date","publish_date","before","after","decision","flag","change"]
-    usecols = [0,1,2,3,4,5,6]
-    dtypes={"minutes_date":'str',"publish_date":'str',"before":'float',"after":'float',
-            "decision":'str',"flag":'float',"change":'float'}
-    df = pd.read_csv(decisionFile, 
-                     usecols=usecols,
-                     header=None, 
-                     names=names,
-                     dtype=dtypes,
-                     sep=",")
-    df['minutes_date'] = pd.to_datetime(df['minutes_date'],format="%Y%m%d")
-    df['publish_date'] = pd.to_datetime(df['publish_date'],format="%Y%m%d")
-    return df
 
-def getMinutes(minutesDir, decisionDF, clean_algo):
-    minutes, publish , data = [], [], []
-    for files in sorted(os.listdir(minutesDir)):
-        f, ext = os.path.splitext(files)
-        minutes.append(datetime.datetime.strptime(f.split("_")[0],"%Y%m%d"))
-        publish.append(datetime.datetime.strptime(f.split("_")[-1],"%Y%m%d"))
-        try:
-            text = clean_algo(open(os.path.join(minutesDir, files)).read().strip())
-            dec = df[df["publish_date"] == publish[-1]].iloc[0]["flag"]
-            data.append([text, dec])
-        except Exception as e:
-            print("exception reading file %s" % files)
-            print(e)
-            quit()
-    return data, publish
+def runModels(models, model_data_set, Nitr, pctTrain, ngram):
+    def pctPos(tdata):
+        tl, tpos = len(tdata), tdata['sentiment'].sum()
+        print(tl, tpos, tpos/tl)
 
-def getStatements(statementsDir, decisionDF, clean_algo):
-    statements, data = [], []
-    for files in sorted(os.listdir(statementsDir)):
-      f, ext = os.path.splitext(files)
[…]

### 2019-04-23 src/modelutils.py
modelutils parsing returns pandas df now

@@ -15,21 +15,21 @@ class modelutils:
 
     
     def decisionDF(decisionFile):
-        names = ["minutes_date",
-                 "publish_date",
-                 "before",
-                 "after",
-                 "decision",
-                 "flag",
-                 "change"]
+        names = ["MeetingDate",
+                 "MinutesRelease",
+                 "PreviousTarget",
+                 "PostTarget",
+                 "Direction",
+                 "ActionFlag",
+                 "Amount"]
         usecols = [0,1,2,3,4,5,6]
-        dtypes={"minutes_date":'str',
-                "publish_date":'str',
-                "before":'float',
-                "after":'float',
-                "decision":'str',
-                "flag":'float',
-                "change":'float'}
+        dtypes={"MeetingDate":'str',
+                "MinutesRelease":'str',
+                "PreviousTarget":'float',
+                "PostTarget":'float',
+                "Direction":'str',
+                "ActionFlag":'float',
+                "Amount":'float'}
         df = pd.read_csv(decisionFile, 
                          usecols=usecols,
                          header=None, 
@@ -38,56 +38,94 @@ class modelutils:
                          sep=",")
         # done outside of df construction as dateimte conversion can be extremely 
         # slow without a format hint as data size grows
-        df['minutes_date'] = pd.to_datetime(df['minutes_date'],format="%Y%m%d")
-        df['publish_date'] = pd.to_datetime(df['publish_date'],format="%Y%m%d")
+        df['MeetingDate'] = pd.to_datetime(df['MeetingDate'],format="%Y%m%d")
+        df['MinutesRelease'] = pd.to_datetime(df['MinutesRelease'],format="%Y%m%d")
         return df
 
-
+    """
+    return FedMinutes as pandas DataFrame
+    """
     def getMinutes(minutesDir, df, clean_algo, abortOnFail=False):
-        publish , data = [], []
+        data={"meetingDate":[], "year":[], "doctext":[], "actionFlag":[], "rateChange":[], "documentType":[]}
         for files in sorted(os.listdir(minutesDir)):
             f, ext = os.path.splitext(files)
             try:
                 # commented out for now as its not used 
                 #minutes_date = datetime.datetime.strptime(f.split("_")[0],"%Y%m%d")
-                publish_date = datetime.datetime.strptime(f.split("_")[-1],"%Y%m%d")
+                release_date = datetime.datetime.strptime(f.split("_")[-1],"%Y%m%d")
                 text = clean_algo(open(os.path.join(minutesDir, files)).read().strip())
[…]

### 2019-04-23 src/test_modelutils.py
added test_modelutils

@@ -1,0 +1,33 @@
+from modelutils import modelutils
+from clean import simple_clean
+from clean import complex_clean
+import argparse
+
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
+    parser.add_argument('--minutes', default="../text/minutes")
+    parser.add_argument('--speeches', default="../text/speeches")
+    parser.add_argument('--statements', default="../text/statements")
+    parser.add_argument('--pctTrain', default=0.75, type=float)
+    parser.add_argument('--Niter', default=10, type=int)
+    parser.add_argument('--cleanAlgo', default="complex")
+    parser.add_argument('--ngram', nargs='+', default=['1,1'])
+    args = parser.parse_args()
+
+    df = modelutils.decisionDF(args.decision)
+    mn = modelutils.getMinutes(args.minutes, df, complex_clean)
+    st = modelutils.getStatements(args.statements, df, complex_clean)
+    sp = modelutils.getSpeeches(args.speeches, df, complex_clean)
+    
+    print("--RatesDecision")
+    print(df)
+    print("---Minutes")
+    print(mn)
+    print("---Statements")
+    print(st)
+    print("---Speeches")
+    print(sp)
+

### 2019-04-23 src/modelutils.py
new trainTestSplit in modelutils

@@ -5,6 +5,7 @@ import numpy as np
 import bisect
 from sklearn.feature_extraction.text import CountVectorizer
 from sklearn.feature_extraction.text import TfidfVectorizer
+from sklearn.model_selection import train_test_split
 
 
 """
@@ -138,23 +139,9 @@ class modelutils:
     def to_days(x):
         return x.astype('timedelta64[D]')/np.timedelta64(1, 'D')
 
-
     def splitTrainTest(data_sets, train_pct):
-        def isMultipleDataSets(data_sets):
-            for d in data_sets:
-                # first line is 2 elements and has decision variable
-                if len(d) == 2 and d[1] < 3: return False
-                return True
-        combined = data_sets
-        if isMultipleDataSets(data_sets):
-            combined = data_sets[0]
-            for i in range(1,len(data_sets)):
-                combined.extend(data_sets[i])
-        Ntrain = int(len(combined)* train_pct)
-        np.random.shuffle(combined)
-        train_data = pd.DataFrame(combined[0:Ntrain],columns=['text', 'sentiment'])
-        test_data = pd.DataFrame(combined[Ntrain:], columns=['text', 'sentiment'])
-        return train_data, test_data
+        combined = pd.concat(data_sets) if type(data_sets) is list else data_sets
+        return train_test_split(combined, test_size=1.0-train_pct)
 
     def getFeatures(train_data, test_data, ngram):
         vectorizer = CountVectorizer(stop_words="english",preprocessor=None, ngram_range=ngram)

### 2019-04-23 src/model2_0.py
model fixes

@@ -24,7 +24,7 @@ from modelutils import modelutils
 # allows the text preprocessing algorithm to be selected
 # running each model Niter Times
 
-# python ./model2_0.py --ngram 1,1 2,2 3,3 1,3 2,3 --Niter 50 --pctTrain .8
+# python ./model2_0.py --ngram 1,1 2,2 3,3 1,3 2,3 --Niter 3 --pctTrain .8 --data minutes speeches statements
 
 
 def runModels(models, model_data_set, Nitr, pctTrain, ngram):
@@ -38,9 +38,9 @@ def runModels(models, model_data_set, Nitr, pctTrain, ngram):
         training_features, test_features = modelutils.getFeatures(train_data, test_data, ngram)
         for i, m in enumerate(models):
             model=m[1]
-            model.fit(training_features, train_data["sentiment"])
+            model.fit(training_features, train_data["actionFlag"])
             y_pred = model.predict(test_features)
-            acc = accuracy_score(test_data["sentiment"], y_pred)
+            acc = accuracy_score(test_data["actionFlag"], y_pred)
             if iter == 0:
                 results.append(np.zeros(Nitr))
             results[i][iter]=acc
@@ -54,37 +54,59 @@ if __name__ == '__main__':
     parser.add_argument('--speeches', default="../text/speeches")
     parser.add_argument('--statements', default="../text/statements")
     parser.add_argument('--pctTrain', default=0.75, type=float)
-    parser.add_argument('--Niter', default=10, type=int)
+    parser.add_argument('--Niter', help="number of times to refit data", default=10, type=int)
     parser.add_argument('--cleanAlgo', default="complex")
     parser.add_argument('--ngram', nargs='+', default=['1,1'])
+    parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=25000, type=int)
+    parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
+    parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
-
     clean_algo = complex_clean if args.cleanAlgo == "complex" else simple_clean
[…]

### 2019-04-23 src/modelutils.py

@@ -145,7 +145,9 @@ class modelutils:
 
     def getFeatures(train_data, test_data, ngram):
         vectorizer = CountVectorizer(stop_words="english",preprocessor=None, ngram_range=ngram)
-        training_features = vectorizer.fit_transform(train_data["text"])                                 
-        test_features = vectorizer.transform(test_data["text"])
+        training_features = vectorizer.fit_transform(train_data["doctext"])                                 
+        test_features = vectorizer.transform(test_data["doctext"])
         return training_features, test_features
 
+    def getBounds(datadf):
+        return (len(datadf), modelutils.to_dt(datadf["meetingDate"].min()), modelutils.to_dt(datadf["meetingDate"].max()))

### 2019-04-23 src/test_modelutils.py

@@ -21,13 +21,20 @@ if __name__ == '__main__':
     mn = modelutils.getMinutes(args.minutes, df, complex_clean)
     st = modelutils.getStatements(args.statements, df, complex_clean)
     sp = modelutils.getSpeeches(args.speeches, df, complex_clean)
-    
-    print("--RatesDecision")
-    print(df)
-    print("---Minutes")
-    print(mn)
-    print("---Statements")
-    print(st)
-    print("---Speeches")
-    print(sp)
 
+    if False:
+        print("--RatesDecision")
+        print(df)
+        print("---Minutes")
+        print(mn)
+        print("---Statements")
+        print(st)
+        print("---Speeches")
+        print(sp)
+
+    train, test = modelutils.splitTrainTest([mn, st, sp], 0.75)
+    print("train_size=%d, test_size=%d, total_size=%d" % (len(train), len(test), len(train) + len(test)))
+    print("randmoly split training set")
+    print(train)
+    print("randmoly split test set")
+    print(test)

### 2019-04-23 src/model3_neuralNet.py
update model3

@@ -54,17 +54,43 @@ if __name__ == '__main__':
     parser.add_argument('--speeches', default="../text/speeches")
     parser.add_argument('--statements', default="../text/statements")
     parser.add_argument('--pctTrain', default=0.75, type=float)
-    parser.add_argument('--Niter', default=10, type=int)
+    parser.add_argument('--Niter', help="number of times to refit data", default=10, type=int)
     parser.add_argument('--cleanAlgo', default="complex")
     parser.add_argument('--ngram', nargs='+', default=['1,1'])
+    parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=25000, type=int)
+    parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
+    parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     args = parser.parse_args()
 
-    
+    ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
     clean_algo = complex_clean if args.cleanAlgo == "complex" else simple_clean
-    df = modelutils.decisionDF(args.decision)
-    data, publish = modelutils.getMinutes(args.minutes, df, clean_algo)
-    #data_statements = modelutils.getStatements(args.statements, df, clean_algo)
+    pctTrain, cleanA, Niter, ngram = args.pctTrain, args.cleanAlgo, args.Niter, args.ngram
+    solver, max_iter, datasetlist = args.solver, args.max_iter, args.data
 
+    assert len(datasetlist) > 0, "no data sets specified"
+    datasetlabel=":".join(d for d in datasetlist)
+
+    # fed rate decison matrix
+    df = modelutils.decisionDF(args.decision)
+
+    # datsets
+    data_set, N, start, end = [], 0, datetime.datetime.now(), datetime.datetime(1970, 1, 1)
+    if "minutes" in datasetlist:
+        data_set.append(modelutils.getMinutes(args.minutes, df, clean_algo))
+        (N, start, end) = modelutils.getBounds(data_set[-1])
+    if "speeches" in datasetlist:
+        data_set.append(modelutils.getSpeeches(args.speeches, df, clean_algo))
+        (N1, start1, end1) = modelutils.getBounds(data_set[-1])
+        N , start, end = N + N1, min(start, start1), max(end, end1)
+    if "statements" in datasetlist:
[…]

### 2019-04-23 src/model2_0.py
update dataframe to include MinutesReleaseDate

@@ -28,19 +28,15 @@ from modelutils import modelutils
 
 
 def runModels(models, model_data_set, Nitr, pctTrain, ngram):
-    def pctPos(tdata):
-        tl, tpos = len(tdata), tdata['sentiment'].sum()
-        print(tl, tpos, tpos/tl)
-
     results=[]
     for iter in range(Nitr):
         train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
         training_features, test_features = modelutils.getFeatures(train_data, test_data, ngram)
         for i, m in enumerate(models):
             model=m[1]
-            model.fit(training_features, train_data["actionFlag"])
+            model.fit(training_features, train_data["ActionFlag"])
             y_pred = model.predict(test_features)
-            acc = accuracy_score(test_data["actionFlag"], y_pred)
+            acc = accuracy_score(test_data["ActionFlag"], y_pred)
             if iter == 0:
                 results.append(np.zeros(Nitr))
             results[i][iter]=acc

### 2019-04-23 src/modelutils.py

@@ -43,11 +43,20 @@ class modelutils:
         df['MinutesRelease'] = pd.to_datetime(df['MinutesRelease'],format="%Y%m%d")
         return df
 
+    def updateData(data, minutesReleaseDate, docDate, docText, action, amount, docType):
+        data["MinutesRelease"].append(minutesReleaseDate)
+        data["DocDate"].append(docDate)
+        data["Year"].append(docDate.year)
+        data["DocText"].append(docText)
+        data["ActionFlag"].append(action)
+        data["Amount"].append(amount)
+        data["DocumentType"].append(docType)
+
     """
     return FedMinutes as pandas DataFrame
     """
     def getMinutes(minutesDir, df, clean_algo, abortOnFail=False):
-        data={"meetingDate":[], "year":[], "doctext":[], "actionFlag":[], "rateChange":[], "documentType":[]}
+        data={"MinutesRelease":[],"DocDate":[], "Year":[], "DocText":[], "ActionFlag":[], "Amount":[], "DocumentType":[]}
         for files in sorted(os.listdir(minutesDir)):
             f, ext = os.path.splitext(files)
             try:
@@ -56,13 +65,8 @@ class modelutils:
                 release_date = datetime.datetime.strptime(f.split("_")[-1],"%Y%m%d")
                 text = clean_algo(open(os.path.join(minutesDir, files)).read().strip())
                 action = df[df["MinutesRelease"] == release_date].iloc[0]["ActionFlag"]
-                change = df[df["MinutesRelease"] == release_date].iloc[0]["Amount"]
-                data["meetingDate"].append(release_date)
-                data["year"].append(release_date.year)
-                data["doctext"].append(text)
-                data["actionFlag"].append(action)
-                data["rateChange"].append(change)
-                data["documentType"].append("minutes")
+                amount = df[df["MinutesRelease"] == release_date].iloc[0]["Amount"]
+                modelutils.updateData(data, release_date, release_date, text, action, amount, "minutes")
             except Exception as e:
                 print("exception reading minutes, file %s" % files)
                 print(e)
@@ -72,21 +76,17 @@ class modelutils:
 
 
     def getStatements(statementsDir, df, clean_algo, abortOnFail=False):
-        data={"meetingDate":[], "year":[], "doctext":[], "actionFlag":[], "rateChange":[], "documentType":[]}
[…]

### 2019-04-23 src/model2_0.py
added pct positive in training and test data

@@ -28,7 +28,7 @@ from modelutils import modelutils
 
 
 def runModels(models, model_data_set, Nitr, pctTrain, ngram):
-    results=[]
+    results, trainPos, testPos=[], np.zeros(Nitr), np.zeros(Nitr)
     for iter in range(Nitr):
         train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
         training_features, test_features = modelutils.getFeatures(train_data, test_data, ngram)
@@ -40,7 +40,9 @@ def runModels(models, model_data_set, Nitr, pctTrain, ngram):
             if iter == 0:
                 results.append(np.zeros(Nitr))
             results[i][iter]=acc
-    return results
+        trainPos[iter] = train_data["ActionFlag"].sum()/ len(train_data)
+        testPos[iter] = test_data["ActionFlag"].sum()/ len(test_data)
+    return results, trainPos, testPos
                 
 
 if __name__ == '__main__':
@@ -94,15 +96,15 @@ if __name__ == '__main__':
             ("Naive Bayes",MultinomialNB())]
 
     print("Determining Fed Action from minutes")
-    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s" % 
-          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets"))
+    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s" % 
+          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP"))
     for ngram in ngrams:
-        results= runModels(models, data_set, Niter, pctTrain, ngram)
+        results, trainPos, testPos = runModels(models, data_set, Niter, pctTrain, ngram)
         ngramstr = str(ngram[0]) + ":" + str(ngram[1])
         for m, r in zip(models, results):
             name, mu, s = m[0], np.mean(r), np.std(r) 
-            print("%-20s %5s %5s %10.4f %10.4f %5d %8.3f %7s %10s %10s %-27s" % 
-                  (name, ngramstr, Niter, mu, s, N, pctTrain, cleanA, start, end, datasetlabel))
+            print("%-20s %5s %5s %10.4f %10.4f %5d %8.3f %7s %10s %10s %-27s %6.3f %6.3f" % 
[…]

### 2019-04-24 src/model2_0-precision-recall.py
precision/recall/f1

@@ -1,0 +1,120 @@
+import os
+import sys
+import argparse
+import numpy as np
+import pandas as pd
+import datetime
+import bisect
+import re
+from clean import simple_clean
+from clean import complex_clean
+from sklearn.feature_extraction.text import CountVectorizer
+from sklearn.feature_extraction.text import TfidfVectorizer
+from sklearn.metrics import accuracy_score
+from sklearn.svm import LinearSVC
+from sklearn.linear_model import LogisticRegression
+from sklearn.naive_bayes import MultinomialNB
+import matplotlib.pyplot as plt
+import csv
+from modelutils import modelutils
+from sklearn.metrics import precision_recall_fscore_support
+
+# this version allows for multiple fit methods (SVM, Logistic, Logistic Lasso)
+# this method also computes the mean and std deviation of the accuracy by
+# this version also allows for ngrams
+# allows the text preprocessing algorithm to be selected
+# running each model Niter Times
+
+# python ./model2_0.py --ngram 1,1 2,2 3,3 1,3 2,3 --Niter 3 --pctTrain .8 --data minutes speeches statements
+
+
+def runModels(models, model_data_set, Nitr, pctTrain, ngram):
+    results, prec,recall,f1, trainPos, testPos=[],[],[],[], np.zeros(Nitr), np.zeros(Nitr)
+    for iter in range(Nitr):
+        train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
+        training_features, test_features = modelutils.getFeatures(train_data, test_data, ngram)
+        for i, m in enumerate(models):
+            model=m[1]
+            model.fit(training_features, train_data["ActionFlag"])
+            y_pred = model.predict(test_features)
+            acc = accuracy_score(test_data["ActionFlag"], y_pred)
+            if iter == 0:
+                results.append(np.zeros(Nitr))
+                prec.append(np.zeros(Nitr))
+                recall.append(np.zeros(Nitr))
+                f1.append(np.zeros(Nitr))
+            results[i][iter]=acc
+            prec_recall = precision_recall_fscore_support(test_data['ActionFlag'].tolist(), y_pred, average='binary') 
+            prec[i][iter] = prec_recall[0]
+            recall[i][iter] = prec_recall[1]
+            f1[i][iter] = prec_recall[2]
[…]

### 2019-04-24 src/simulator.py
add simulator

@@ -1,0 +1,154 @@
+import os
+import numpy as np
+import argparse
+import pandas as pd
+from sklearn.metrics import accuracy_score
+from sklearn.svm import LinearSVC
+from sklearn.linear_model import LogisticRegression
+from sklearn.feature_extraction.text import CountVectorizer
+import matplotlib.pyplot as plt
+
+#
+# This run random experiments to detect sentimate in randomly generated text
+#
+# Overview 
+# 1) load 3 word dictionaries common, positive, negative
+# 2) randomly generate data using (common, positive) (common, negative), shuffle
+# 3) split into test training
+# 4) create features (X's) for trainng/test using Vectorize
+# 5) fit the model
+# 6) check its accuracy
+
+# To run download the following 3 files of common, positive and negative words: 
+# (1) A list of 20k commonly used English Words
+#    curl https://raw.githubusercontent.com/first20hours/google-10000-english/master/20k.txt -o 20k.txt
+# (2) A list of negative words 
+#    curl https://gist.githubusercontent.com/mkulakowski2/4289441/raw/dad8b64b307cd6df8068a379079becbb3f91101a/negative-words.txt -o neg_words.tx
+# (3) A list of positive words
+#    curl https://gist.githubusercontent.com/mkulakowski2/4289437/raw/1bb4d7f9ee82150f339f09b5b1a0e6823d633958/positive-words.txt -o pos_words.txt
+# To run download the following 3 files
+#
+
+#
+# read in words from common, postive, negative
+# return 3 lists common, postive, negative
+#
+def loadWords(commonFile="./20k.txt", positiveFile="./pos_words.txt", negativeFile="./neg_words.txt"):
+    # curl https://gist.githubusercontent.com/mkulakowski2/4289441/raw/dad8b64b307cd6df8068a379079becbb3f91101a/negative-words.txt -o neg_words.tx
+    # curl https://gist.githubusercontent.com/mkulakowski2/4289437/raw/1bb4d7f9ee82150f339f09b5b1a0e6823d633958/positive-words.txt -o pos_words.txt
+    # curl https://raw.githubusercontent.com/first20hours/google-10000-english/master/20k.txt -o 20k.txt
+
+    neg = [w for w in open(negativeFile).read().split('\n')
+           if len(w) > 0 and w[0] != ';']
+
+    pos = [w for w in open(positiveFile).read().split('\n')
+           if len(w) > 0 and w[0] != ';']
+
[…]

### 2019-04-24 src/simulator.py
sim

@@ -9,6 +9,9 @@ from sklearn.feature_extraction.text import CountVectorizer
 import matplotlib.pyplot as plt
 
 #
+# Code simulator
+
+#
 # This run random experiments to detect sentimate in randomly generated text
 #
 # Overview 

### 2019-04-24 src/simulator.py
update simulator.py

@@ -112,9 +112,9 @@ def fitData(train_data, test_data, modelType="svc"):
 
 if __name__ == '__main__':
     parser = argparse.ArgumentParser(description='ML Project')
-    parser.add_argument('--common', default="./20k.txt")
-    parser.add_argument('--positive', default="./pos_words.txt")
-    parser.add_argument('--negative', default="./neg_words.txt")
+    parser.add_argument('--common', default="../simdata/20k.txt")
+    parser.add_argument('--positive', default="../simdata/pos_words.txt")
+    parser.add_argument('--negative', default="../simdata/neg_words.txt")
     parser.add_argument('-n','--N', default=50, type=int)
     parser.add_argument('-t','--trials', default=3, type=int)
     parser.add_argument('-l','--textLen', default=60, type=int)

### 2019-04-24 src/simulator.py
simchagne

@@ -120,14 +120,14 @@ if __name__ == '__main__':
     parser.add_argument('-l','--textLen', default=60, type=int)
     parser.add_argument('-s','--pctSen', help='pct of sentiment words in the text', default=0.10, type=float)
     parser.add_argument('-p','--pctTrain', help='pct of sample for training', default=0.75, type=float)
+    parser.add_argument('--stp', help='stepsize', default=10, type=int)
     args = parser.parse_args()
 
 
     common, pos, neg = loadWords(args.common, args.positive, args.negative)
-    T, N, textLen, pctSen, pctTrain = args.trials, args.N, args.textLen, args.pctSen, args.pctTrain
+    T, N, textLen, pctSen, pctTrain, stp = args.trials, args.N, args.textLen, args.pctSen, args.pctTrain, args.stp
     
     print("%10s, %10s, %10s, %10s, %10s, %10s, %10s" %('T','N',' TextLen', 'PctSen', 'PctTrain', 'mean(acc)', 'std(acc)'))
-    stp=40
     S = int(textLen/stp)
     L, Asvm, Alog, Aloglasso = np.zeros(S), np.zeros(S), np.zeros(S), np.zeros(S)
     # vary textLen

### 2019-04-24 src/simulator.py
sim

@@ -63,15 +63,15 @@ def loadWords(commonFile="./20k.txt", positiveFile="./pos_words.txt", negativeFi
 # output 
 # returns randomly shuffeled nparray ([text0, score0], [text1, score1], ... [textN-1, scoreN-1])
 # where text_i is either postive or negative
-def generateData(common_words, pos_words, neg_words, N, textLen, pctSen, pos_score=1, neg_score=0):
+def generateData(common_words, pos_words, neg_words, NSamples, textLen, pctSen, pos_score=1, neg_score=0):
     def genText(Ncommon, common_words, Nsen, sen_words):
         words=np.concatenate((np.random.choice(sen_words, Nsen), np.random.choice(common_words, Ncommon)))
         np.random.shuffle(words)
         return " ".join(words[i] for i in range(len(words)))
     Nsen = int(textLen*pctSen)
     Ncommon = textLen - Nsen
-    pos_data = [[genText(Ncommon, common_words, Nsen, pos_words),pos_score] for i in range(N)]
-    neg_data = [[genText(Ncommon, common_words, Nsen, neg_words),neg_score] for i in range(N)]
+    pos_data = [[genText(Ncommon, common_words, Nsen, pos_words),pos_score] for i in range(NSamples)]
+    neg_data = [[genText(Ncommon, common_words, Nsen, neg_words),neg_score] for i in range(NSamples)]
     all_data = np.concatenate((pos_data, neg_data))
     np.random.shuffle(all_data)
     return all_data

### 2019-04-24 src/simulator.py
sim

@@ -138,6 +138,7 @@ if __name__ == '__main__':
             accsvm[i] = fitData(train_data, test_data, modelType='svc')
             acclog[i] = fitData(train_data, test_data, modelType='logistic')
             accloglasso[i] = fitData(train_data, test_data, modelType='logistic_lasso')
+        label=" %Sen={} N={}".format(pctSen, N) 
         Asvm[j] = np.mean(accsvm)
         Alog[j] = np.mean(acclog)
         Aloglasso[j] = np.mean(accloglasso)
@@ -146,9 +147,9 @@ if __name__ == '__main__':
               (T,N, l, pctSen, pctTrain, np.mean(accsvm), np.std(accsvm), np.mean(acclog), np.std(acclog), np.mean(accloglasso), np.std(accloglasso)))
             
 
-    plt.plot(L, Asvm, label='svm')
-    plt.plot(L, Alog, label='logistic')
-    plt.plot(L, Aloglasso, label='logistic_lasso')
+    plt.plot(L, Asvm, label='svm_{}'.format(label))
+    plt.plot(L, Alog, label='logistic_{}'.format(label))
+    plt.plot(L, Aloglasso, label='logistic_lasso_{}'.format(label))
     plt.title("Accuracy vs N Words in Text")
     plt.xlabel("Words in Text")
     plt.ylabel("Accuracy")

### 2019-04-24 src/simulator.py
refactor sim

@@ -5,6 +5,7 @@ import pandas as pd
 from sklearn.metrics import accuracy_score
 from sklearn.svm import LinearSVC
 from sklearn.linear_model import LogisticRegression
+from sklearn.naive_bayes import MultinomialNB
 from sklearn.feature_extraction.text import CountVectorizer
 import matplotlib.pyplot as plt
 
@@ -36,117 +37,97 @@ import matplotlib.pyplot as plt
 # read in words from common, postive, negative
 # return 3 lists common, postive, negative
 #
-def loadWords(commonFile="./20k.txt", positiveFile="./pos_words.txt", negativeFile="./neg_words.txt"):
-    # curl https://gist.githubusercontent.com/mkulakowski2/4289441/raw/dad8b64b307cd6df8068a379079becbb3f91101a/negative-words.txt -o neg_words.tx
-    # curl https://gist.githubusercontent.com/mkulakowski2/4289437/raw/1bb4d7f9ee82150f339f09b5b1a0e6823d633958/positive-words.txt -o pos_words.txt
-    # curl https://raw.githubusercontent.com/first20hours/google-10000-english/master/20k.txt -o 20k.txt
 
-    neg = [w for w in open(negativeFile).read().split('\n')
-           if len(w) > 0 and w[0] != ';']
+class Words:
 
-    pos = [w for w in open(positiveFile).read().split('\n')
-           if len(w) > 0 and w[0] != ';']
+    def __init__(self, common, neg, pos):
+        self.common = common
+        self.neg = neg
+        self.pos = pos
 
-    common = [w for w in open(commonFile).read().split('\n')
-              if len(w) > 0]
+    def load(commonFile, negFile, posFile): 
+        neg = [w for w in open(negFile).read().split('\n')
+               if len(w) > 0 and w[0] != ';']
+        
+        pos = [w for w in open(posFile).read().split('\n')
+               if len(w) > 0 and w[0] != ';']
+        common = [w for w in open(commonFile).read().split('\n')
+                  if len(w) > 0]
     
-    return common, pos, neg
+        return Words(common, neg, pos)
 
-# generateData
-# inputs
-# N       - total sample size generated
-# Ncommon - number of common_words in text
-# Nsen    - number of sentiment words in text
-# common_words - list of common words
-# pos_words - list of positive words
-# neg_words - list of negative words
-# output 
-# returns randomly shuffeled nparray ([text0, score0], [text1, score1], ... [textN-1, scoreN-1])
[…]

### 2019-04-24 src/simulator.py
sim

@@ -116,12 +116,8 @@ class Simulator:
             resdict[name][i]=acc
         return pd.DataFrame(result)
 
-    def run(words, params):
+    def run(words, params, models):
         max_iter, solver = params.max_iter, params.solver
-        models=[("svm",LinearSVC(max_iter=max_iter)),
-                ("logistic",LogisticRegression(solver=solver,max_iter=max_iter)),
-                ("logistic_lasso",LogisticRegression(penalty='l1',solver=solver,max_iter=max_iter)),
-                ("Naive Bayes",MultinomialNB())]
         resdict = {name:np.zeros(params.trials) for (name,model) in models}
         for i in range(params.trials):
             Simulator.trial(words, params, models, resdict, i)
@@ -156,8 +152,29 @@ if __name__ == '__main__':
 
     words = Words.load(args.common, args.negative, args.positive)
     params = Params(args.trials, args.nSamples, args.textLen, args.pctSen, args.pctTrain, args.max_iter, args.solver)
-    res = Simulator.run(words, params)
-    print(res)
+    max_iter, solver = params.max_iter, params.solver
+    models=[("svm",LinearSVC(max_iter=max_iter)),
+            ("logistic",LogisticRegression(solver=solver,max_iter=max_iter)),
+            ("logistic_lasso",LogisticRegression(penalty='l1',solver=solver,max_iter=max_iter)),
+            ("Naive Bayes",MultinomialNB())]
+    
+    # vary pct words
+    pct = np.arange(0.01, 0.5+0.025, .025)
+    sim_res = {name:np.zeros(len(pct)) for (name, model) in models}
+    for i in range(len(pct)):
+        cp = params
+        cp.pctSen = pct[i]
+        sim_i = Simulator.run(words, params, models)
+        for name in sim_res.keys():
+            sim_res[name][i] = sim_i[name].mean()
+    for sim in sim_res:
+            plt.plot(pct, sim_res[sim], label='{}'.format(sim))
+    plt.title("acc vs pct in text")
+    plt.xlabel("pct in txt")
+    plt.ylabel("acc")
+    plt.legend()
+    plt.show()
+
 
 
 

### 2019-04-25 presentation/paper.tex
paper

@@
 
- \item We test the accuracy of ML models trained on FOMC statements and a percentage of FOMC minutes on a test set of FOMC minutes
+ \item We test the accuracy of ML models trained on a random mixture of FOMC minutes, speeches, and statements on a test set of FOMC documents.
+In this stage, we are determining the viability of ML methods in predicting FOMC action on test documents, and we will evaluate the model accuracy with precision and recall.
+The models are:
+ \begin{itemize}
+    \item Naive Bayes
+    \item Logistic Regression 
+    \item SVM
+    \item Logistic Lasso
+ \end{itemize}
  \item We create a predictive model that is trained on documents that are temporally released before the test document.
-Typically we will test with FOMC minutes releases or Board of Governor speeches.
+Typically we will test with FOMC minutes releases or Board of Governor speeches that are temporally released after the training documents.
+ \item  
 \end{enumerate}
@@
 
-When we train the model with statements and minutes, ten statements will be considered one document because of the magnitude of minute size to statement size.
-
 \subsection{Scraping and Text Pre-Processing}

### 2019-04-26 presentation/paper.tex
update; ;

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
 
@@
 Typically we will test with FOMC minutes releases or Board of Governor speeches that are temporally released after the training documents.
- \item  
+ \item  To determine the appropriate feature vector size, for example, concatenate the documents associated with a meeting or treat each document separately, we simulated how sentiment analysis performs as the feature vector becomes larger.
+ \item  We applied Latent Dirichlet Allocation to the entire corpus of speeches and assumed $k=3$ latent topics to explore whether LDA captures the Federal Reserve's mandates of: maximum employment, stable prices, and financial stability.
 \end{enumerate}
@@
 
-We will provide an overview of how we utilized the following models in our research
+We will provide an overview of how we utilized the following models in our research:
+
+  \begin{itemize}
+
+    \item Naive Bayes
+    \item Logistic Regression
+    \item Logistic Lasso
+    \item SVM
+    \item Neural Network
+    \item Latent Dirilchet Allocation
+
+  \end{itemize}
+
+\textbf{Latent Dirilchet Allocation}: Given the Federal Reserve's mandates of stable prices, maximum employment, and financial stability, we explored Latent Dirichlet Distribution of the speeches and minutes' word distribution over three latent topics.
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{Topic-Model-3-topics.PNG}
+  \caption{Top 15 Words Distributed Over Three Latent Topics}
+  \label{fig:LDA}
+\end{figure}
+
+We found it interesting that "Topic 1" referred solely to financial stability, "Topic 0" primarily referred to inflation and spending, and "Topic 2" returned a word distribution that included labor, growth, and lower for longer monetary policy.
+\vertSpace
+
+\textbf{Naive Bayes}
 

### 2019-04-26 src/model2-lda.py

@@ -18,6 +18,8 @@ import matplotlib.pyplot as plt
 import csv
 from modelutils import modelutils
 from sklearn.metrics import precision_recall_fscore_support
+from sklearn import decomposition
+from sklearn.decomposition import LatentDirichletAllocation
 
 # this version allows for multiple fit methods (SVM, Logistic, Logistic Lasso)
 # this method also computes the mean and std deviation of the accuracy by
@@ -27,31 +29,29 @@ from sklearn.metrics import precision_recall_fscore_support
 
 # python ./model2_0.py --ngram 1,1 2,2 3,3 1,3 2,3 --Niter 3 --pctTrain .8 --data minutes speeches statements
 
+def print_top_words(model, feature_names, n_top_words):
+    print()
+    for topic_idx, topic in enumerate(model.components_):
+        message = "Topic #%d: " % topic_idx
+        message += "|".join([feature_names[i]
+                             for i in topic.argsort()[:-n_top_words - 1:-1]])
+        print(message)
+        print()
+    print()
 
-def runModels(models, model_data_set, Nitr, pctTrain, ngram):
-    results, prec,recall,f1, trainPos, testPos=[],[],[],[], np.zeros(Nitr), np.zeros(Nitr)
-    for iter in range(Nitr):
-        train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
-        training_features, test_features = modelutils.getFeatures(train_data, test_data, ngram)
-        for i, m in enumerate(models):
-            model=m[1]
-            model.fit(training_features, train_data["ActionFlag"])
-            y_pred = model.predict(test_features)
-            acc = accuracy_score(test_data["ActionFlag"], y_pred)
-            if iter == 0:
-                results.append(np.zeros(Nitr))
-                prec.append(np.zeros(Nitr))
-                recall.append(np.zeros(Nitr))
-                f1.append(np.zeros(Nitr))
-            results[i][iter]=acc
-            prec_recall = precision_recall_fscore_support(test_data['ActionFlag'].tolist(), y_pred, average='binary') 
-            prec[i][iter] = prec_recall[0]
-            recall[i][iter] = prec_recall[1]
-            f1[i][iter] = prec_recall[2]
[…]

### 2019-04-27 src/modelutils.py
add direction to data matrix

@@ -43,20 +43,24 @@ class modelutils:
         df['MinutesRelease'] = pd.to_datetime(df['MinutesRelease'],format="%Y%m%d")
         return df
 
-    def updateData(data, minutesReleaseDate, docDate, docText, action, amount, docType):
+    def updateData(data, minutesReleaseDate, docDate, docText, action, amount, direction, docType):
         data["MinutesRelease"].append(minutesReleaseDate)
         data["DocDate"].append(docDate)
         data["Year"].append(docDate.year)
         data["DocText"].append(docText)
         data["ActionFlag"].append(action)
         data["Amount"].append(amount)
+        data["Direction"].append(direction)
         data["DocumentType"].append(docType)
+
+    def getDataCols():
+        return {"MinutesRelease":[],"DocDate":[], "Year":[], "DocText":[], "ActionFlag":[], "Amount":[], "Direction":[], "DocumentType":[]}
 
     """
     return FedMinutes as pandas DataFrame
     """
     def getMinutes(minutesDir, df, clean_algo, abortOnFail=False):
-        data={"MinutesRelease":[],"DocDate":[], "Year":[], "DocText":[], "ActionFlag":[], "Amount":[], "DocumentType":[]}
+        data = modelutils.getDataCols()
         for files in sorted(os.listdir(minutesDir)):
             f, ext = os.path.splitext(files)
             try:
@@ -66,7 +70,8 @@ class modelutils:
                 text = clean_algo(open(os.path.join(minutesDir, files)).read().strip())
                 action = df[df["MinutesRelease"] == release_date].iloc[0]["ActionFlag"]
                 amount = df[df["MinutesRelease"] == release_date].iloc[0]["Amount"]
-                modelutils.updateData(data, release_date, release_date, text, action, amount, "minutes")
+                direction = df[df["MinutesRelease"] == release_date].iloc[0]["Direction"] 
+                modelutils.updateData(data, release_date, release_date, text, action, amount, direction, "minutes")
             except Exception as e:
                 print("exception reading minutes, file %s" % files)
                 print(e)
@@ -76,7 +81,7 @@ class modelutils:
 
 
     def getStatements(statementsDir, df, clean_algo, abortOnFail=False):
-        data={"MinutesRelease":[],"DocDate":[], "Year":[], "DocText":[], "ActionFlag":[], "Amount":[], "DocumentType":[]}
+        data = modelutils.getDataCols()
         for files in sorted(os.listdir(statementsDir)):
             f, ext = os.path.splitext(files)
             try:
[…]

### 2019-04-27 src/modelutils.py
added stack features to modelutils

@@ -121,6 +121,25 @@ class modelutils:
                     quit()
         return pd.DataFrame(data)
 
+    def stackFeatures(data_set):
+            c = pd.concat(data_set)
+            g=c.groupby(['MinutesRelease']).agg({'MinutesRelease':['min'],
+                                                 'DocDate':['min','max'],
+                                                 'Year':['min'],
+                                                 'ActionFlag':['max'],
+                                                 'Amount' : ['mean'],
+                                                 'Direction': lambda x : '_'.join(x),
+                                                 'DocText': lambda x : ' '.join(x),
+                                                 'DocumentType': lambda x : ' '.join(x)})
+            dirV = g['Direction']['<lambda>'].values
+            return pd.DataFrame({'MinutesRelease':g['MinutesRelease']['min'].values,
+                                 'DocDate':g['DocDate']['min'].values,
+                                 'Year':g['Year']['min'].values,
+                                 'ActionFlag':g['ActionFlag']['max'].values,
+                                 'Direction':[dirV[i].split("_")[0] for i in range(len(dirV))],
+                                 'DocText':g['DocText']['<lambda>'].values,
+                                 'DocumentType':g['DocumentType']['<lambda>'].values})
+
     def get_ix(dateV, date):
         dt64 = modelutils.to_np64(date)
         return modelutils.get_ge(dateV, dt64)

### 2019-04-27 src/test_modelutils.py
test_modeltulis

@@ -38,3 +38,11 @@ if __name__ == '__main__':
     print(train)
     print("randmoly split test set")
     print(test)
+
+    #
+    #
+    #
+    data_stacked = modelutils.stackFeatures([mn, st, sp])
+    print("--- all of the features stacked---")
+    print(data_stacked)
+

### 2019-04-27 src/model2_0.py
add stack to model2_0

@@ -58,6 +58,7 @@ if __name__ == '__main__':
     parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=25000, type=int)
     parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
+    parser.add_argument('--stack', action='store_true', default=False)
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -88,6 +89,12 @@ if __name__ == '__main__':
     assert N  > 0, "no data in data_set"
     start, end = start.strftime("%m/%d/%Y"), end.strftime("%m/%d/%Y")
     
+    if args.stack:
+        data_set = modelutils.stackFeatures(data_set)
+        N = len(data_set)
+        stack="True"
+    else:
+        stack="Flase"
 
     # Train on current minutes
     models=[("svm",LinearSVC(max_iter=max_iter)),
@@ -96,15 +103,15 @@ if __name__ == '__main__':
             ("Naive Bayes",MultinomialNB())]
 
     print("Determining Fed Action from minutes")
-    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s" % 
-          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP"))
+    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %5s" % 
+          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Stack"))
     for ngram in ngrams:
         results, trainPos, testPos = runModels(models, data_set, Niter, pctTrain, ngram)
         ngramstr = str(ngram[0]) + ":" + str(ngram[1])
         for m, r in zip(models, results):
             name, mu, s = m[0], np.mean(r), np.std(r) 
-            print("%-20s %5s %5s %10.4f %10.4f %5d %8.3f %7s %10s %10s %-27s %6.3f %6.3f" % 
[…]

### 2019-04-27 src/model2_0-precision-recall.py
added stack to mode2prec

@@ -66,6 +66,7 @@ if __name__ == '__main__':
     parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=25000, type=int)
     parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
+    parser.add_argument('--stack', action='store_true', default=False)
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -95,6 +96,14 @@ if __name__ == '__main__':
 
     assert N  > 0, "no data in data_set"
     start, end = start.strftime("%m/%d/%Y"), end.strftime("%m/%d/%Y")
+
+    if args.stack:
+        data_set = modelutils.stackFeatures(data_set)
+        N = len(data_set)
+        stack="True"
+    else:
+        stack="Flase"
+
     
 
     # Train on current minutes
@@ -104,8 +113,8 @@ if __name__ == '__main__':
             ("Naive Bayes",MultinomialNB())]
 
     print("Determining Fed Action from minutes")
-    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s" % 
-          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1"))
+    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s %5s" % 
+          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1", "Stack"))
 
     outputDF = []
 
@@ -114,11 +123,11 @@ if __name__ == '__main__':
         ngramstr = str(ngram[0]) + ":" + str(ngram[1])
         for m, r, t, u, v in zip(models, results, prec, recall, f1):
             name, mu, s, precMu, recallMu, f1Mu = m[0], np.mean(r), np.std(r), np.mean(t), np.mean(u), np.mean(v)
[…]

### 2019-04-27 src/model2-pre-recall-simulations.py
stack pre-recall

@@ -68,6 +68,7 @@ if __name__ == '__main__':
     parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     parser.add_argument('--outputFileName', default = 'data_multiple_iterations.csv')
+    parser.add_argument('--stack', action='store_true', default=False)
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -100,6 +101,12 @@ if __name__ == '__main__':
     assert N  > 0, "no data in data_set"
     start, end = start.strftime("%m/%d/%Y"), end.strftime("%m/%d/%Y")
     
+    if args.stack:
+        data_set = modelutils.stackFeatures(data_set)
+        N = len(data_set)
+        stack="True"
+    else:
+        stack="Flase"
 
     # Train on current minutes
     models=[("svm",LinearSVC(max_iter=max_iter)),
@@ -108,8 +115,8 @@ if __name__ == '__main__':
             ("Naive Bayes",MultinomialNB())]
 
     print("Determining Fed Action from minutes")
-    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s" % 
-          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1"))
+    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s %5s" % 
+          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1", "Stack"))
 
     outputDF = []
     for i in range(1,IterLoop):
@@ -119,11 +126,11 @@ if __name__ == '__main__':
           ngramstr = str(ngram[0]) + ":" + str(ngram[1])
           for m, r, t, u, v in zip(models, results, prec, recall, f1):
[…]

### 2019-04-27 src/model2-lda.py
stack in lda

@@ -66,6 +66,7 @@ if __name__ == '__main__':
     parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=25000, type=int)
     parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
+    parser.add_argument('--stack', action='store_true', default=False)
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -94,4 +95,6 @@ if __name__ == '__main__':
         N , start, end = N + N1, min(start, start1), max(end, end1)
     assert N  > 0, "no data in data_set"
     start, end = start.strftime("%m/%d/%Y"), end.strftime("%m/%d/%Y")
+    if args.stack:
+        data_set = [modelutils.stackFeatures(data_set)]
     runModels(data_set)

### 2019-04-28 presentation/paper.tex
update

@@
 \usepackage{graphicx}
-
+\usepackage{caption}
+\usepackage{subcaption}
 \newcommand{\vertSpace}[1]{\vspace{3mm}}
@@
 
-We will provide an overview of how we utilized the following models in our research:
+\subsubsection{Latent Dirichlet Allocation}
+
+We explored latent topic modelling in our research to determine how a machine learning algorithm would classify $k=3$ topics, a proxy for the Federal Reserve's three objectives. \vertSpace
+
+Given the Federal Reserve's mandates of stable prices, maximum employment, and financial stability, we explored Latent Dirichlet Distribution of the speeches and minutes' word distribution over three latent topics.
+We were interested in exploring how well a topic model would distribute words over the three objectives and if the meaning of the distributions were relatively clear.
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{Topic-Model-3-topics.PNG}
+  \caption{Top 15 Words Distributed Over Three Latent Topics}
+  \label{fig:LDA}
+\end{figure}
+
+We found that the topic model generally distributed the speeches and minutes into the three categories fairly well.
+It was interesting that "Topic 1" referred solely to financial stability, "Topic 0" primarily referred to inflation and spending, and "Topic 2" returned a word distribution that included labor, growth, and lower for longer monetary policy.
+\vertSpace
+
+\subsubsection{Supervised Models}
+
+We utilized the following models in our research:
 
@@
     \item Neural Network
-    \item Latent Dirilchet Allocation
 
@@
 
-\textbf{Latent Dirilchet Allocation}: Given the Federal Reserve's mandates of stable prices, maximum employment, and financial stability, we explored Latent Dirichlet Distribution of the speeches and minutes' word distribution over three latent topics.
+\subsubsection{Basic Model Choice and Performance}
+
+The basic models are Naive Bayes, Logistic Regression, Logistic Lasso, and SVM.
+We tested for model accuracy through averaging various iterations of each model's results, and we empirically tested for the optimal number of bigrams and anagrams.
+\vertSpace
+
+We found that the general accuracy of each model (for bigrams) peaked at around ten iterations of each model.
+The F1 score, measured as the accuracy of predicting an FOMC move (up = down = 1) with bigrams, also peaks at around 10 iterations per model.
+\vertSpace
+
+Given that the basic models are predicting binary classification we expected the Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform the best.
+Based on empirical knowledge, FOMC rate moves are analyzed in terms of probabilities and the upcoming meeting is judged primarily on the outcome of Fed action or no action.
+\vertSpace
+
+Despite some good properties of SVM such as, SVM tend to perform better than logistic regression due to the face that SVMs are less sensitive to outliers and SVM try to maximize the margin between the closest support vectors while LR the posterior class probability.
+SVM generally find a solution which is as fare as possible for the two categories.
+SVM provide prediction of 1 or 0, while the Logistic Regression provides a probability were a probability of 0.501 is enough for the prediction of FOMC rate action.
+\vertSpace
+
+In addition, because this is a binary classification problem, we also exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression with L2 regularization.
+\vertSpace
+
+We included Naive Bayes as a benchmark due to prior study of FOMC sentiment analysis using NLP found that Naive Bayes perfomed the best in their study.
 
 \begin{figure}[h!]
-  \includegraphics[width=\linewidth]{Topic-Model-3-topics.PNG}
-  \caption{Top 15 Words Distributed Over Three Latent Topics}
-  \label{fig:LDA}
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+\includegraphics[height=2in,width=2in]{../text/data_for_graphs/accuracy.pdf}
+\caption{Accuracy peaks at around 10 iterations}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+\includegraphics[height=2in,width=2in]{../text/data_for_graphs/F1.pdf}
+  \caption{A subfigure}
+  \label{fig:sub2}
+\end{subfigure}
+\caption{F1 also peaks at around 10 iterations}
+\label{fig:test}
 \end{figure}
 
-We found it interesting that "Topic 1" referred solely to financial stability, "Topic 0" primarily referred to inflation and spending, and "Topic 2" returned a word distribution that included labor, growth, and lower for longer monetary policy.
-\vertSpace
-
-\textbf{Naive Bayes}
+As seen in the graphs above, the Logistic Lasso regression performs the best out of the four basic models.
 

### 2019-04-29 presentation/paper.tex
update

@@
 
+\subsection{Feature Choice}
+
+Based on previous research that applied Naive Bayes to analyzing FOMC transcripts \cite{stanford} ML models performed better with N-grams and performance peaked at tri-grams for Naive Bayes.
+In our models, we found that N-grams of greater N saw greater accuracy and lower standard deviation.
+
 \begin{figure}[h!]
@@
 
+\bibitem{stanford} Puri, Indira \emph{USING MACHINE LEARNING TO PREDICT INTEREST RATE CHANGES FROM FEDERAL RESERVE PROCEEDINGS}
 \end{thebibliography}

### 2019-04-30 src/model3_neuralNet.py
neural net working v1

@@ -11,40 +11,18 @@ import argparse
 import torch
 import torch.nn as nn
 import torch.nn.functional as F
-import torch.utils.data as data 
+import torch.utils.data as udata 
 from torch.autograd import Variable
+import torch
+from torchtext import data
+
+
 from clean import simple_clean
 from clean import complex_clean
 from modelutils import modelutils
 
 # to install pytorch
 # conda install pytorch torchvision -c soumith
-
-#
-# Neural Net1 Fully Connected
-#
-class FCNet1(nn.Module):
-
-    def __init__(self, N):
-        super(FCNet1, self).__init__()
-
-        # 2 hidden layer NN
-
-        # layer1 x->
-        self.fc1 = nn.Sequential(nn.Linear(N, N), nn.ReLU())
-
-        #layer2 
-        n2 = int(N/2)
-        
-        self.fc2 = nn.Sequential(nn.Linear(N, n2), nn.ReLU())
-
-        #output could do three to predict if raise, lower or hold
-        self.fc3 = nn.Sequential(nn.Linear(n2, 2), nn.Sigmoid())
-
-    def forward(self, X):
-        xo = self.fc1(X)
-        xo = self.fc2(xo)
-        return self.fc2(xo)
 
 
 if __name__ == '__main__':
@@ -60,6 +38,7 @@ if __name__ == '__main__':
     parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=25000, type=int)
     parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
+    parser.add_argument('--stack', action='store_true', default=False)
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -89,9 +68,30 @@ if __name__ == '__main__':
 
     assert N  > 0, "no data in data_set"
     start, end = start.strftime("%m/%d/%Y"), end.strftime("%m/%d/%Y")
-
     
-    net = FCNet1(100)
+    if args.stack:
+        data_set = modelutils.stackFeatures(data_set)
+        N = len(data_set)
+        stack="True"
+    else:
+        stack="Flase"
+
+    model_data_set = data_set
+    train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
[…]

### 2019-04-30 src/model3_neuralNet.py
clean nn

@@ -8,13 +8,8 @@ import time
 import datetime
 import numpy as np
 import argparse
-import torch
-import torch.nn as nn
-import torch.nn.functional as F
-import torch.utils.data as udata 
-from torch.autograd import Variable
-import torch
-from torchtext import data
+from sklearn.neural_network import MLPClassifier  
+from sklearn.metrics import accuracy_score
 
 
 from clean import simple_clean
@@ -81,8 +76,6 @@ if __name__ == '__main__':
     training_features, test_features = modelutils.getFeatures(train_data, test_data, ngrams[0])
 
 
-    from sklearn.neural_network import MLPClassifier  
-    from sklearn.metrics import accuracy_score
     #mlp = MLPClassifier(hidden_layer_sizes=(10, 10, 10), max_iter=1000)  
     mlp = MLPClassifier(hidden_layer_sizes=(50, 40, 10), max_iter=1000)  
     #mlp.fit(X_train, y_train.values.ravel())  

### 2019-04-30 src/model4_nn_pytorch.py
put pytorhc nn into model4

@@ -1,0 +1,113 @@
+#
+#
+#
+from __future__ import print_function
+import sys
+import os
+import time
+import datetime
+import numpy as np
+import argparse
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.utils.data as udata 
+from torch.autograd import Variable
+import torch
+from torchtext import data
+
+
+from clean import simple_clean
+from clean import complex_clean
+from modelutils import modelutils
+
+# to install pytorch
+# conda install pytorch torchvision -c soumith
+
+#
+# Neural Net1 Fully Connected
+#
+class FCNet1(nn.Module):
+
+    def __init__(self, N):
+        super(FCNet1, self).__init__()
+
+        # 2 hidden layer NN
+
+        # layer1 x->
+        self.fc1 = nn.Sequential(nn.Linear(N, N), nn.ReLU())
+
+        #layer2 
+        n2 = int(N/2)
+        
+        self.fc2 = nn.Sequential(nn.Linear(N, n2), nn.ReLU())
+
+        #output could do three to predict if raise, lower or hold
+        self.fc3 = nn.Sequential(nn.Linear(n2, 2), nn.Sigmoid())
+
+    def forward(self, X):
+        xo = self.fc1(X)
+        xo = self.fc2(xo)
+        return self.fc2(xo)
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
+    parser.add_argument('--minutes', default="../text/minutes")
+    parser.add_argument('--speeches', default="../text/speeches")
+    parser.add_argument('--statements', default="../text/statements")
+    parser.add_argument('--pctTrain', default=0.75, type=float)
+    parser.add_argument('--Niter', help="number of times to refit data", default=10, type=int)
+    parser.add_argument('--cleanAlgo', default="complex")
+    parser.add_argument('--ngram', nargs='+', default=['1,1'])
+    parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=25000, type=int)
+    parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
+    parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
+    parser.add_argument('--stack', action='store_true', default=False)
[…]

### 2019-04-30 src/model3_nn.py
put in model loop

@@ -8,9 +8,10 @@ import time
 import datetime
 import numpy as np
 import argparse
+import pandas as pd
 from sklearn.neural_network import MLPClassifier  
 from sklearn.metrics import accuracy_score
-
+from sklearn.metrics import precision_recall_fscore_support
 
 from clean import simple_clean
 from clean import complex_clean
@@ -18,6 +19,31 @@ from modelutils import modelutils
 
 # to install pytorch
 # conda install pytorch torchvision -c soumith
+def runModels(models, model_data_set, Nitr, pctTrain, ngram):
+    results, prec,recall,f1, trainPos, testPos=[],[],[],[], np.zeros(Nitr), np.zeros(Nitr)
+    for iter in range(Nitr):
+        train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
+        training_features, test_features = modelutils.getFeatures(train_data, test_data, ngram)
+        for i, m in enumerate(models):
+            model=m[1]
+            model.fit(training_features, train_data["ActionFlag"])
+            y_pred = model.predict(test_features)
+            acc = accuracy_score(test_data["ActionFlag"], y_pred)
+            if iter == 0:
+                results.append(np.zeros(Nitr))
+                prec.append(np.zeros(Nitr))
+                recall.append(np.zeros(Nitr))
+                f1.append(np.zeros(Nitr))
+            results[i][iter]=acc
+            prec_recall = precision_recall_fscore_support(test_data['ActionFlag'].tolist(), y_pred, average='binary') 
+            prec[i][iter] = prec_recall[0]
+            recall[i][iter] = prec_recall[1]
+            f1[i][iter] = prec_recall[2]
+        trainPos[iter] = train_data["ActionFlag"].sum()/ len(train_data)
+        testPos[iter] = test_data["ActionFlag"].sum()/ len(test_data)
+    return results, trainPos, testPos, prec, recall, f1
+
+
 
 
 if __name__ == '__main__':
@@ -71,20 +97,23 @@ if __name__ == '__main__':
     else:
         stack="Flase"
 
-    model_data_set = data_set
-    train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
[…]

### 2019-04-30 src/model3_nn.py
added header

@@ -99,6 +99,9 @@ if __name__ == '__main__':
 
     models=[("nn_30_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000))]
     outputDF = []
+    print("Determining Fed Action from minutes")
+    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s %5s" % 
+          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1", "Stack"))
 
     for ngram in ngrams:
         results, trainPos, testPos, prec, recall, f1 = runModels(models, data_set, Niter, pctTrain, ngram)

### 2019-04-30 src/model3_nn.py
added various layered nn

@@ -97,7 +97,11 @@ if __name__ == '__main__':
     else:
         stack="Flase"
 
-    models=[("nn_30_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000))]
+    models=[("nn_30_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000)),
+            ("nn_40_20_10", MLPClassifier(hidden_layer_sizes=(40, 20, 10), max_iter=1000)),
+            ("nn_40_20_10_2", MLPClassifier(hidden_layer_sizes=(40, 20, 10, 2), max_iter=1000))]
+
+            
     outputDF = []
     print("Determining Fed Action from minutes")
     print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s %5s" % 

### 2019-04-30 src/model3_nn.py
nn3

@@ -98,10 +98,11 @@ if __name__ == '__main__':
         stack="Flase"
 
     models=[("nn_30_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000)),
+            ("nn_10_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000)),
+            ("nn_10_10_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000)),
             ("nn_40_20_10", MLPClassifier(hidden_layer_sizes=(40, 20, 10), max_iter=1000)),
             ("nn_40_20_10_2", MLPClassifier(hidden_layer_sizes=(40, 20, 10, 2), max_iter=1000))]
 
-            
     outputDF = []
     print("Determining Fed Action from minutes")
     print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s %5s" % 

### 2019-05-01 src/model2_0-precision-recall.py
create output option

@@ -67,6 +67,7 @@ if __name__ == '__main__':
     parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     parser.add_argument('--stack', action='store_true', default=False)
+    parser.add_argument('-o','--output', default='../text/data_for_graphs/model2_anagrams.csv')
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -130,4 +131,5 @@ if __name__ == '__main__':
         print("")
 
     outputDF = pd.DataFrame(outputDF)
-    outputDF.to_csv('../text/data_for_graphs/model2_anagrams.csv', index=False, header=["Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1", "Stack"])
+    print("writing to {}".format(args.output))
+    outputDF.to_csv(args.output, index=False, header=["Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1", "Stack"])

### 2019-05-01 src/model2_0-precision-recall.py
desc

@@ -54,7 +54,7 @@ def runModels(models, model_data_set, Nitr, pctTrain, ngram):
                 
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Project Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/documentMetadata.py
fix desc

@@ -61,7 +61,7 @@ def printMetaData(docType,numWords,numDocs,wordVec):
   print('Total Words in '+docType+ ': '+str(numWords) + '\nTotal Docs: '+str(numDocs) + '\nAvg Words Per Doc: ' + str(numWords/numDocs) + '\nStDev: ' + str(statistics.stdev(wordVec, numWords/numDocs))+ '\n')
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")
     parser.add_argument('--statements', default="../text/statements")

### 2019-05-01 src/model0.py

@@ -57,7 +57,7 @@ def getMinutes(minutesDir, decisionDF):
     return data
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/model1-v2.py

@@ -107,7 +107,7 @@ def runModels(models, data, data_statements, Nitr, pctTrain, ngrams):
                 
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/model1.py

@@ -85,7 +85,7 @@ def runModels(models, data, Nitr, pctTrain):
                 
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/model2-lda.py

@@ -54,7 +54,7 @@ def runModels(model_data_set):
     print_top_words(lda, tf_feature_names, 15)
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/model2-pre-recall-simulations.py

@@ -54,7 +54,7 @@ def runModels(models, model_data_set, Nitr, pctTrain, ngram):
                 
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/model2_0.py

@@ -46,7 +46,7 @@ def runModels(models, model_data_set, Nitr, pctTrain, ngram):
                 
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/model3_nn.py
fix desc

@@ -47,7 +47,7 @@ def runModels(models, model_data_set, Nitr, pctTrain, ngram):
 
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/model4_nn_pytorch.py

@@ -52,7 +52,7 @@ class FCNet1(nn.Module):
 
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/test_modelutils.py

@@ -6,7 +6,7 @@ import argparse
 
 
 if __name__ == '__main__':
-    parser = argparse.ArgumentParser(description='SocialNetworks CSV to HDF5')
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('--decision', default="../text/history/RatesDecision.csv")
     parser.add_argument('--minutes', default="../text/minutes")
     parser.add_argument('--speeches', default="../text/speeches")

### 2019-05-01 src/plot_results.py
add plot results

@@ -1,0 +1,74 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+import argparse
+
+
+"""
+Compare Plot fits accuracy, precision, recall and f1 vs ngram length
+"""
+def fitScore(df, fit, output):
+    ll = df[df["Model Name"] == fit]
+    x = ll.NGramInt
+    f1 = ll.F1
+    recall = ll.Recall
+    precision = ll.Prec
+    
+    acc = ll["mean(acc)"].values
+    plt.title("{} vs NGram Length".format(fit))
+    plt.plot(x, f1, label='F1')
+    plt.plot(x, recall, label='Recall')
+    plt.plot(x, precision, label='Precision')
+    plt.plot(x, acc, label='Accuracy')
+    plt.xlabel('NGram Length')
+    plt.ylabel('Pct')
+    plt.legend()
+    if output is not None:
+        plt.savefig("{}.pdf".format(output), bbox_inches='tight')
+    else:
+        plt.show()
+
+
+"""
+Compare F1 Scores of the Fits vs NGram Length
+"""
+def compareFits(df, fits, output):
+    for f in fits:
+        ll = df[df["Model Name"] == f]
+        x = ll.NGramInt
+        f1 = ll.F1
+        plt.plot(x, f1, label='{} F1'.format(f))
+    plt.title('F1 Scores: ' + ','.join(f for f in fits))
+    plt.xlabel('NGram Length')
+    plt.ylabel('Pct')
+    plt.legend()
+    if output is not None:
+        plt.savefig("{}.pdf".format(output), bbox_inches='tight')
+    else:
+        plt.show()
+    
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
+    parser.add_argument('-i','--input', default=None)
+    parser.add_argument('-o','--output', default=None)
+    parser.add_argument('-f','--fit', nargs='+', choices=['svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'], default='logistic_lasso')
+    args = parser.parse_args()
+    
+
+    df = pd.read_csv(args.input)
+    ng = df.NGram.values
+    z = [int(x.split(':')[0]) for x in ng]
+    df["NGramInt"] = z
+
+    fits = [f.replace("_B"," B") for f in args.fit]
+    if len(fits) == 1:
+        fitScore(df, fits[0], args.output)
+    if len(fits) > 1:
+        compareFits(df, fits, args.output)
+
+
+
+
+

### 2019-05-01 src/model2_0-precision-recall.py
add warning to model

@@ -67,6 +67,7 @@ if __name__ == '__main__':
     parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     parser.add_argument('--stack', action='store_true', default=False)
+    parser.add_argument('--slow', action='store_true', default=False)
     parser.add_argument('-o','--output', default='../text/data_for_graphs/model2_anagrams.csv')
     args = parser.parse_args()
 
@@ -77,6 +78,10 @@ if __name__ == '__main__':
 
     assert len(datasetlist) > 0, "no data sets specified"
     datasetlabel=":".join(d for d in datasetlist)
+
+    if args.stack == False and max_iter > 100 and args.slow == False:
+        print("warning this is going to run very slowly, max_iter should be lowered below 100, run with --slow to override this warning")
+        quit()
 
     # fed rate decison matrix
     df = modelutils.decisionDF(args.decision)

### 2019-05-01 src/model3_nn.py
update nn model

@@ -17,6 +17,10 @@ from clean import simple_clean
 from clean import complex_clean
 from modelutils import modelutils
 
+# example usage
+# run 3 nn first with one hidden layer with 10 units , then one with 2 hidden layers then one with 3 hidden layers
+#python ./model3_nn.py --data minutes statements --layers 10 10,10 10,10,10  --max_iter 100 --stack --ngram 15:15
+
 # to install pytorch
 # conda install pytorch torchvision -c soumith
 def runModels(models, model_data_set, Nitr, pctTrain, ngram):
@@ -53,13 +57,14 @@ if __name__ == '__main__':
     parser.add_argument('--speeches', default="../text/speeches")
     parser.add_argument('--statements', default="../text/statements")
     parser.add_argument('--pctTrain', default=0.75, type=float)
-    parser.add_argument('--Niter', help="number of times to refit data", default=10, type=int)
+    parser.add_argument('--Niter', help="number of times to refit data", default=3, type=int)
     parser.add_argument('--cleanAlgo', default="complex")
     parser.add_argument('--ngram', nargs='+', default=['1,1'])
-    parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=25000, type=int)
+    parser.add_argument('--max_iter', help="max iterations for sklearn solver", default=250, type=int)
     parser.add_argument('--solver', help="solver for sklearn algo", default='liblinear')
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     parser.add_argument('--stack', action='store_true', default=False)
+    parser.add_argument('--layers', nargs='+', default=['10,10'])
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -97,11 +102,12 @@ if __name__ == '__main__':
     else:
         stack="Flase"
 
-    models=[("nn_30_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000)),
-            ("nn_10_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000)),
-            ("nn_10_10_10", MLPClassifier(hidden_layer_sizes=(30, 10), max_iter=1000)),
-            ("nn_40_20_10", MLPClassifier(hidden_layer_sizes=(40, 20, 10), max_iter=1000)),
[…]

### 2019-05-01 src/model3_nn.py
modify nn plot

@@ -65,6 +65,7 @@ if __name__ == '__main__':
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     parser.add_argument('--stack', action='store_true', default=False)
     parser.add_argument('--layers', nargs='+', default=['10,10'])
+    parser.add_argument('-o','--output', default='../text/data_for_graphs/model2_anagrams.csv')
     args = parser.parse_args()
 
     ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
@@ -126,7 +127,7 @@ if __name__ == '__main__':
         print("")
 
     outputDF = pd.DataFrame(outputDF)
-    outputDF.to_csv('../text/data_for_graphs/model2_anagrams.csv', index=False, header=["Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1", "Stack"])
+    outputDF.to_csv(args.output, index=False, header=["Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1", "Stack"])
 
 
 

### 2019-05-01 src/plot_results.py

@@ -53,7 +53,7 @@ if __name__ == '__main__':
     parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('-i','--input', default=None)
     parser.add_argument('-o','--output', default=None)
-    parser.add_argument('-f','--fit', nargs='+', choices=['svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'], default='logistic_lasso')
+    parser.add_argument('-f','--fit', nargs='+', help= "'svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'", default='logistic_lasso')
     args = parser.parse_args()
     
 

### 2019-05-02 presentation/paper.tex
paper update

@@
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/log_lass_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/log_reg_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/NB_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/SVM_accuracy_more iterations".pdf}
+\end{center}
+\end{figure}
+
 \subsection{Feature Choice}
@@
 \begin{figure}[h!]
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-\includegraphics[height=2in,width=2in]{../text/data_for_graphs/accuracy.pdf}
-\caption{Accuracy peaks at around 10 iterations}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-\includegraphics[height=2in,width=2in]{../text/data_for_graphs/F1.pdf}
-  \caption{A subfigure}
-  \label{fig:sub2}
-\end{subfigure}
-\caption{F1 also peaks at around 10 iterations}
-\label{fig:test}
+\begin{center}
+\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/log_lasso_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/log_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/naive_bayes_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../text/data_for_graphs/SVM_f1".pdf}
+\end{center}
 \end{figure}
@@
 
-\bibitem{stanford} Puri, Indira \emph{USING MACHINE LEARNING TO PREDICT INTEREST RATE CHANGES FROM FEDERAL RESERVE PROCEEDINGS}
+\bibitem{stanford} Puri, Indira \emph{Using Machine Learning to Predict Interest Rate Changes from Federal Reserve Proceedings}
 \end{thebibliography}

### 2019-05-02 src/model3_nn.py
put ngram seq into nn

@@ -68,10 +68,16 @@ if __name__ == '__main__':
     parser.add_argument('-o','--output', default='../text/data_for_graphs/model2_anagrams.csv')
     args = parser.parse_args()
 
-    ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
     clean_algo = complex_clean if args.cleanAlgo == "complex" else simple_clean
     pctTrain, cleanA, Niter, ngram = args.pctTrain, args.cleanAlgo, args.Niter, args.ngram
     solver, max_iter, datasetlist = args.solver, args.max_iter, args.data
+
+    if len(ngram[0].split(':')) > 1 :
+        ngram = ngram[0]
+        lb , ub = int(ngram.split(':')[0]), int(ngram.split(':')[1])
+        ngrams = [(i,i) for i in range(lb, ub+1)]
+    else :
+        ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in ngram]
 
     assert len(datasetlist) > 0, "no data sets specified"
     datasetlabel=":".join(d for d in datasetlist)
@@ -108,7 +114,7 @@ if __name__ == '__main__':
         hidden=tuple([int(x) for x in nn.split(",")])
         model_name = "nn_" + "_".join(x for x in nn.split(","))
         models.append((model_name,MLPClassifier(hidden_layer_sizes=hidden, max_iter=max_iter)))
-        
+        print("model {}".format(model_name))
 
     outputDF = []
     print("Determining Fed Action from minutes")

### 2019-05-02 src/model2_pr.py
fix 2

@@ -71,10 +71,17 @@ if __name__ == '__main__':
     parser.add_argument('-o','--output', default='../text/data_for_graphs/model2_anagrams.csv')
     args = parser.parse_args()
 
-    ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in args.ngram]
     clean_algo = complex_clean if args.cleanAlgo == "complex" else simple_clean
     pctTrain, cleanA, Niter, ngram = args.pctTrain, args.cleanAlgo, args.Niter, args.ngram
     solver, max_iter, datasetlist = args.solver, args.max_iter, args.data
+
+    if len(ngram[0].split(':')) > 1 :
+        ngram = ngram[0]
+        lb , ub = int(ngram.split(':')[0]), int(ngram.split(':')[1])
+        ngrams = [(i,i) for i in range(lb, ub+1)]
+    else :
+        ngrams = [(int(x.split(",")[0]),int(x.split(",")[1])) for x in ngram]
+
 
     assert len(datasetlist) > 0, "no data sets specified"
     datasetlabel=":".join(d for d in datasetlist)

### 2019-05-02 src/plot_results.py
mod plot

@@ -32,12 +32,14 @@ def fitScore(df, fit, output):
 """
 Compare F1 Scores of the Fits vs NGram Length
 """
-def compareFits(df, fits, output):
+def compareFits(df, fits, output, range):
+    range = int(range) if range is not None  else len(df)
     for f in fits:
         ll = df[df["Model Name"] == f]
+        ll = ll[ll["NGramInt"] <= range]
         x = ll.NGramInt
         f1 = ll.F1
-        plt.plot(x, f1, label='{} F1'.format(f))
+        plt.plot(x, f1, marker='o', label='{} F1'.format(f))
     plt.title('F1 Scores: ' + ','.join(f for f in fits))
     plt.xlabel('NGram Length')
     plt.ylabel('Pct')
@@ -53,6 +55,7 @@ if __name__ == '__main__':
     parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('-i','--input', default=None)
     parser.add_argument('-o','--output', default=None)
+    parser.add_argument('-r','--range', default=None)
     parser.add_argument('-f','--fit', nargs='+', help= "'svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'", default='logistic_lasso')
     args = parser.parse_args()
     
@@ -66,7 +69,7 @@ if __name__ == '__main__':
     if len(fits) == 1:
         fitScore(df, fits[0], args.output)
     if len(fits) > 1:
-        compareFits(df, fits, args.output)
+        compareFits(df, fits, args.output, args.range)
 
 
 

### 2019-05-04 presentation/paper.tex
update

--- 2019-04-29 presentation/paper.tex
@@
     \item Naive Bayes
+
+      $$P(A|x_1,x_2,...,x_n) = p(A)\prod_{i=1}^n p(x_i|A)$$
+
     \item Logistic Regression
+
+     $$A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}$$
+
     \item Logistic Lasso
+     $$A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}+ L1$$
     \item SVM
+
+     $$\left [\frac{1}{n} \sum_{i=1}^n max(0,1 - y_i(\vec{w} \dot \vec{x_i} - b)) \right] + \lambda ||\vec{w}||^2$$
     \item Neural Network
-
+      We test a mixture of wide and deep neural nets. 
   \end{itemize}
@@
 
-In addition, because this is a binary classification problem, we also exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression with L2 regularization.
+In addition, because this is a binary classification problem, we also exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.
 \vertSpace
 
-We included Naive Bayes as a benchmark due to prior study of FOMC sentiment analysis using NLP found that Naive Bayes perfomed the best in their study.
+Given that we are modelling a classification problem, we would expect the performance of the Logistic Lasso model based on the mathematical properties of Logistic Lasso more robust for predicting FOMC rate action.
+Logistic regression models the probability distribution of the class label $y$ given a feature vector $x$:
+
+$$p(y=1|x,\theta) = \sigma(\theta^T x) = \frac{1}{1+\exp(-\theta^Tx)}$$
+
+The L1 regularized logistic regression (Logistic Lasso) is defined as:
+
+$$\underset{\rm \theta}{\rm min} \sum_{i=1}^M -\log p(y^{(i)}|x^{(i)}; \theta) + \beta ||\theta||$$
+
+L1 regularization has the effect of forcing feature selection, and as we observe the Logistic Lasso model performs best Tri-grams to 7-grams and performance significantly drops with larger Ngrams.
+\vertSpace
+
+Below is the average accuracy of the four basic classifiers (Naive Bayes, SVM, Logistic Regression, and Logistic Lasso) after 10 iterations:
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lass_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_reg_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/NB_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_accuracy_more iterations".pdf}
+\end{center}
+\end{figure}
+
+\vspace{5cm}
 
@@
 \begin{figure}[h!]
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-\includegraphics[height=2in,width=2in]{../text/data_for_graphs/accuracy.pdf}
-\caption{Accuracy peaks at around 10 iterations}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-\includegraphics[height=2in,width=2in]{../text/data_for_graphs/F1.pdf}
-  \caption{A subfigure}
-  \label{fig:sub2}
-\end{subfigure}
-\caption{F1 also peaks at around 10 iterations}
-\label{fig:test}
+\begin{center}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1".pdf}
+\end{center}
 \end{figure}

### 2019-05-04 presentation/paper.tex
update

@@
 \begin{figure}[h!]
-  \includegraphics[width=\linewidth]{Topic-Model-3-topics.PNG}
+  \includegraphics[width=\linewidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
   \caption{Top 15 Words Distributed Over Three Latent Topics}
@@
 
-L1 regularization has the effect of forcing feature selection, and as we observe the Logistic Lasso model performs best Tri-grams to 7-grams and performance significantly drops with larger Ngrams.
+L1 regularization has the effect of forcing feature selection, and as we observe the Logistic Lasso model performs best with Tri-grams to 7-grams while the F1 measure significantly drops with larger Ngrams.
 \vertSpace
@@
 
+\subsection{Neural Network} 
 % Bibliography

### 2019-05-04 presentation/presentation.tex
update

@@
 
-\frametitle{Introduction}
-test intro
-\end{frame}
+\begin{figure}[h!]
+\includegraphics[width=1\textwidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
+\end{figure}
 
-\begin{frame}
-
-\frametitle{Introduction}
-test 2
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
+\end{center}
+\end{figure}
 
@@
 
-\begin{frame}
-\frametitle{Data}
-TEST
-\end{frame}
-
-\begin{frame}
-\frametitle{Summary}
-
-\begin{itemize}
-  \item The \alert{first main message} of your talk in one or two lines.
-\end{itemize}
-\end{frame}
-
 \end{document}

### 2019-05-04 presentation/paper.tex
update

@@
 \usepackage{subcaption}
+\usepackage{float}
 \newcommand{\vertSpace}[1]{\vspace{3mm}}
@@
 
-In addition, because this is a binary classification problem, we also exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.
+Below is the average accuracy of the four basic classifiers (Naive Bayes, SVM, Logistic Regression, and Logistic Lasso) after 10 iterations:
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lass_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_reg_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/NB_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_accuracy_more iterations".pdf}
+\end{center}
+\end{figure}
+
+\subsection{Feature Choice}
+
+In our search for the optimal model, we tested different strategies for feature selection, namely different size Ngrams and document stacking (i.e., combining the minutes, statements, and speeches for a meeting into one document).
+
+\subsubsection{Ngrams}
+
+For Ngrams, based on previous research analyzing FOMC transcripts \cite{stanford} with ML models, tri-grams and Naive Bayes performed the best for classifying the outcome of an FOMC meeting.
+In line with that research, we found that N-grams of greater N generally resulted in greater accuracy and lower standard deviation.
+\vertSpace
+
+We observed that the optimal number of Ngrams for Logistic Lasso, Logistic regression, and SVM was between three to seven Ngrams.
+The performance of the three models based on F1 score started to drop significantly with Ngrams greater than seven.
+However, we observed that performance (F1 score) for Naive Bayes increased with larger Ngrams.
+Please refer to charts below for an illustration of the performance (F1 score) of the models with Ngrams between one and ten.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1".pdf}
+\end{center}
+\end{figure}
+
+We observed that the Logistic regression with L1 penalty (i.e.
+Logistic Lasso) performed the best for Ngrams between one and ten and we attribute this to the model being well suited for the binary classification problem.
+We exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.
 \vertSpace
@@
 
-Below is the average accuracy of the four basic classifiers (Naive Bayes, SVM, Logistic Regression, and Logistic Lasso) after 10 iterations:
+\subsubsection{Stacked Documents}
 
-\begin{figure}[h!]
+In our research, we found that reducing the number of features through combining documents for each FOMC meeting into one and increasing Ngram size had a positive impact on accuracy for most of our models.
+\vertSpace
+
+We created and tested 'super features' through stacking documents and increasing Ngrams, and we observed steadily increasing F1 performance for most of our simple models (except Logistic Lasso) and the verious Neural Net models we created.
+Below is a snapshot of the results:
+
+\begin{figure}[H]
 \begin{center}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lass_accuracy_more iterations".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_reg_accuracy_more iterations".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/NB_accuracy_more iterations".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_accuracy_more iterations".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1_stacked".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1_stacked".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1_stacked".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1_stacked".pdf}
 \end{center}
@@
 
-\vspace{5cm}
+\textbf{Neural Network}
 
-\subsection{Feature Choice}
-
-Based on previous research that applied Naive Bayes to analyzing FOMC transcripts \cite{stanford} ML models performed better with N-grams and performance peaked at tri-grams for Naive Bayes.
-In our models, we found that N-grams of greater N saw greater accuracy and lower standard deviation.
-
-\begin{figure}[h!]
+\begin{figure}[H]
 \begin{center}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_20_10_5_f1_stacked".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_40_40_40_f1_stacked".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_40_40_f1_stacked".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_40_f1_stacked".pdf}
+\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/nn_80_f1_stacked".pdf}
 \end{center}
@@
 
-As seen in the graphs above, the Logistic Lasso regression performs the best out of the four basic models.
+\subsection{Neural Network}
 
-\subsection{Neural Network} 
 % Bibliography

### 2019-05-04 presentation/presentation.tex
update

@@
 \usepackage{pgfpages}
+\usepackage{float}
 % citations
 \usepackage{natbib}
+\usepackage{lipsum}
+\usepackage[export]{adjustbox}
+
 \bibpunct{(}{)}{;}{a}{,}{,}
@@
 \begin{frame}
-
-\begin{figure}[h!]
+Federal Open Market Committee (FOMC): Maximum Employment, Stable Inflation, Financial Stability
+\begin{figure}[H]
 \includegraphics[width=1\textwidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
 \end{figure}
+\vspace{-5mm}
 
-\begin{figure}[h!]
+Ngrams (unigrams to 10-grams)
+\vspace{-1mm}
+\begin{figure}[H]
 \begin{center}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
+\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
+\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
 \end{center}
+\end{figure}
+\vspace{-5mm}
+
+Reduced Features (stacked documents, larger Ngrams)
+\vspace{-1mm}
+\begin{figure}[H]
+\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/nn_40_40_f1_stacked".pdf}
+\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/nn_40_f1_stacked".pdf}
+\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/log_lasso_f1_stacked".pdf}
+\includegraphics[width=.2\textwidth]{"../output/data_for_graphs/naive_bayes_f1_stacked".pdf}
 \end{figure}

### 2019-05-04 presentation/presentation.tex
update

--- 2019-05-04 presentation/presentation.tex
@@
 \begin{frame}
-
-\begin{figure}[h!]
+Federal Open Market Committee (FOMC): Maximum Employment, Stable Inflation, Financial Stability
+\vspace{-3mm}
+\begin{figure}[H]
 \includegraphics[width=1\textwidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
 \end{figure}
+\vspace{-5mm}
 
-\begin{figure}[h!]
+Ngrams (unigrams to 10-grams)
+\vspace{-1mm}
+\begin{figure}[H]
 \begin{center}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
+\includegraphics[width=.25\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
+\includegraphics[width=.25\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
 \end{center}
+\end{figure}
+\vspace{-5mm}
+
+Reduced Features (stacked documents, larger Ngrams)
+\vspace{-1mm}
+\begin{figure}[H]
+\includegraphics[width=.22\textwidth]{"../output/data_for_graphs/nn_40_40_f1_stacked".pdf}
+\includegraphics[width=.22\textwidth]{"../output/data_for_graphs/nn_40_f1_stacked".pdf}
+\includegraphics[width=.22\textwidth]{"../output/data_for_graphs/log_lasso_f1_stacked".pdf}
+\includegraphics[width=.22\textwidth]{"../output/data_for_graphs/naive_bayes_f1_stacked".pdf}
 \end{figure}

### 2019-05-05 presentation/equations.tex
add equations

\documentclass[a4paper,12pt]{article}
\usepackage[fleqn]{amsmath}
\usepackage{amsmath}
\begin{document}
\noindent
{\setlength{\mathindent}{0cm}

\noindent \textbf{FOMC Decison $D_t$ based on lagged document text}
\begin{equation*}
E[D_t | \mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}]
\end{equation*}

\noindent \textbf{FOMC Decison $D_t$ based on aggregated lagged document text}
\begin{equation*}
E[D_t | \mbox{AGG}(\mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k})]
\end{equation*}
\noindent where 
\begin{equation*}
D_t = 1, \mbox{if change to rates}
\end{equation*}
\begin{equation*}
D_t = 0, \mbox{if no chagne to rates}
\end{equation*}
\end{document}

### 2019-05-05 presentation/equations.tex
equatinos update

@@
-\documentclass[a4paper,12pt]{article}
+\documentclass[a4paper,11pt]{article}
 \usepackage[fleqn]{amsmath}
 \usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{pgf}
+
+\addtolength{\oddsidemargin}{-.75in} 
+\addtolength{\evensidemargin}{-.75in} 
+\addtolength{\textwidth}{2.5in}
 \begin{document}
@@
 {\setlength{\mathindent}{0cm}
+\noindent \textbf{Predicting FOMC Actions using ML and NLP}\\
 
-\noindent \textbf{FOMC Decison $D_t$ based on lagged document text}
+\noindent \textbf{Jeremy Lao - jjl359, John Reynolds - jr4716}\\
+
+\noindent \textbf{Model1: FOMC Decison $D_t$ based on lagged document text}
 \begin{equation*}
-E[D_t | \mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}]
+E[D_t | \mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}, \mbox{N-gram}]
 \end{equation*}
 
-\noindent \textbf{FOMC Decison $D_t$ based on aggregated lagged document text}
+\noindent \textbf{Model2: FOMC Decison $D_t$ based on aggregated lagged document text}
 \begin{equation*}
-E[D_t | \mbox{AGG}(\mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k})]
+E[D_t | \mbox{AGG}(\mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}), \mbox{N-gram}]
 \end{equation*}
-\noindent where 
-\begin{equation*}
-D_t = 1, \mbox{if change to rates}
-\end{equation*}
-\begin{equation*}
-D_t = 0, \mbox{if no chagne to rates}
-\end{equation*}
+\noindent where $D_t = 1$, if change to rates, $D_t = 0$, if no change.
+
+\begin{figure}[h]
+\includegraphics{./combined.pdf}
+\end{figure}
+
 \end{document}

### 2019-05-05 src/plot_pre.py
added presentation plot

@@ -1,0 +1,78 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+import argparse
+
+
+
+"""
+Compare F1 Scores of the Fits vs NGram Length
+"""
+def compareFits(ax,df, fits, output, range, title=None, xaxis=None):
+    range = int(range) if range is not None  else len(df)
+    for f in fits:
+        ll = df[df["Model Name"] == f]
+        ll = ll[ll["NGramInt"] <= range]
+        x = ll.NGramInt
+        f1 = ll.F1
+        ax.plot(x, f1, marker='o', label='{} F1'.format(f))
+    ax.set_ylabel('F1 Score')
+    ax.set_title(title)
+    if xaxis is not None : ax.set_xlabel(xaxis)
+    ax.legend()
+    
+
+
+def getdf(f):
+    df = pd.read_csv(f)
+    ng = df.NGram.values
+    z = [int(x.split(':')[0]) for x in ng]
+    df["NGramInt"] = z
+    return df
+    
+
+
+if __name__ == '__main__':
+
+    #to see plot
+    #python ./plot_pre.py -i ../output/models_stack.csv ../output/models_nostack.csv -r 40
+
+    # to save plot
+    #python ./plot_pre.py -i ../output/models_stack.csv ../output/models_nostack.csv -r 40 -o ./combined
+
+    parser = argparse.ArgumentParser(description='ML Spring 2019')
+    parser.add_argument('-i','--input', nargs='+',default=None)
+    parser.add_argument('-o','--output', default=None)
+    parser.add_argument('-r','--range', default=None)
+    parser.add_argument('--f0', nargs='+', help= "'svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'", 
+                        default=['logistic_lasso', 'Naive_Bayes','nn_40', 'nn_40_40'])
+    parser.add_argument('--f1', nargs='+', help= "'svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'", 
+                        default=['logistic_lasso', 'Naive_Bayes','svm'])
+    args = parser.parse_args()
+
+    assert len(args.input) == 2
+    d0 = getdf(args.input[0])
+    d1 = getdf(args.input[1])
+    output = args.output
+
+    fig, axs=plt.subplots(2,1, figsize=(6,6))
[…]

### 2019-05-05 presentation/presentation.tex
update
JLs presentation proposal
update presentation slide

--- 2019-05-04 presentation/presentation.tex
@@
 \usepackage{pgfpages}
+\usepackage{float}
 % citations
 \usepackage{natbib}
+\usepackage{lipsum}
+\usepackage[export]{adjustbox}
+\usepackage{subfig}
+
 \bibpunct{(}{)}{;}{a}{,}{,}
@@
 
-\title{Modelling Federal Open Market Committee Decisions Using ML and NLP}
+\title{Predicting FOMC Actions Using ML and NLP}
 
@@
 %\author{F.~Author\inst{1} \and S.~Another\inst{2}}
-\author{Jeremy Lao \& John Reynolds}
+\author{Jeremy Lao - jjl359  \& John Reynolds - jr4716}
 
@@
 
-\date{Date}
+\date{May-7-2019}
 
@@
 \begin{frame}
-\titlepage
-\end{frame}
+\frametitle {Predicting FOMC Actions Using ML and NLP  \\Jeremy Lao - jjl359  \& John Reynolds - jr4716 }
 
-\begin{frame}
+\small \textbf{Model-1: FOMC Decison $D_t$ based on lagged document text}
+\vspace{-2mm}
+\begin{small}
+$$E[D_t | \mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}, \mbox{N-gram}]$$
+\end{small}
+\vspace{-2.5mm}
+\small \textbf{Model-2: FOMC Decison $D_t$ based on aggregated lagged document text}
+\begin{small}
+$$E[D_t | \mbox{AGG}(\mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}), \mbox{N-gram}]$$
+\end{small}
 
-\begin{figure}[h!]
-\includegraphics[width=1\textwidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
-\end{figure}
+\vspace{-7mm}
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
-\end{center}
+\noindent \center {\small where} {$D_t = 1$}{\small, if change to rates,} {$D_t = 0$}{\small, if no change.}
+
+\vspace{-5mm}
+\begin{figure}[h]
+  \subfloat
+   {\includegraphics[width=.5\textwidth]{./model1.jpg}  
+   \hspace{10px}} 
+  \includegraphics[width=.5\textwidth]{./model2.jpg}
+  \captionsetup{labelformat=empty}
+  \caption{x-axis: Ngram, y-axis: F1 Score}
 \end{figure}

### 2019-05-05 presentation/paper.tex
update paper

@@
 
-In our research, we found that reducing the number of features through combining documents for each FOMC meeting into one and increasing Ngram size had a positive impact on accuracy for most of our models.
+In our research, we found that reducing the number of features through combining documents for each FOMC meeting into one and increasing Ngram size had an impact on accuracy for most of our models.
+However, while it improved the performance of Naive Bayes, the net effect (as measured in F1 score) was lower precision and accuracy.
 \vertSpace
 
-We created and tested 'super features' through stacking documents and increasing Ngrams, and we observed steadily increasing F1 performance for most of our simple models (except Logistic Lasso) and the verious Neural Net models we created.
+We created and tested 'super features' through stacking documents and increasing Ngrams, and we observed that F1 score steadily increased for all the simple models (except Logistic Lasso) and the verious Neural Net models we created.
 Below is a snapshot of the results:

### 2019-05-05 src/plot_pre_jl.py
created a copy of plot_pre-graph side by side

@@ -49,15 +49,17 @@ if __name__ == '__main__':
     parser.add_argument('--f1', nargs='+', help= "'svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'", 
                         default=['logistic_lasso', 'Naive_Bayes','svm'])
     args = parser.parse_args()
+    print(len(args.input))
+    print(args.input)
     assert len(args.input) == 2
     d0 = getdf(args.input[0])
     d1 = getdf(args.input[1])
     output = args.output
     
-    fig, axs=plt.subplots(2,1,figsize=(6,6)) 
+    fig, axs=plt.subplots(1,2,figsize=(20,5)) 
     fits0 = [f.replace("_B"," B") for f in args.f0]
     title0 = r'$E[D_t|Agg(St_{t-i}, Min_{t-j}, Sp_{t-k}),NGram]$'
-    compareFits(axs[0],d0, fits0, None, args.range, title0)
+    compareFits(axs[0],d0, fits0, None, args.range, title0, xaxis='NGram Length')
 
 
     fits1 = [f.replace("_B"," B") for f in args.f1]

### 2019-05-05 src/model2_pr.py
fixing model2_pr.py output path

@@ -68,7 +68,7 @@ if __name__ == '__main__':
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     parser.add_argument('--stack', action='store_true', default=False)
     parser.add_argument('--slow', action='store_true', default=False)
-    parser.add_argument('-o','--output', default='../text/data_for_graphs/model2_anagrams.csv')
+    parser.add_argument('-o','--output', default='../output/data_for_graphs/model2_anagrams.csv')
     args = parser.parse_args()
 
     clean_algo = complex_clean if args.cleanAlgo == "complex" else simple_clean

### 2019-05-09 presentation/paper.tex
update
updating paper, adding a plot_pre that has option to print v or h

--- 2019-05-04 presentation/paper.tex
@@
 
-\subsubsection{Basic Model Choice and Performance}
+\subsubsection{Model Choice}
 
-The basic models are Naive Bayes, Logistic Regression, Logistic Lasso, and SVM.
-We tested for model accuracy through averaging various iterations of each model's results, and we empirically tested for the optimal number of bigrams and anagrams.
+To identify the optimal prediction model we developed a simulator that would randomly create a training set and select a test set of meetings that temporally came after the training set: $$E[D_t | \mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}, \mbox{N-gram}]$$
+
+We tested for model accuracy through averaging various iterations of each model's results, we evaluated model performance with F1 scores (precision and recall), and we empirically tested for the optimal number of Ngrams for each model.
 \vertSpace
 
-We found that the general accuracy of each model (for bigrams) peaked at around ten iterations of each model.
-The F1 score, measured as the accuracy of predicting an FOMC move (up = down = 1) with bigrams, also peaks at around 10 iterations per model.
-\vertSpace
-
-Given that the basic models are predicting binary classification we expected the Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform the best.
+Given our binary classification objective, we expected the Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform the best.
 Based on empirical knowledge, FOMC rate moves are analyzed in terms of probabilities and the upcoming meeting is judged primarily on the outcome of Fed action or no action.
@@
 
-Despite some good properties of SVM such as, SVM tend to perform better than logistic regression due to the face that SVMs are less sensitive to outliers and SVM try to maximize the margin between the closest support vectors while LR the posterior class probability.
-SVM generally find a solution which is as fare as possible for the two categories.
-SVM provide prediction of 1 or 0, while the Logistic Regression provides a probability were a probability of 0.501 is enough for the prediction of FOMC rate action.
+Despite some good properties of SVM such as, SVM generally performs better than logistic regression due to the face that SVMs are less sensitive to outliers and SVM try to maximize the margin between the closest support vectors.
+However, becuase SVM provides prediction of 1 or 0 and Logistic Regression provides a probability, where a probability of 0.501 is enough for the prediction of FOMC rate action, Logistic Lasso most closely resembles how an interest rate expert would view FOMC action, a probabilistic approach.
 \vertSpace
 
-In addition, because this is a binary classification problem, we also exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.
+\subsubsection{Feature Choice}
+
+In our search for the optimal model, we tested different strategies for feature selection, namely different size Ngrams and document stacking (i.e., combining the minutes, statements, and speeches for a meeting into one document):
+
+$$E[D_t | \mbox{AGG}(\mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}), \mbox{N-gram}]$$
+
+Document stacking is a basic way to reduce the dimensionality of each meeting's documents, and we thought it would be an appropriate basic strategy to enhance model performance based on research from [footnote].
+\vertSpace
+
+For Ngrams, based on previous research analyzing FOMC transcripts \cite{stanford} with ML models, tri-grams wiht a Naive Bayes model performed the best for classifying the outcome of an FOMC meeting.
+In line with that research, we found that N-grams of greater N generally resulted in greater accuracy and lower standard deviation.
+\vertSpace
+
+\subsection{Model Performance and Results}
+
+Based on our simulation we observed that the Logistic regression with L1 penalty (i.e.
+Logistic Lasso) performed the best for Ngrams between two and ten and we attribute this to the model being well suited for the binary classification problem.
+We exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.
 \vertSpace
@@
 
-Below is the average accuracy of the four basic classifiers (Naive Bayes, SVM, Logistic Regression, and Logistic Lasso) after 10 iterations:
+Below is a picutre of model performance which shows that the Logistic Lasso has the highest F1 $(>90\%)$
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lass_accuracy_more iterations".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_reg_accuracy_more iterations".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/NB_accuracy_more iterations".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_accuracy_more iterations".pdf}
-\end{center}
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{"side-by-side".pdf}
 \end{figure}
 
-\vspace{5cm}
+\subsection{Conclusion}
 
-\subsection{Feature Choice}
+We found that the model results and methodology for simulating training and test data for model and feature selection to be robust.
+Our next recommendation is to utilize this in the production environment and evaluate whether there are trading opportunities when predicting the probability of a move versus the market implied probability from Fed Funds futures.
 
-Based on previous research that applied Naive Bayes to analyzing FOMC transcripts \cite{stanford} ML models performed better with N-grams and performance peaked at tri-grams for Naive Bayes.
-In our models, we found that N-grams of greater N saw greater accuracy and lower standard deviation.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
-\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1".pdf}
-\end{center}
-\end{figure}
-
-As seen in the graphs above, the Logistic Lasso regression performs the best out of the four basic models.
-
-\subsection{Neural Network} 
 % Bibliography

### 2019-05-11 src/model_anlysis.py
add sparse model_analysis

@@ -1,0 +1,181 @@
+import os
+import sys
+import argparse
+import numpy as np
+import pandas as pd
+import datetime
+import bisect
+import re
+from clean import simple_clean
+from clean import complex_clean
+from sklearn.feature_extraction.text import CountVectorizer
+from sklearn.feature_extraction.text import TfidfVectorizer
+from sklearn.metrics import accuracy_score
+from sklearn.svm import LinearSVC
+from sklearn.linear_model import LogisticRegression
+from sklearn.naive_bayes import MultinomialNB
+from sklearn.naive_bayes import BernoulliNB
+from sklearn.naive_bayes import GaussianNB
+from sklearn.naive_bayes import MultinomialNB
+import matplotlib.pyplot as plt
+import csv
+from modelutils import modelutils
+from sklearn.metrics import precision_recall_fscore_support
+import scipy
+
+# this version allows for multiple fit methods (SVM, Logistic, Logistic Lasso)
+# this method also computes the mean and std deviation of the accuracy by
+# this version also allows for ngrams
+# allows the text preprocessing algorithm to be selected
+# running each model Niter Times
+
+# python ./model2_0.py --ngram 1,1 2,2 3,3 1,3 2,3 --Niter 3 --pctTrain .8 --data minutes speeches statements
+
+
+def runModels(models, model_data_set, Nitr, pctTrain, ngram):
+    results, prec,recall,f1, trainPos, testPos=[],[],[],[], np.zeros(Nitr), np.zeros(Nitr)
+    for iter in range(Nitr):
+        train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
+        training_features, test_features = modelutils.getFeatures(train_data, test_data, ngram)
+        norm = scipy.sparse.linalg.norm(training_features)
+        norm_i = scipy.sparse.linalg.norm(training_features, ord=np.inf)
+        (d1, NF) = training_features.get_shape()
+        nz = training_features.count_nonzero()
+        sz = d1*NF
+        sparcity_score =  nz/sz
+        for i, m in enumerate(models):
+            model=m[1]
+            model.fit(training_features, train_data["ActionFlag"])
+            y_pred = model.predict(test_features)
+            acc = accuracy_score(test_data["ActionFlag"], y_pred)
[…]

### 2019-05-11 src/model_anlysis.py
add tfid to modelutils

@@ -32,7 +32,7 @@ import scipy
 # python ./model2_0.py --ngram 1,1 2,2 3,3 1,3 2,3 --Niter 3 --pctTrain .8 --data minutes speeches statements
 
 
-def runModels(models, model_data_set, Nitr, pctTrain, ngram):
+def runModels(models, model_data_set, Nitr, pctTrain, ngram, tfid):
     results, prec,recall,f1, trainPos, testPos=[],[],[],[], np.zeros(Nitr), np.zeros(Nitr)
     for iter in range(Nitr):
         train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
@@ -78,6 +78,7 @@ if __name__ == '__main__':
     parser.add_argument('--data', nargs="+", default=["minutes", "speeches", "statements"])
     parser.add_argument('--stack', action='store_true', default=False)
     parser.add_argument('--slow', action='store_true', default=False)
+    parser.add_argument('--tfid',action='store_true', default=False)
     parser.add_argument('-o','--output', default='../output/data_for_graphs/model2_anagrams.csv')
     args = parser.parse_args()
 
@@ -127,6 +128,9 @@ if __name__ == '__main__':
     else:
         stack="Flase"
 
+    tfid= args.tfid
+    tfidstr= "False" if tfid == False else "True"
+
     
 
     # Train on current minutes
@@ -159,19 +163,19 @@ if __name__ == '__main__':
 
 
     print("Determining Fed Action from minutes")
-    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s %5s %10s %8s %8s %8s %10s %6s" % 
-          ("Model Name", "NGram", "Niter", "mean(acc)", "std(acc)","N","PctTrain", "clean", "start", "end", "Data Sets", "TrainP", "TestP", "Prec", "Recall", "F1", "Stack", "NF", "Norm", "Ratio", "Sparcity", "Size", "NZ"))
+    print("%-20s %5s %5s %10s %10s %5s %8s %7s %10s %10s %-27s %6s %6s %6s %6s %6s %5s %5s %10s %8s %8s %8s %10s %6s" % 
[…]

### 2019-05-11 src/modelutils.py

@@ -165,8 +165,11 @@ class modelutils:
         combined = pd.concat(data_sets) if type(data_sets) is list else data_sets
         return train_test_split(combined, test_size=1.0-train_pct)
 
-    def getFeatures(train_data, test_data, ngram):
-        vectorizer = CountVectorizer(stop_words="english",preprocessor=None, ngram_range=ngram)
+    def getFeatures(train_data, test_data, ngram, Tfid=False):
+        if Tfid :
+            vectorizer = TfidVectorizer(stop_words="english",preprocessor=None, ngram_range=ngram)
+        else:
+            vectorizer = CountVectorizer(stop_words="english",preprocessor=None, ngram_range=ngram)
         training_features = vectorizer.fit_transform(train_data["DocText"])                                 
         test_features = vectorizer.transform(test_data["DocText"])
         return training_features, test_features

### 2019-05-11 src/model_anlysis.py
more changes to model_analysis

@@ -33,7 +33,7 @@ import scipy
 
 
 def runModels(models, model_data_set, Nitr, pctTrain, ngram, tfid):
-    results, prec,recall,f1, trainPos, testPos=[],[],[],[], np.zeros(Nitr), np.zeros(Nitr)
+    results, prec,recall,f1, nonZeroC, trainPos, testPos=[],[],[],[], [], np.zeros(Nitr), np.zeros(Nitr)
     for iter in range(Nitr):
         train_data, test_data = modelutils.splitTrainTest(model_data_set, pctTrain)
         training_features, test_features = modelutils.getFeatures(train_data, test_data, ngram)
@@ -46,6 +46,8 @@ def runModels(models, model_data_set, Nitr, pctTrain, ngram, tfid):
         for i, m in enumerate(models):
             model=m[1]
             model.fit(training_features, train_data["ActionFlag"])
+            C = model.coef_
+            gtZ = len(C[np.abs(C[:]) > 1e-5])
             y_pred = model.predict(test_features)
             acc = accuracy_score(test_data["ActionFlag"], y_pred)
             if iter == 0:
@@ -53,14 +55,16 @@ def runModels(models, model_data_set, Nitr, pctTrain, ngram, tfid):
                 prec.append(np.zeros(Nitr))
                 recall.append(np.zeros(Nitr))
                 f1.append(np.zeros(Nitr))
+                nonZeroC.append(np.zeros(Nitr))
             results[i][iter]=acc
             prec_recall = precision_recall_fscore_support(test_data['ActionFlag'].tolist(), y_pred, average='binary') 
             prec[i][iter] = prec_recall[0]
             recall[i][iter] = prec_recall[1]
             f1[i][iter] = prec_recall[2]
+            nonZeroC[i][iter] = gtZ
         trainPos[iter] = train_data["ActionFlag"].sum()/ len(train_data)
         testPos[iter] = test_data["ActionFlag"].sum()/ len(test_data)
-    return results, trainPos, testPos, prec, recall, f1, NF, norm, nz , sz
+    return results, trainPos, testPos, prec, recall, f1, NF, norm, nz , sz, nonZeroC
                 
 
 if __name__ == '__main__':
[…]

### 2019-05-11 src/model_analysis.py
make sure dir exists

@@ -91,6 +91,8 @@ if __name__ == '__main__':
     pctTrain, cleanA, Niter, ngram = args.pctTrain, args.cleanAlgo, args.Niter, args.ngram
     solver, max_iter, datasetlist = args.solver, args.max_iter, args.data
 
+    assert os.path.isdir(os.path.dirname(args.output))
+
     if len(ngram[0].split(':')) > 1 :
         ngram = ngram[0]
         lb , ub = int(ngram.split(':')[0]), int(ngram.split(':')[1])

### 2019-05-12 src/analysis.py
add module to graph analyze impact of sparsity and matrix size

@@ -1,0 +1,132 @@
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import sys
+import argparse
+
+def save(d1, fname):
+    d1.to_csv(fname, index=False)
+
+def getUnique(d1):
+    # Make Sure No Duplicate Models in DataFrame
+    d1["N"].apply(lambda x : int(x))
+    d1["C"] = [1/float(s.split("Lasso")[-1]) if len(s.split("Lasso")) > 1 else 0 for s in d1["Model Name"].values]
+    d1["id"] = [d1.iloc[i]["Model Name"] + d1.iloc[i]["NGram"] + str(d1.iloc[i]["Stack"]) + str(d1.iloc[i]["Tfid"]) for i in range(len(d1))]
+    d1.set_index("id")
+    d1=d1.drop_duplicates(subset=['id'])
+    d1 = d1.sort_values(by=['F1','Model Name', 'NGram', 'Stack'],ascending=False)
+    return d1
+
+def fixf1(f1, f2, fname="./all_lasso.csv"):
+    d1 = pd.read_csv(f1)
+    d2 = pd.read_csv(f2)
+    d1 = getUnique(d1)
+    d1 = d1[d1["Tfid"] == False]
+    giant=d1.append(d2)
+    giant.drop(columns=['id'])
+    save(giant,fname)
+
+#
+# for the different regularization parameters, get
+# the mean F1 values and regularization strength
+#
+def L1_Impact(d1):
+    # For all of the runs
+    # Group By Model Name - ModelName = Logistic Lasso + <Regularization Parameter>
+    # Note sklearn regularization parameter is 'C', higher C is less regularization
+    # We are graphing based on traditional alpha parameter which is saved in file as 1/C
+    # Get the Mean F1 score for each model
+    # Get L1 Regularization Impact 
+    g=d1.groupby(['Model Name']).agg({
+            'Model Name': [lambda x : ' '.join(x)],
+            'C' :['mean'],
+            'F1':['mean']})
+    mn = g['Model Name']['<lambda>'].values
+    gv = g['F1']['mean'].values
+    cv = g['C']['mean'].values
+    mn =[s.split(" ")[-1] for s in mn]
+    combo=sorted([(m,vx,ci) for m,vx,ci in zip(mn, gv, cv)], key=lambda x : x[2], reverse=False)
+    reg = np.zeros(len(combo))
+    f1 = np.zeros(len(combo))
+    for i,c in enumerate(combo):
[…]

### 2019-05-12 src/analysis.py
updated label on graph

@@ -65,11 +65,11 @@ def PlotL1(f1, output=None):
     xs, ys = L1_Impact(ds)
     
     plt.title('Logistic Lasso Regularization')
-    plt.xlabel('L1 Regularization, larger more regularization')
+    plt.xlabel('L1 Regularization(larger more regularization)')
     plt.ylabel('F1 Score')
 
-    plt.plot(xns[1:],yns[1:], marker='o', label='more sparsity')
-    plt.plot(xs[1:],ys[1:], marker='o', label='less sparsity')
+    plt.plot(xns[1:],yns[1:], marker='o', label='unstacked')
+    plt.plot(xs[1:],ys[1:], marker='o', label='stacked')
     plt.legend()
     if output is not None:
         plt.savefig("{}.pdf".format(output), bbox_inches='tight')

### 2019-05-12 src/analysis.py
added matrix sparsity graphs

@@ -109,6 +109,31 @@ def matrixSize(f1, output=None):
     else:
         plt.show()
 
+def sparse(f1, output=None):
+    d1 = pd.read_csv(f1)
+    ds = d1[d1["Stack"] == True]
+    nfs = ds["NF"].values/1e6
+    svs = ds["sparcity"].values
+    f1s = ds["F1"].values
+    #plt.scatter(sv, f1)
+    plt.scatter(nfs, svs, marker='o', label='stacked')
+
+    dns = d1[d1["Stack"] == False]
+    dns = dns[dns["NGram"] != "1:1"]
+    nfns = dns["NF"].values/1e6
+    svns = dns["sparcity"].values
+    f1ns = dns["F1"].values
+    mx = dns["sparcity"].max()
+    plt.scatter(nfns, svns, marker='x', label='unstacked')
+    plt.legend()
+    plt.title('Number of Features and Matrix Sparcity')
+    plt.xlabel('Number of Features (Millions)')
+    plt.ylabel('Matrix Sparcity')
+    if output is not None:
+        plt.savefig("{}.pdf".format(output), bbox_inches='tight')
+    else:
+        plt.show()
+
 if __name__ == '__main__':
     # to get bar graph of matrix sizes
     # python ./analysis.py -i ../analysis/all_lasso.csv -r size -o [to save to file]
@@ -121,7 +146,7 @@ if __name__ == '__main__':
     parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('-i','--input', default=None)
     parser.add_argument('-o','--output', default=None)
-    parser.add_argument('-r','--run', help='l1 , size', default='l1')
+    parser.add_argument('-r','--run', help='l1 , size, sparse', default='l1')
     args = parser.parse_args()
 
     if args.run == 'l1':
@@ -129,4 +154,6 @@ if __name__ == '__main__':
         PlotL1(args.input, args.output)
     elif args.run == 'size':
         matrixSize(args.input, args.output)
+    elif args.run == 'sparse':
+        sparse(args.input, args.output)
 

### 2019-05-12 src/analysis.py
added NAIVE Bayes Smoothing analysis

@@ -40,18 +40,25 @@ def L1_Impact(d1):
     g=d1.groupby(['Model Name']).agg({
             'Model Name': [lambda x : ' '.join(x)],
             'C' :['mean'],
-            'F1':['mean']})
-    mn = g['Model Name']['<lambda>'].values
-    gv = g['F1']['mean'].values
-    cv = g['C']['mean'].values
-    mn =[s.split(" ")[-1] for s in mn]
-    combo=sorted([(m,vx,ci) for m,vx,ci in zip(mn, gv, cv)], key=lambda x : x[2], reverse=False)
-    reg = np.zeros(len(combo))
-    f1 = np.zeros(len(combo))
-    for i,c in enumerate(combo):
-        reg[i] = c[2]
-        f1[i] = c[1]
-    return reg, f1
+            'F1':['mean','min','max']})
+    nameV = g['Model Name']['<lambda>'].values
+    f1MeanV = g['F1']['mean'].values
+    f1MinV = g['F1']['min'].values
+    f1MaxV = g['F1']['max'].values
+    CV = g['C']['mean'].values
+    namveV =[s.split(" ")[-1] for s in nameV]
+    combo=sorted([(name, ci, f1mean, f1min, f1max, ci) for name, ci, f1mean, f1min, f1max in zip(nameV, CV, f1MeanV, f1MinV, f1MaxV)], 
+                 key=lambda x : x[1], reverse=False)
+    N = len(combo)
+    model = [None]* N
+    param, f1Mean, f1Min, f1Max = np.zeros(N), np.zeros(N), np.zeros(N), np.zeros(N) # 
+    for i, c in enumerate(combo):
+        model = c[0]
+        param[i] = c[1]
+        f1Mean[i] = c[2]
+        f1Min[i] = c[3]
+        f1Max[i] = c[4]
+    return model, param, f1Mean, f1Min, f1Max
 
 #
 # Plot impact of regularization parameter on predicted F1 Score
@@ -59,17 +66,22 @@ def L1_Impact(d1):
 def PlotL1(f1, output=None):
     d1 = pd.read_csv(f1)
     dns = d1[d1["Stack"] == False]
-    xns, yns = L1_Impact(dns)
+    modelns, xns, yns, yns_min, yns_max = L1_Impact(dns)
 
     ds = d1[d1["Stack"] == True]
-    xs, ys = L1_Impact(ds)
+    models, xs, ys, ys_min, ys_max = L1_Impact(ds)
     
[…]

### 2019-05-12 src/analysis.py
changed labels

@@ -30,13 +30,16 @@ def fixf1(f1, f2, fname="./all_lasso.csv"):
 # for the different regularization parameters, get
 # the mean F1 values and regularization strength
 #
-def L1_Impact(d1):
+def ParameterImpact(d1):
     # For all of the runs
-    # Group By Model Name - ModelName = Logistic Lasso + <Regularization Parameter>
-    # Note sklearn regularization parameter is 'C', higher C is less regularization
-    # We are graphing based on traditional alpha parameter which is saved in file as 1/C
-    # Get the Mean F1 score for each model
-    # Get L1 Regularization Impact 
+    # Group By Model Name - ModelName 
+
+    # Logistic Lasso + <Regularization Parameter>
+    # For Logistic Lasso the Inverse Regularization Parameter is 'C' in sklearn
+    
+    # Naive Bayes model names are MultiNB+<smoothing parameter>
+    # For Naive Bayse the Laplace Smoothing Parameter is alpha in sklearn
+
     g=d1.groupby(['Model Name']).agg({
             'Model Name': [lambda x : ' '.join(x)],
             'C' :['mean'],
@@ -66,20 +69,20 @@ def L1_Impact(d1):
 def PlotL1(f1, output=None):
     d1 = pd.read_csv(f1)
     dns = d1[d1["Stack"] == False]
-    modelns, xns, yns, yns_min, yns_max = L1_Impact(dns)
+    modelns, xns, yns, yns_min, yns_max = ParameterImpact(dns)
 
     ds = d1[d1["Stack"] == True]
-    models, xs, ys, ys_min, ys_max = L1_Impact(ds)
+    models, xs, ys, ys_min, ys_max = ParameterImpact(ds)
     
     plt.title('Logistic Lasso Regularization')
     plt.xlabel('L1 Regularization(larger more regularization)')
     plt.ylabel('F1 Score')
 
-    plt.plot(xns[1:],yns[1:], marker='o', label='unstacked-mean')
+    plt.plot(xns[1:],yns[1:], marker='o', label='unstacked-mean F1 score')
     #plt.plot(xns[1:],yns_max[1:], marker='o', label='unstacked-max')
     #plt.plot(xns[1:],yns_min[1:], marker='o', label='unstacked-min')
 
-    plt.plot(xs[1:],ys[1:], marker='o', label='stacked-mean')
[…]

### 2019-05-12 src/analysis.py
sparsity n size analysis

@@ -63,10 +63,17 @@ def ParameterImpact(d1):
         f1Max[i] = c[4]
     return model, param, f1Mean, f1Min, f1Max
 
+
+def showOrSave(output=None):
+    if output is not None:
+        plt.savefig("{}.pdf".format(output), bbox_inches='tight')
+    else:
+        plt.show()
+    
 #
 # Plot impact of regularization parameter on predicted F1 Score
 #    
-def PlotL1(f1, output=None):
+def PlotL1(f1, output=None, showMinMax=False):
     d1 = pd.read_csv(f1)
     dns = d1[d1["Stack"] == False]
     modelns, xns, yns, yns_min, yns_max = ParameterImpact(dns)
@@ -79,17 +86,16 @@ def PlotL1(f1, output=None):
     plt.ylabel('F1 Score')
 
     plt.plot(xns[1:],yns[1:], marker='o', label='unstacked-mean F1 score')
-    #plt.plot(xns[1:],yns_max[1:], marker='o', label='unstacked-max')
-    #plt.plot(xns[1:],yns_min[1:], marker='o', label='unstacked-min')
-
     plt.plot(xs[1:],ys[1:], marker='o', label='stacked-mean F1 score')
-    #plt.plot(xs[1:],ys_min[1:], marker='o', label='stacked-min')
-    #plt.plot(xs[1:],ys_max[1:], marker='o', label='stacked-max')
+
+    if showMinMax :
+        plt.plot(xns[1:],yns_max[1:], marker='o', label='unstacked-max F1')
+        plt.plot(xns[1:],yns_min[1:], marker='o', label='unstacked-min F1')
+        plt.plot(xs[1:],ys_min[1:], marker='o', label='stacked-min F1')
+        plt.plot(xs[1:],ys_max[1:], marker='o', label='stacked-max F1')
+
     plt.legend()
-    if output is not None:
-        plt.savefig("{}.pdf".format(output), bbox_inches='tight')
-    else:
-        plt.show()
+    showOrSave(output)
 
 #
 # Plot the Number of Elements in the Matricies for different NGrams with
@@ -119,10 +125,7 @@ def matrixSize(f1, output=None):
     plt.xlabel("ngrams")
     plt.ylabel("matrix elements (billions)")
     plt.legend()
-    if output is not None:
-        plt.savefig("{}.pdf".format(output), bbox_inches='tight')
-    else:
-        plt.show()
+    showOrSave(output)
 
 def sparse(f1, output=None):
[…]

### 2019-05-13 src/analysis.py
added model ranking

@@ -210,13 +210,34 @@ def performanceSparsity(f1, output=None, f2=None, limit=1.0):
     showOrSave(output)
 
 
-def modelRanking(f1, output=None):
+def modelRanking(f1, output=None, f2=None):
     d1 = pd.read_csv(f1)
     if f2 is not None:
         d2 = pd.read_csv(f2)
-        d2= d2[d2["Tfid"] == True]
         d1 = d1.append(d2)
-    
+    ngram = d1["NGram"].unique()
+    combo = []
+    exclude = ["6:6", "8:8", "10:10", "12:12", "20:20", "4:6", "10:15", "15:15"]
+    for n in ngram:
+        if n in exclude: continue
+        dn = d1[d1["NGram"] == n]
+        ds = dn[dn["Stack"] == True]
+        dns = dn[dn["Stack"] == False]
+        combo.append((n, dns.F1.max(), ds.F1.max()))
+    combo = sorted(combo, key = lambda x : max(x[1],x[2]))
+    label = [c[0] for c in combo]
+    vns    = [c[1] for c in combo]
+    vs   = [c[2] for c in combo]
+    width = 0.15
+    ind = np.arange(len(label)) 
+    plt.bar(ind-width/2, vs, width, label="F1-stacked")
+    plt.bar(ind+width/2, vns, width, label="F1-not-stacked")
+    plt.xticks(ind-width, label)
+    plt.xlabel("NGram")
+    plt.ylabel("F1 Score")
+    plt.title("NGram Model Performance")
+    plt.legend()
+    showOrSave(output)
 
 if __name__ == '__main__':
     # to get bar graph of matrix sizes
@@ -261,4 +282,6 @@ if __name__ == '__main__':
     elif args.run == 'psize':
         performanceMatrixSize(f1, args.output, f2, args.limit)
     elif args.run == 'psparse':
-        performanceSparsity(f1, args.output, f2, args.limit)
+        performanceSparsity(f1, args.output, f2, args.limit) 
+    elif args.run == 'rank':
+        modelRanking(f1, args.output, f2)

### 2019-05-13 src/analysis.py
added comment

@@ -261,6 +261,9 @@ if __name__ == '__main__':
     # Sparsity vs F1
     #python analysis.py -i ../analysis/all_lasso.csv ../analysis/naive.csv -r psparse -l 0.0025 -o SparsityVF1
 
+    # Model Ranking
+    #python analysis.py -i ../analysis/all_lasso.csv ../analysis/naive.csv -r rank -o ModelRanking
+
     parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('-i','--input', nargs='+', default=None)
     parser.add_argument('-o','--output', default=None)

### 2019-05-13 src/analysis.py
added in creating a table

@@ -101,8 +101,12 @@ def PlotL1(f1, output=None, showMinMax=False):
 # Plot the Number of Elements in the Matricies for different NGrams with
 # Stacking and UnStacking Documents
 #   
-def matrixSize(f1, output=None):
+def matrixSize(f1, output=None, f2=None):
     d1 = pd.read_csv(f1)
+    if f2 is not None:
+        d2 = pd.read_csv(f2)
+        d1 = d1.append(d2)
+
     ng = sorted(d1["NGram"].unique(), key = lambda x : int(x.split(':')[0])*10 + int(x.split(':')[1]))
     ds = d1[d1["Stack"] == True]
     dns = d1[d1["Stack"] == False]
@@ -127,7 +131,43 @@ def matrixSize(f1, output=None):
     plt.legend()
     showOrSave(output)
 
-def sparse(f1, output=None):
+#
+# Plot the Number of Elements in the Matricies for different NGrams with
+# Stacking and UnStacking Documents
+#   
+def matrixSparse(f1, output=None, f2=None):
+    d1 = pd.read_csv(f1)
+    if f2 is not None:
+        d2 = pd.read_csv(f2)
+        d1 = d1.append(d2)
+    sparse_min = d1.sparcity.min()
+    ng = sorted(d1["NGram"].unique(), key = lambda x : int(x.split(':')[0])*10 + int(x.split(':')[1]))
+    ds = d1[d1["Stack"] == True]
+    dns = d1[d1["Stack"] == False]
+    label, nf_ns, nf_s = [], [], []
+    skip = ['8:8', '12:12', '15:15'] # remove a couple of ngrams ot make it fit nicely on x axis
+    skip = []
+    for i in range(len(ng)):
+        dxs = ds[ds['NGram'] == ng[i]]
+        dxns = dns[dns['NGram'] == ng[i]]
+        if len(dxs) == 0 or len(dxns) == 0: continue
+        if ng[i] in skip : continue
+        label.append(ng[i])
+        nf_ns.append(dxns.sparcity.mean())
+        nf_s.append(dxs.sparcity.mean())
+    ind = np.arange(len(label)) 
+    width = 0.15
+    plt.title('NGram Sparsity')
+    plt.bar(ind-width/2,nf_s, width, label='stacked')
+    plt.bar(ind+width/2,nf_ns, width, label='unstacked')
[…]

### 2019-05-13 src/plot_pre_jl.py
updating paper.tex

@@ -2,7 +2,7 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 import argparse
-
+import sys
 
 
 """
@@ -43,30 +43,42 @@ if __name__ == '__main__':
     parser = argparse.ArgumentParser(description='ML Spring 2019')
     parser.add_argument('-i','--input', nargs='+',default=None)
     parser.add_argument('-o','--output', default=None)
+    parser.add_argument('-d','--direction', default='h')
     parser.add_argument('-r','--range', default=None)
     parser.add_argument('--f0', nargs='+', help= "'svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'", 
                         default=['logistic_lasso', 'Naive_Bayes','nn_40', 'nn_40_40'])
     parser.add_argument('--f1', nargs='+', help= "'svm', 'logistic_lasso', 'Naive_Bayes', 'logistic'", 
                         default=['logistic_lasso', 'Naive_Bayes','svm'])
     args = parser.parse_args()
-    print(len(args.input))
-    print(args.input)
     assert len(args.input) == 2
     d0 = getdf(args.input[0])
     d1 = getdf(args.input[1])
     output = args.output
     
-    fig, axs=plt.subplots(1,2,figsize=(20,5)) 
-    fits0 = [f.replace("_B"," B") for f in args.f0]
-    title0 = r'$E[D_t|Agg(St_{t-i}, Min_{t-j}, Sp_{t-k}),NGram]$'
-    compareFits(axs[0],d0, fits0, None, args.range, title0, xaxis='NGram Length')
+    if args.direction not in ['h','v']:
+      sys.exit("--direction is either 'v' or 'h'")
+    elif args.direction == 'h':
+      fig, axs=plt.subplots(1,2,figsize=(20,5)) 
+      fits0 = [f.replace("_B"," B") for f in args.f0]
+      title0 = r'$E[D_t|Agg(St_{t-i}, Min_{t-j}, Sp_{t-k}),NGram]$'
+      compareFits(axs[0],d0, fits0, None, args.range, title0, xaxis='NGram Length')
 
+      fits1 = [f.replace("_B"," B") for f in args.f1]
+      title1 = r'$E[D_t|St_{t-i}, Min_{t-j}, Sp_{t-k},NGram]$'
[…]

### 2019-05-13 presentation/paperv2.tex
paperv2

--- 2019-05-09 presentation/paper.tex
@@
 % AMS packages:
+\usepackage[fleqn]{amsmath}
 \usepackage{amsmath, amsthm, amsfonts}
@@
 
-%-----------------------------------------------------------------
-\title{Predicting FOMC Actions using ML and NLP}
+%----------------------------------------------------------------
+\title{Predicting FOMC Actions using NLP; Assesing the impact of matrix sparsity and regularization}
 \author{
@@
 \begin{document}
+{\setlength{\mathindent}{0cm}
 \maketitle
@@
 The Federal Funds rate is one of the primary monetary policy tools, and it impacts the cost of borrowing money globally.
-This paper explores ML and NLP methods to predict the potential outcome of an upcoming FOMC using past FOMC statements and meeting minutes to train ML and NLP models.}}
+This paper explores ML and NLP methods, examines the impact of matrix sparsity from NLP methods and regularization from ML models, to predict the potential outcome of an upcoming FOMC using past FOMC statements and meeting minutes to train ML and NLP models.}}
 
 \section{Introduction}
-In this paper we methods in Natural Language Processing (NLP) and Machine Learning (ML) to predict Federal Open Market Committee (FOMC) rate actions (hold or change) using text from FOMC meeting minutes, Board of Governors speeches, and FOMC post-meeting statements.
-Since this is work in sentiment analysis we created a simulator to gain insight into the sensitiviy of detecting sentiment by randomly generating words with from a mix of distributions containing hawkish or dovish(positive) words, negative words, and commonly used words.
-That simulator showed accuracy could hit levels of 100 percent given enough training data and high percentage of sentiment (i.e., positive)  words to overall text.
+In this paper we use methods in Natural Language Processing (NLP) and Machine Learning (ML) to predict Federal Open Market Committee (FOMC) rate actions (hold or change) using text from FOMC meeting minutes, Board of Governors speeches, and FOMC post-meeting statements.
+For this analysis we used 713 separate documents (rougly 1.6 Million Words) and 148 Fed Decisions for our data set.  
+Employing NLP techniques can result in large numbers of features being generated and an extremly sparse resultant feature matrix.  
+In the analysis we conducted some of the feature matricies generated contained over 2 Billion elements with fractions as small as 0.0025 of the elements containing a non-zero value.  
+Our analysis and techniques used were driven by the issue of feature sizes orders of magnitued larger than the label size and the extreme degrees of sparsness in the feature matrix.  
+To make sure the analysis was at least plausible we created a simulator to detect positive or negative sentiment from randomly generated text and found as the number of sentiment words increased the prediction accuracy approached close to 1.0.
+For the study the analysis hones in on the mix of distributions containing hawkish or dovish(positive) words.
+
+\subsection{git repository for project}
+\url{https://www.github.com/jrrpanix/ML9}
+
+\section{Objective}
+\begin{enumerate}
+\item Since its pretty easy to just blindly apply tools to a set of data we wanted to understand the 
+characteristics of the output from the text processing functions (in our case CountVectorizer) in terms of number of features, matrix sparsity, matrix norm
+that are generated from calls to this function.
+\item Assess the effeiveness of Bayesian Approaches and Regularization on the analysis.
+\item Determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate).
+\item Because 70$\%$ of the actions are ``no action'', make sure the prediction is not always just ``no action'' (which would give a 70$\%$ accuracy).
+\end{enumerate}
+
+\section{Methodology}
+
+\subsection{Data}
+
+The time frame of our study covered 2000 to 2018. 
+We primarily utilized three sources for our data, FOMC statements, FOMC meeting minutes and Boarde of Governors speeches.
+Details on datasources, extraction and scrubbing are left to the appendix to keep the focus on the methods and results.
+Preparing the data was a large amount of work and we are not aware of any data sets that combine the three types of documents
+and then map the documents to a Fed Action.
+
+\subsection{Feature Modeling and Data Label Mapping}
+\noindent Documents are mapped to the first rate decision on or before the document date at time $ti$
+where $j=\text{Statement}$ or $j=\text{Speech}$ or $j=\text{Minutes}$
+\begin{equation*}
+\mbox{Document}_{j,ti} \rightarrow \mbox{Decision}_{ti+k}
+ = \begin{cases}
+  1, & \text{if  Decision = change}, \\
+  0, & \text{if  Decision = no change}
+\end{cases}
+\end{equation*}
+
+\noindent 
+\textbf{Model 1: Unstacked}\\
+\noindent
+The \textbf{Unstacked} model maps each document to a feature vector generated by CountVector given an n-gram($n_1$, $n_2$)
+where $n_1 <= n_2$ and $n_i$ are integers $>0$. Given there are approximately 713 documents, this will generate
+a feature matrix with 713 rows and $K$ columns where each column will be and instance of the word sequence
+generated by the n-gram.
+
+\begin{equation*}
+E[D_ti] = f(ngram(n_1, n_2)[\mbox{Document}_{j,ti-k}])
+\end{equation*}
+
+\noindent
+\textbf{Model 2: Stacked}\\
+The \textbf{Stacked}  model maps the set of documents which occurr after the previous decision date but on or before the
+next decision date to one rate decision.  This has the effect of contatenating the documents between decisions into
+one large document, but cuts down the number from 713 to 148.
+where $n_1 <= n_2$ and $n_i$ are integers $>0$. Given there are approximately 713 documents, this will generate
+a feature matrix with 713 rows and $K$ columns where each column will be and instance of the word sequence
+generated by the n-gram.
+
+\begin{equation*}
+E[D_{ti}] = f(ngram(n_1, n_2)[\mbox{Document}_{j1,ti-k1},{Document}_{j2,ti-k2},...]) \text{, } ti-1 < ti-ki < ti+1
+\end{equation*}
+
+\subsection{Matrix Sizes and Sparsity from CountVector}
+\noindent For this study we used \textbf{CountVector} (\textbf{TfiDf} can also be used, but it did not alter the conclustions of this study).
+When are n-gram is applied to corpus it combinatorics diticates a large number of features will be generated and for a given feature, most of the column entries will
+be zero, resulting in extremly sparse matricies.  The table below gives a measure of $\mbox{sparsity} = \frac{non-zero elements}{total elements}$ and 
+the resulting number of elements in each n-gram generated matrix in the billions. In general stacking reduces the sparsity by a factor of 4 and
+the matrix size by a factor of 5.\\
+
+\noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
+ \hline
+ \multicolumn{5}{|c|}{CountVector Matrix Size} \\
+ \hline
+ \multicolumn{1}{|c|}{} &
+ \multicolumn{2}{|c|}{Unstacked} &
+ \multicolumn{2}{|c|}{Stacked}\\
+ \hline
+ N-gram & sparsity & size(billions) & sparsity & size(billions)\\
+ \hline
+       1:1& 0.03628801& 0.008561&  0.10635940&   0.001757 \\
+       1:2& 0.00544312& 0.170058&  0.02081416&    0.036107\\
+       1:3& 0.00368457& 0.439898&  0.01508941&     0.092869\\
+       3:5& 0.00238128& 0.900721&  0.01059293&     0.173040\\
+       4:7& 0.00224699& 1.332560&  0.00996789&     0.271117\\
+      5:10& 0.00218455& 1.995502&  0.00972276&     0.402041\\
+      8:10& 0.00213633& 1.019811&  0.00955894&     0.198627\\
+     10:15& 0.00210643& 2.097187&  0.00945586&     0.398312\\
+     20:20& 0.00205055& 0.347043&  0.00931157&     0.074799\\
+ \hline
+\end{tabular}
+
+\section{Conclusion}
+
+We found that the model results and methodology for simulating training and test data for model and feature selection to be robust.
+Our next recommendation is to utilize this in the production environment and evaluate whether there are trading opportunities when predicting the probability of a move versus the market implied probability from Fed Funds futures.
+
+\appendix
+\section{Appendix}
 
@@
 
-\section{Objective}
-
-The aim of our research is to determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate).  Our models approached this question in two steps:
-
-\begin{enumerate}
-
- \item We test the accuracy of ML models trained on a random mixture of FOMC minutes, speeches, and statements on a test set of FOMC documents.
-In this stage, we are determining the viability of ML methods in predicting FOMC action on test documents, and we will evaluate the model accuracy with precision and recall.
-The models are:
- \begin{itemize}
-    \item Naive Bayes
-    \item Logistic Regression 
-    \item SVM
-    \item Logistic Lasso
- \end{itemize}
- \item We create a predictive model that is trained on documents that are temporally released before the test document.
-Typically we will test with FOMC minutes releases or Board of Governor speeches that are temporally released after the training documents.
- \item  To determine the appropriate feature vector size, for example, concatenate the documents associated with a meeting or treat each document separately, we simulated how sentiment analysis performs as the feature vector becomes larger.
- \item  We applied Latent Dirichlet Allocation to the entire corpus of speeches and assumed $k=3$ latent topics to explore whether LDA captures the Federal Reserve's mandates of: maximum employment, stable prices, and financial stability.
-\end{enumerate}
-
-\section{Methodology}
-
 \subsection{Data}
 
-We primarily utilized three sources for our data, they are outlined below. \vertSpace
-
+\subsubsection{Data Sources}
 The time frame of our study covered 2000 to 2018.  
-The primary source of our textual data were FOMC statements, FOMC meeting minutes, and Board of Governors speeches from \url{www.federalreserve.gov}.
+The primary source of our textual data were FOMC statements, FOMC meeting minutes, and Board of Governors speeches from \url{https://www.federalreserve.gov}.  
 For FOMC statements between 2000 and 2008 we utilized Stanford's FOMC corpus.  
 The Stanford FOMC corpus only has text prior to 2008 and it does not have Board of Governor speeches.
+The data for the Federal Funds target rate and target range (post 2009) is from FRED St. Louis.  
+FRED offers a wealth of economic data and information to promote economic education and enhance economic research. 
+FRED is updated regularly and allows 24/7 access to regional and national financial and economic data.
+
+\subsubsection{Scraping and Text Pre-Processing}
+
+We collected data from the Federal Reserve website and pre-processed the data for the document-term matrix. \vertSpace
+
+We utilized Python packages \textit{beautifulsoup4}, \textit{re}, and \textit{urllib} to scrape contextual data from the Federal Reserve website.
+Our scraping algorithm used regular expressions to handle and remove extraneous \textit{html} and \textit{javascript} text collected by the page scraper.
+We had to handle non UTF-8 characters upfront and remove them at this stage altogether.
+We collected over six hundred documents from the Federal Reserve website.
 \vertSpace
 
-The data for the Federal Funds target rate and target range (post 2009) is from FRED St.
-Louis.
-FRED offers a wealth of economic data and information to promote economic education and enhance economic research.
-FRED is updated regularly and allows 24/7 access to regional and national financial and economic data.
-\vspace{5mm}
+After scraping the data, we pre-processed the text by removing all punctuation, ensuring proper spacing between words, setting all words to lower case, and making all numbers \textit{d} to reduce the dimensionality document-term matrix.
+We also used Regex to detect direct references to the Federal Funds target rate/range and transformed those references (a mixture of numbers, punctuation, and the word 'percent') to \textit{ddpercentrate}.
+Since we were modeling the sentiment of FOMC rate action, this was one of our strategies to directly capture the target rate in the document-term matrix.
+\vertSpace
 
+This formed the bulk of our text pre-processing and it allowed us to essentially utilize the stored text in the document-term matrix for NLP and ML models.
+
+\subsubsection{Meta-Data}
 \noindent Below is a table of the FOMC document metadata:
@@
 
-\subsection{Scraping and Text Pre-Processing}
-
-We collected data from the Federal Reserve website and pre-processed the data for the document-term matrix. \vertSpace
-
-We utilized Python packages \textit{beautifulsoup4}, \textit{re}, and \textit{urllib} to scrape contextual data from the Federal Reserve website.
-Our scraping algorithm used regular expressions to handle and remove extraneous \textit{html} and \textit{javascript} text collected by the page scraper.
-We had to handle non UTF-8 characters upfront and remove them at this stage altogether.
-We collected over six hundred documents from the Federal Reserve website.
-\vertSpace
-
-After scraping the data, we pre-processed the text by removing all punctuation, ensuring proper spacing between words, setting all words to lower case, and making all numbers \textit{d} to reduce the dimensionality document-term matrix.
-We also used Regex to detect direct references to the Federal Funds target rate/range and transformed those references (a mixture of numbers, punctuation, and the word 'percent') to \textit{ddpercentrate}.
-Since we were modeling the sentiment of FOMC rate action, this was one of our strategies to directly capture the target rate in the document-term matrix.
-\vertSpace
-
-This formed the bulk of our text pre-processing and it allowed us to essentially utilize the stored text in the document-term matrix for NLP and ML models.
-
-\subsection{Models}
-
-\subsubsection{Latent Dirichlet Allocation}
+\subsection{Latent Dirichlet Allocation}
 
@@
 
-\subsubsection{Supervised Models}
-
-We utilized the following models in our research:
-
-  \begin{itemize}
-
-    \item Naive Bayes
-
-      $$P(A|x_1,x_2,...,x_n) = p(A)\prod_{i=1}^n p(x_i|A)$$
-
-    \item Logistic Regression
-
-     $$A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}$$
-
-    \item Logistic Lasso
-     $$A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}+ L1$$
-    \item SVM
-
-     $$\left [\frac{1}{n} \sum_{i=1}^n max(0,1 - y_i(\vec{w} \dot \vec{x_i} - b)) \right] + \lambda ||\vec{w}||^2$$
-    \item Neural Network
-      We test a mixture of wide and deep neural nets. 
-  \end{itemize}
-
-\subsubsection{Model Choice}
-
-To identify the optimal prediction model we developed a simulator that would randomly create a training set and select a test set of meetings that temporally came after the training set: $$E[D_t | \mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}, \mbox{N-gram}]$$
-
-We tested for model accuracy through averaging various iterations of each model's results, we evaluated model performance with F1 scores (precision and recall), and we empirically tested for the optimal number of Ngrams for each model.
-\vertSpace
-
-Given our binary classification objective, we expected the Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform the best.
-Based on empirical knowledge, FOMC rate moves are analyzed in terms of probabilities and the upcoming meeting is judged primarily on the outcome of Fed action or no action.
-\vertSpace
-
-Despite some good properties of SVM such as, SVM generally performs better than logistic regression due to the face that SVMs are less sensitive to outliers and SVM try to maximize the margin between the closest support vectors.
-However, becuase SVM provides prediction of 1 or 0 and Logistic Regression provides a probability, where a probability of 0.501 is enough for the prediction of FOMC rate action, Logistic Lasso most closely resembles how an interest rate expert would view FOMC action, a probabilistic approach.
-\vertSpace
-
-\subsubsection{Feature Choice}
-
-In our search for the optimal model, we tested different strategies for feature selection, namely different size Ngrams and document stacking (i.e., combining the minutes, statements, and speeches for a meeting into one document):
-
-$$E[D_t | \mbox{AGG}(\mbox{Statements}_{t-i}, \mbox{Minutes}_{t-j} , \mbox{Speeches}_{t-k}), \mbox{N-gram}]$$
-
-Document stacking is a basic way to reduce the dimensionality of each meeting's documents, and we thought it would be an appropriate basic strategy to enhance model performance based on research from [footnote].
-\vertSpace
-
-For Ngrams, based on previous research analyzing FOMC transcripts \cite{stanford} with ML models, tri-grams wiht a Naive Bayes model performed the best for classifying the outcome of an FOMC meeting.
-In line with that research, we found that N-grams of greater N generally resulted in greater accuracy and lower standard deviation.
-\vertSpace
-
-\subsection{Model Performance and Results}
-
-Based on our simulation we observed that the Logistic regression with L1 penalty (i.e.
-Logistic Lasso) performed the best for Ngrams between two and ten and we attribute this to the model being well suited for the binary classification problem.
-We exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.
-\vertSpace
-
-Given that we are modelling a classification problem, we would expect the performance of the Logistic Lasso model based on the mathematical properties of Logistic Lasso more robust for predicting FOMC rate action.
-Logistic regression models the probability distribution of the class label $y$ given a feature vector $x$:
-
-$$p(y=1|x,\theta) = \sigma(\theta^T x) = \frac{1}{1+\exp(-\theta^Tx)}$$
-
-The L1 regularized logistic regression (Logistic Lasso) is defined as:
-
-$$\underset{\rm \theta}{\rm min} \sum_{i=1}^M -\log p(y^{(i)}|x^{(i)}; \theta) + \beta ||\theta||$$
-
-L1 regularization has the effect of forcing feature selection, and as we observe the Logistic Lasso model performs best with Tri-grams to 7-grams while the F1 measure significantly drops with larger Ngrams.
-\vertSpace
-
-Below is a picutre of model performance which shows that the Logistic Lasso has the highest F1 $(>90\%)$
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{"side-by-side".pdf}
-\end{figure}
-
-\subsection{Conclusion}
-
-We found that the model results and methodology for simulating training and test data for model and feature selection to be robust.
-Our next recommendation is to utilize this in the production environment and evaluate whether there are trading opportunities when predicting the probability of a move versus the market implied probability from Fed Funds futures.
-
 % Bibliography
@@
 \bibitem{stanford} Puri, Indira \emph{Using Machine Learning to Predict Interest Rate Changes from Federal Reserve Proceedings}
+
+\bibitem{nyu} Ranganath, Rajesh  \emph{NYU - CSCI-GA.2565 ML Lecture Slides Spring 2019}
 \end{thebibliography}

### 2019-05-13 presentation/paperv2.tex
more edits to v2

@@
 \subsection{Matrix Sizes and Sparsity from CountVector}
-\noindent For this study we used \textbf{CountVector} (\textbf{TfiDf} can also be used, but it did not alter the conclustions of this study).
+
+\noindent For this study we used \textbf{CountVectorizer} (\textbf{TfiDf} can also be used, but it did not alter the conclustions of this study).
 When are n-gram is applied to corpus it combinatorics diticates a large number of features will be generated and for a given feature, most of the column entries will
@@
 the resulting number of elements in each n-gram generated matrix in the billions. In general stacking reduces the sparsity by a factor of 4 and
-the matrix size by a factor of 5.\\
+the matrix size by a factor of 5. The L1 matrix norm for all of the matricies ranged between 1200 to 1600.\\
 
@@
 
+\subsection{Apply ML to Sparse Matricies generated from CountVectorizer}
+<TODO>
+
 \section{Conclusion}
-
-We found that the model results and methodology for simulating training and test data for model and feature selection to be robust.
-Our next recommendation is to utilize this in the production environment and evaluate whether there are trading opportunities when predicting the probability of a move versus the market implied probability from Fed Funds futures.
+Reducing the sparsity of the matricies generated from CountVectorizer by stacking the documents greatly improved the results.
+We were able to attain maximum test accuracy of 95.9$\%$ using a 10:15 n-gram with a recall of 93.4$\%$ and an F1 score of 92.5$\%$.
+Because of the number of features generated can be in the millions, Logistic Lasso with small penatly proved to be the most effective 
+means of eliminating the large number of the coefficients. 
+The fraction of non-zero coefficients remaining after applying logistic lasso
+would range between 3e-05 to 1.6e-03.  (Compared to .97 with no regularization using logistic regression).
+Logistic regression and Logistic Lasso both broke down at extreme levels of sparsity 
+(2.5e-03). 
+MultiNomial Naive Bayes with Laplace smoothing at zero proved to be the most stable method for producing useful results at the
+most extreme measures of matrix sparcity.  In general no smoothing or large smoothing proved to give the best results with
+MultiNomial Naive Bayes.
 

### 2019-05-13 presentation/paperv2.tex
v2

@@
 \noindent For this study we used \textbf{CountVectorizer} (\textbf{TfiDf} can also be used, but it did not alter the conclustions of this study).
-When are n-gram is applied to corpus it combinatorics diticates a large number of features will be generated and for a given feature, most of the column entries will
+When an n-gram is applied to corpus combinatorics diticates a large number of features will be generated and for a given feature, most of the column entries will
 be zero, resulting in extremly sparse matricies.  The table below gives a measure of $\mbox{sparsity} = \frac{non-zero elements}{total elements}$ and 
@@
 \subsection{Apply ML to Sparse Matricies generated from CountVectorizer}
-<TODO>
+\noindent
+For this problem the large feature size relative to the the number of labels dicitates looking
+at Bayesian approach or some from of L1 regularization (HW1 problem 2) to push a large number
+of coefficients to zero.
+\begin{itemize}
+
+\item Naive Bayes
+\begin{equation*}
+P(A|x_1,x_2,...,x_n) = p(A)\prod_{i=1}^n p(x_i|A)
+\end{equation*}
+
+\item Logistic Lasso
+\begin{equation*}
+A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}+ L1
+\end{equation*}
+
+\end{itemize}
 

### 2019-05-13 presentation/paperv2.tex
added table

@@
 \begin{itemize}
-
 \item Naive Bayes
@@
 \end{equation*}
+\end{itemize}
 
-\end{itemize}
+\noindent 
+For \textbf{Logistic Lasso} we are interested in examining the impact of the regularization parameter on
+the fraction of  non-zero coefficients remaining after regularization is applied and on the impact of the predictive
+score on test data. \\
+
+\noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
+ \hline
+ \multicolumn{6}{|c|}{Comparision of Logistic Lasso with different regularization} \\
+ \hline
+ \multicolumn{1}{|c|}{} &
+ \multicolumn{1}{|c|}{} &
+ \multicolumn{2}{|c|}{Unstacked} &
+ \multicolumn{2}{|c|}{Stacked}\\
+ \hline
+ N-gram & $\alpha$ & F1 & frac remain & F1 & frac remain\\
+ \hline
+
+10:15 &  3.333 & 0.454 & 0.000040 & 0.720 & 0.000016 \\
+10:15 &  2.000 & 0.575 & 0.000066 & 0.897 & 0.000029 \\
+10:15 &  1.000 & 0.647 & 0.000148 & 0.893 & 0.000055 \\
+10:15 &  0.500 & 0.679 & 0.000291 & 0.913 & 0.000094 \\
+10:15 &  0.200 & 0.708 & 0.000339 & 0.913 & 0.000134 \\
+10:15 &  0.100 & 0.710 & 0.000463 & 0.923 & 0.000161 \\
+10:15 &  0.050 & 0.711 & 0.000619 & 0.925 & 0.000206 \\
+10:15 &  0.020 & 0.715 & 0.000764 & 0.923 & 0.000243 \\
+10:15 &  0.010 & 0.713 & 0.001045 & 0.913 & 0.000315 \\
+10:15 &  0.002 & 0.730 & 0.001659 & 0.906 & 0.000517 \\
+10:15 &  0.000 & 0.669 & 0.978049 & 0.669 & 1.000000 \\
+ \hline
+\end{tabular}
 

### 2019-05-13 presentation/paperv2.tex
v2

@@
 
+\subsubsection{The impact of regularization coefficient $\alpha$ on logistic regression}
 \noindent 
-For \textbf{Logistic Lasso} we are interested in examining the impact of the regularization parameter on
+For \textbf{Logistic Lasso} we are interested in examining the impact of the regularization parameter $\alpha$ on
 the fraction of  non-zero coefficients remaining after regularization is applied and on the impact of the predictive
-score on test data. \\
+score on test data. The results show the regularization parameter at the extremes produces the worst results
+and the stacked model has a higher fraction of coefficients eliminated from logistic lasso. The expected result
+is the larger regularization parameter reduces the fraction of non-zero coefficients.\\
 
@@
  \hline
- \multicolumn{6}{|c|}{Comparision of Logistic Lasso with different regularization} \\
+ \multicolumn{6}{|c|}{Comparision of Logistic Lasso varying regularization coefficient $\alpha$} \\
  \hline

### 2019-05-13 presentation/paperv2.tex
v2

@@
 
+\subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with extrem sparse Matricies}
+
 \section{Conclusion}
@@
 Because of the number of features generated can be in the millions, Logistic Lasso with small penatly proved to be the most effective 
-means of eliminating the large number of the coefficients. 
+method for reducing the number of coefficients.
 The fraction of non-zero coefficients remaining after applying logistic lasso
-would range between 3e-05 to 1.6e-03.  (Compared to .97 with no regularization using logistic regression).
+ranged between 3e-05 to 1.6e-03.  (Compared to .97 with no regularization using logistic regression).
 Logistic regression and Logistic Lasso both broke down at extreme levels of sparsity 
 (2.5e-03).
+In general the Regularization parameter at the extremes produced inferior results.
 MultiNomial Naive Bayes with Laplace smoothing at zero proved to be the most stable method for producing useful results at the

### 2019-05-13 presentation/paperv2.tex
v2

@@
 that are generated from calls to this function.
-\item Assess the effeiveness of Bayesian Approaches and Regularization on the analysis.
+\item Assess the effeiveness of Multinomial Niave Bayes and Logistic Lasso applied to problmes where the feature size is orders of magnitues larger than the label size.
 \item Determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate).
@@
 \end{itemize}
+
+\subsubsection{Training, Testing and Determining the efficacy of the Models}
+For this study we randomly sample 75$\%$ of the corpus for training and then 
+predict Fed action using the ramining 25$\%$ of the data and calculate
+\begin{itemize}
+\item Accuracy
+\item Precision
+\item Recall
+\item F1 Score
+\end{itemize}
+Approximately 70$\%$ of the time there is no Action so a model that does nothing will
+have an accuracy of 70$\%$, but a recall of 0.  The results are summarized using F1
+score.
 

### 2019-05-13 presentation/paperv2.tex
v2

@@
 \subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with extrem sparse Matricies}
+We noticed that under extreme levels of sparseness from the Matricies generated by CountVectorizer ,
+both Logistic Lasso and Logistic Regression would break down, while Multinomial Naive Bayes would produce
+usable results. Matricies with a sparseness measure of less than $0.003$ would cause the results for 
+Logistic Lasso to deteriorate.
 

### 2019-05-13 presentation/paperv2.tex
v2

--- 2019-05-13 presentation/paperv2.tex
@@
 \subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with extrem sparse Matricies}
+We noticed that under extreme levels of sparseness (sparseness measure of less than $0.003$) from the Matricies 
+generated by CountVectorizer , Logistic Regression and Logistic Lasso with larger regularization parameters would break down, 
+while Multinomial Naive Bayes would produce usable results. Logistic Lasso with $\alpha=0.002$ seemed to hold up
+well even under extreme sparsness.
 
@@
 ranged between 3e-05 to 1.6e-03.  (Compared to .97 with no regularization using logistic regression).
-Logistic regression and Logistic Lasso both broke down at extreme levels of sparsity 
+Logistic regression ($\alpha > 0.05$) and Logistic Lasso both broke down at extreme levels of sparsity 
 (2.5e-03).
@@
 most extreme measures of matrix sparcity.  In general no smoothing or large smoothing proved to give the best results with
-MultiNomial Naive Bayes.
+MultiNomial Naive Bayes. Overall Logistic Lasso with $\alpha = 0.002$ produced the most stable results.
 

### 2019-05-14 src/analysis.py
analysis

@@ -7,24 +7,18 @@ import argparse
 def save(d1, fname):
     d1.to_csv(fname, index=False)
 
-def getUnique(d1):
-    # Make Sure No Duplicate Models in DataFrame
-    d1["N"].apply(lambda x : int(x))
-    d1["C"] = [1/float(s.split("Lasso")[-1]) if len(s.split("Lasso")) > 1 else 0 for s in d1["Model Name"].values]
-    d1["id"] = [d1.iloc[i]["Model Name"] + d1.iloc[i]["NGram"] + str(d1.iloc[i]["Stack"]) + str(d1.iloc[i]["Tfid"]) for i in range(len(d1))]
-    d1.set_index("id")
-    d1=d1.drop_duplicates(subset=['id'])
-    d1 = d1.sort_values(by=['F1','Model Name', 'NGram', 'Stack'],ascending=False)
-    return d1
-
-def fixf1(f1, f2, fname="./all_lasso.csv"):
-    d1 = pd.read_csv(f1)
-    d2 = pd.read_csv(f2)
-    d1 = getUnique(d1)
-    d1 = d1[d1["Tfid"] == False]
-    giant=d1.append(d2)
-    giant.drop(columns=['id'])
-    save(giant,fname)
+def colC(d1):
+    if "C" in d1.columns : return 
+    names = d1["Model Name"].values
+    nv = []
+    for s in names:
+        if "Lasso" in s:
+            v = float(s.split("Lasso")[-1]) if len(s.split("Lasso")) > 1 else 0
+            if v != 0 : v = 1/v
+        else:
+            v = float(s.split("MultiNB")[-1]) if len(s.split("MultiNB")) > 1 else 0
+        nv.append(v)
+    d1["C"] = nv
 
 #
 # for the different regularization parameters, get
@@ -39,7 +33,6 @@ def ParameterImpact(d1):
     
     # Naive Bayes model names are MultiNB+<smoothing parameter>
     # For Naive Bayse the Laplace Smoothing Parameter is alpha in sklearn
-
     g=d1.groupby(['Model Name']).agg({
             'Model Name': [lambda x : ' '.join(x)],
             'C' :['mean'],
@@ -75,6 +68,7 @@ def showOrSave(output=None):
 #    
 def PlotL1(f1, output=None, showMinMax=False):
     d1 = pd.read_csv(f1)
[…]

### 2019-05-14 presentation/paperv3.tex
paper v3, editing

--- 2019-05-13 presentation/paperv2.tex
@@
 \section{Introduction}
-In this paper we use methods in Natural Language Processing (NLP) and Machine Learning (ML) to predict Federal Open Market Committee (FOMC) rate actions (hold or change) using text from FOMC meeting minutes, Board of Governors speeches, and FOMC post-meeting statements.
+In this paper we use Natural Language Processing (NLP) and Machine Learning (ML) methods to predict Federal Open Market Committee (FOMC) rate actions (hold or change) using text from FOMC meeting minutes, Board of Governors speeches, and FOMC post-meeting statements.
+\vertSpace
+
 For this analysis we used 713 separate documents (rougly 1.6 Million Words) and 148 Fed Decisions for our data set.
-Employing NLP techniques can result in large numbers of features being generated and an extremly sparse resultant feature matrix.  
-In the analysis we conducted some of the feature matricies generated contained over 2 Billion elements with fractions as small as 0.0025 of the elements containing a non-zero value.  
-Our analysis and techniques used were driven by the issue of feature sizes orders of magnitued larger than the label size and the extreme degrees of sparsness in the feature matrix.  
-To make sure the analysis was at least plausible we created a simulator to detect positive or negative sentiment from randomly generated text and found as the number of sentiment words increased the prediction accuracy approached close to 1.0.
-For the study the analysis hones in on the mix of distributions containing hawkish or dovish(positive) words.
+We employ the NLP bag-of-words model for our analysis.
+Bag-of-words models have high dimensionality, meaning the space is extremely sparse with a large amount of features leading to a sparse feature matrix.
+We found in our analysis that some of the feature matricies contained over two billion elements with as little as $0.25\%$ of the elements containing a non-zero value.
+\vertSpace
+
+Due to these modelling challenges, the analysis and techniques we used address the issue of features being magnitudes larger than the label size ($p>>n$), and the extreme sparsity in the feature matrix.
+In order to determine the appropriate model, n-gram size, and model parameters, we created a simulator to detect positive or negative sentiment from randomly generated text.
+\vertSpace
+
+Our model simulator found that as the number of sentiment words increased, the prediction accuracy approached close to 1.0 with high F1 scores.
+For the study the analysis hones in on the mix of distributions containing hawkish or dovish (positive-action) words.
 
@@
 
-\section{Objective}
+\section{Objectives}
 \begin{enumerate}
-\item Since its pretty easy to just blindly apply tools to a set of data we wanted to understand the 
-characteristics of the output from the text processing functions (in our case CountVectorizer) in terms of number of features, matrix sparsity, matrix norm
-that are generated from calls to this function.
-\item Assess the effeiveness of Multinomial Niave Bayes and Logistic Lasso applied to problmes where the feature size is orders of magnitues larger than the label size.
-\item Determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate).
-\item Because 70$\%$ of the actions are ``no action'', make sure the prediction is not always just ``no action'' (which would give a 70$\%$ accuracy).
+\item Given the proliferation of robust open-source ML and NLP packages, we were driven to understand the characteristics of the feature matrix output (i.e., document-term matrix) from the text processing functions (i.e., CountVectorizer) analyzing the number of features, matrix sparsity, and matrix norm generated from utilizing packages functions.
+\item Assess the effeiveness of Multinomial Niave Bayes and Logistic Lasso applied to problems where the feature size is orders of magnitues larger than the label size ($p>>n$).
+\item Determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate) using FOMC statements, minutes, and Board of Governors speeches.
+\item Measure model performance on F1 scores because $70\%$ of the actions over the nineteen year period we are measuring are ``no action''.
+F1 scores ensure that the accuracy of the model is not based purely on a naive ``no action'' guess, which in the best case would give a $70\%$ model accuracy.
 \end{enumerate}
@@
 The time frame of our study covered 2000 to 2018.
-We primarily utilized three sources for our data, FOMC statements, FOMC meeting minutes and Boarde of Governors speeches.
-Details on datasources, extraction and scrubbing are left to the appendix to keep the focus on the methods and results.
-Preparing the data was a large amount of work and we are not aware of any data sets that combine the three types of documents
-and then map the documents to a Fed Action.
+We primarily utilized three sources for our data, FOMC statements, FOMC meeting minutes, and Boarde of Governors speeches.
+Details on datasources, extraction and scrubbing are left to the appendix to focus this paper on analyzing our methods and results.
+Preparing the data was a large amount of work and we are not aware of any data sets that combine the three types of documents and mapped the documents to an FOMC Action.
 
 \subsection{Feature Modeling and Data Label Mapping}
-\noindent Documents are mapped to the first rate decision on or before the document date at time $ti$
-where $j=\text{Statement}$ or $j=\text{Speech}$ or $j=\text{Minutes}$
+\noindent Documents are mapped to the first rate decision on or before the document date at time $t_i$, where $j=\text{Statement}$ or $j=\text{Speech}$ or $j=\text{Minutes}$
+
 \begin{equation*}
-\mbox{Document}_{j,ti} \rightarrow \mbox{Decision}_{ti+k}
+\mbox{Document}_{j,t_i} \rightarrow \mbox{Decision}_{t_i+k}
  = \begin{cases}
@@
 \noindent
-The \textbf{Unstacked} model maps each document to a feature vector generated by CountVector given an n-gram($n_1$, $n_2$)
-where $n_1 <= n_2$ and $n_i$ are integers $>0$. Given there are approximately 713 documents, this will generate
-a feature matrix with 713 rows and $K$ columns where each column will be and instance of the word sequence
-generated by the n-gram.
+The \textbf{Unstacked} model maps each document to a feature vector generated by CountVector given an n-gram ($n_1$, $n_2$) where $n_1 <= n_2$ and $n_i$ are integers $>0$.
+Given that our corpus consisted of approximately 713 documents, this will generate a feature matrix with 713 rows and $K$ columns where each column will be a unique instance of the word sequence generated by the n-gram.
 
 \begin{equation*}
-E[D_ti] = f(ngram(n_1, n_2)[\mbox{Document}_{j,ti-k}])
+E[D_{t_i}] = f(ngram(n_1, n_2)[\mbox{Document}_{j,t_i-k}])
 \end{equation*}
@@
 \textbf{Model 2: Stacked}\\
-The \textbf{Stacked}  model maps the set of documents which occurr after the previous decision date but on or before the
-next decision date to one rate decision.  This has the effect of contatenating the documents between decisions into
-one large document, but cuts down the number from 713 to 148.
-where $n_1 <= n_2$ and $n_i$ are integers $>0$. Given there are approximately 713 documents, this will generate
-a feature matrix with 713 rows and $K$ columns where each column will be and instance of the word sequence
-generated by the n-gram.
+The \textbf{Stacked} model maps the set of documents which occurr after the previous decision date but on or before the next decision date to one rate decision.
+We effectively concatenated the documents between decisions into one large document.
+The ``stacked'' model reduces the number of documents from 713 to 148, and we expect this method to reduce the dimensionality of the space.
+This model maintains the same n-gram based feature vector where $n_1 <= n_2$ and $n_i$ are integers $>0$.
 
 \begin{equation*}
-E[D_{ti}] = f(ngram(n_1, n_2)[\mbox{Document}_{j1,ti-k1},{Document}_{j2,ti-k2},...]) \text{, } ti-1 < ti-ki < ti+1
+E[D_{t_i}] = f(ngram(n_1, n_2)[\mbox{Document}_{j_1,t_i-k_1},{Document}_{j_2,t_i-k_2},...]) \text{, } t_i-1 < t_i-k_i < t_i+1
 \end{equation*}
@@
 
-\noindent For this study we used \textbf{CountVectorizer} (\textbf{TfiDf} can also be used, but it did not alter the conclustions of this study).
-When an n-gram is applied to corpus combinatorics diticates a large number of features will be generated and for a given feature, most of the column entries will
-be zero, resulting in extremly sparse matricies.  The table below gives a measure of $\mbox{sparsity} = \frac{non-zero elements}{total elements}$ and 
-the resulting number of elements in each n-gram generated matrix in the billions. In general stacking reduces the sparsity by a factor of 4 and
-the matrix size by a factor of 5. The L1 matrix norm for all of the matricies ranged between 1200 to 1600.\\
+\noindent For this study we used term frequencies generated from \textbf{CountVectorizer} (\textbf{TfiDf} can also be used, but it did not alter the conclusions of this study).
+When an n-gram is applied to a corpus of documents $D$, one can deduce from basic combinatorics that a large number of features will be generated from various mixtures of case studies.
+\vertSpace
+
+As we mentioned in our introduction, the classic problem with NLP bag-of-words models is that most of the column entries (n-grams) are zero, resulting in extremly sparse matricies.
+The table below gives a measure of $\mbox{sparsity} = \frac{non-zero elements}{total elements}$ and the resulting number of elements in each n-gram generated matrix (units are in billions).
+We empirically observed that the ``stacked'' model reduces the sparsity by a factor of four and the matrix size by a factor of five.
+The L1 matrix norm for all of the matricies ranged between 1200 to 1600.\\
 

### 2019-05-14 presentation/paperv3.tex
updating paper v3

@@
 \noindent
-For this problem the large feature size relative to the the number of labels dicitates looking
-at Bayesian approach or some from of L1 regularization (HW1 problem 2) to push a large number
-of coefficients to zero.
+Based upon research into classification models for sparse data, we chose to test Naive Bayes and Logistic Regression with L1 regularization.  \vertSpace
+
 \begin{itemize}
@@
 \end{itemize}
+
+For the ``Unstacked'' document case, our research into classification model performance on sparse data, found that Naive Bayes classification models performed particularly well when encountering cases of missing data.
+Naive Bayes takes advantage of the assumption that the attributes are independent and ignores missing attributes when calculating the probability.
+Therefore, Naive Bayes is generally considered a fairly decent performer with greater sparsity.
+\vertSpace
+
+Based on the table above called ``Count Vector Size'', we decided to test Logistic Lasso as we found in our research that Logistic Lasso can handle sparsity well through identifying a set of relevant variables out of the large collection of candidates making it suitable for discovering interactions in regresssion problems (HW1 problem 2).
+\vertSpace
 
@@
 \bibitem{nyu} Ranganath, Rajesh  \emph{NYU - CSCI-GA.2565 ML Lecture Slides Spring 2019}
+
+\bibitem{NaiveBayes} Li, Xiang et al. \emph{The Convergence Behavior of Naive Bayes on Large Sparse Datasets}, ACM Vol 11 Issue 1, August 2016
+
+\bibitem{LL} Zou, Yuan and Roos, Teemu \emph{Sparse Logistic Regression with Logical Features}, Helsinki Institute for Information Technology (HIIT), Springer International, 2016
 \end{thebibliography}
-
 \end{document}

### 2019-05-14 presentation/paperv3.tex
edits to paper v3
update paper

@@
 
-\subsection{Matrix Sizes and Sparsity from CountVector}
+\subsection{Matrix Sizes and Sparsity from CountVectorizer}
 
@@
 As we mentioned in our introduction, the classic problem with NLP bag-of-words models is that most of the column entries (n-grams) are zero, resulting in extremly sparse matricies.  
-The table below gives a measure of $\mbox{sparsity} = \frac{non-zero elements}{total elements}$ and the resulting number of elements in each n-gram generated matrix (units are in billions).
+Sparsity is defined as
+\begin{equation*}
+\mbox{sparsity} = \frac{\mbox{non-zero elements}}{\mbox{total elements}}
+\end{equation*}
+
+The table below gives a measure of sparsity  and the resulting number of elements in each n-gram generated matrix (units are in billions).
 We empirically observed that the ``stacked'' model reduces the sparsity by a factor of four and the matrix size by a factor of five.
@@
 \subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with extrem sparse Matricies}
-We noticed that under extreme levels of sparseness (sparseness measure of less than $0.003$) from the Matricies 
-generated by CountVectorizer , Logistic Regression and Logistic Lasso with larger regularization parameters would break down, 
-while Multinomial Naive Bayes would produce usable results. Logistic Lasso with $\alpha=0.002$ seemed to hold up
-well even under extreme sparsness.
+Under extreme levels of sparseness (sparseness measure of less than $0.0021$) from  Matricies 
+generated by CountVectorizer , Logistic Regression and Logistic Lasso break down while
+while Multinomial Naive Bayes can still produce usable results. Logistic Lasso with relaitvely low penatly 
+$\alpha=0.002$ functions as well or better than Naive Bayes when sparseness exceeded $0.0025$.
+Logistic Lasso with a larger penalty $> 2.0$ does not performe will with extremley sparse matricies. \\
+
+\noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
+ \hline
+
+ \multicolumn{5}{|c|}{Deterioration of Logistic Lasso with sparse matricies relative to Naive Bayes} \\
+ \hline
+ \multicolumn{1}{|c|}{} &
+ \multicolumn{1}{|c|}{} &
+ \multicolumn{3}{|c|}{F1 Score} \\
+
+ \hline
+ \multicolumn{1}{|c|}{} &
+ \multicolumn{1}{|c|}{} &
+ \multicolumn{1}{|c|}{Naive Bayes} &
+ \multicolumn{2}{|c|}{Logistic Lasso} \\
+
+ \hline
+ \multicolumn{1}{|c|}{N-gram} &
+ \multicolumn{1}{|c|}{sparsity} &
+ \multicolumn{1}{|c|}{smooth$=0.0$} &
+ \multicolumn{1}{|c|}{$\alpha=0.002$} &
+ \multicolumn{1}{|c|}{$\alpha=1.000$} \\
+ \hline
+ 60& 0.001979 & 0.647 & 0.463 & 0.256\\
+ 50& 0.002018 & 0.619 & 0.565 & 0.342\\
+ 30& 0.002038 & 0.724 & 0.620 & 0.460\\
+ 25& 0.002063 & 0.720 & 0.664 & 0.490\\
+ 20& 0.002067 & 0.725 & 0.678 & 0.520\\
+ 12& 0.002069 & 0.682 & 0.743 & 0.656\\
+ \hline
+\end{tabular}
 
@@
 ranged between 3e-05 to 1.6e-03.  (Compared to .97 with no regularization using logistic regression).
-Logistic regression ($\alpha > 0.05$) and Logistic Lasso both broke down at extreme levels of sparsity 
-(2.5e-03).
-In general the Regularization parameter at the extremes produced inferior results.
-MultiNomial Naive Bayes with Laplace smoothing at zero proved to be the most stable method for producing useful results at the
+Logistic regression  and Logistic Lasso both broke down at the most extreme levels of sparsity $<0.0020$ 
+In general Regularization parameters at the extremes ($\alpha=0.0$ or $\alpha > 2.0$) produced inferior results.
+MultiNomial Naive Bayes with Laplace smoothing$=0$ was the most stable method for producing useful results at the
 most extreme measures of matrix sparcity.  In general no smoothing or large smoothing proved to give the best results with
@@
 The primary source of our textual data were FOMC statements, FOMC meeting minutes, and Board of Governors speeches from \url{https://www.federalreserve.gov}.  
-For FOMC statements between 2000 and 2008 we utilized Stanford's FOMC corpus.  
-The Stanford FOMC corpus only has text prior to 2008 and it does not have Board of Governor speeches.
 The data for the Federal Funds target rate and target range (post 2009) is from FRED St. Louis.  

### 2019-05-14 presentation/paperv3.tex
paper
edits and adding plot for paper-v3

@@
 F1 scores ensure that the accuracy of the model is not based purely on a naive ``no action'' guess, which in the best case would give a $70\%$ model accuracy.
+\item Create scraping and cleaning tools to assemble a corpus of documents containing Speeches, Statements, Minutes and Actions from the Federal Reserve.
 \end{enumerate}
@@
 
-\noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
+\noindent 
+\begin{center}
+\begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
  \hline
@@
 \end{tabular}
+\end{center}
 
@@
 
-\subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with extrem sparse Matricies}
-Under extreme levels of sparseness (sparseness measure of less than $0.0021$) from  Matricies 
-generated by CountVectorizer , Logistic Regression and Logistic Lasso break down while
-while Multinomial Naive Bayes can still produce usable results. Logistic Lasso with relaitvely low penatly 
-$\alpha=0.002$ functions as well or better than Naive Bayes when sparseness exceeded $0.0025$.
-Logistic Lasso with a larger penalty $> 2.0$ does not performe will with extremley sparse matricies. \\
+\subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with Extremely Sparse Feature Matrices}
+\noindent
+Under extreme levels of sparseness (sparseness measure of less than $0.0021$) from feature matrices generated by CountVectorizer, Logistic Regression and Logistic Lasso break down with greater sparseness while Multinomial Naive Bayes can still produce usable results.
+\vertSpace
 
+However, we found with less matrix sparsity and a lower Logistic Lasso model penalty (i.e., $\alpha=0.002$), the Logistic Lasso model performance improves.
+Based on F1 scores we observed that Logistic Lasso with low penalties performs as well or better than Naive Bayes when sparseness exceeded $0.0025$.
+\vertSpace
+
+Logistic Lasso with a larger penalty $>2.0$ does not perform will with extremely sparse matricies. \\
+\begin{center}
 \noindent \begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|  }
@@
 \end{tabular}
+\end{center}
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{../output/analysis/unstacked-nb-ll.JPG}
+  \caption{F1 performance of LL and NB - Unstacked Model}
+\end{figure}
 
 \section{Conclusion}
-Reducing the sparsity of the matricies generated from CountVectorizer by stacking the documents greatly improved the results.
-We were able to attain maximum test accuracy of 95.9$\%$ using a 10:15 n-gram with a recall of 93.4$\%$ and an F1 score of 92.5$\%$.
-Because of the number of features generated can be in the millions, Logistic Lasso with small penatly proved to be the most effective 
-method for reducing the number of coefficients.
-The fraction of non-zero coefficients remaining after applying logistic lasso
-ranged between 3e-05 to 1.6e-03.  (Compared to .97 with no regularization using logistic regression).
-Logistic regression  and Logistic Lasso both broke down at the most extreme levels of sparsity $<0.0020$ 
-In general Regularization parameters at the extremes ($\alpha=0.0$ or $\alpha > 2.0$) produced inferior results.
-MultiNomial Naive Bayes with Laplace smoothing$=0$ was the most stable method for producing useful results at the
-most extreme measures of matrix sparcity.  In general no smoothing or large smoothing proved to give the best results with
-MultiNomial Naive Bayes. Overall Logistic Lasso with $\alpha = 0.002$ produced the most stable results.
+Reducing the sparsity of the matricies generated from CountVectorizer by stacking the documents greatly improved the results.  \vertSpace
+
+We were able to attain maximum test accuracy of $95.9\%$ using a $10:15$ n-gram, producing a recall of $93.4\%$ and an F1 score of $92.5\%$.
+Because of the large number (i.e., millions) of features in the feature matrix, Logistic Lasso with small penatly proved to be the most effective method for reducing the number of coefficients, leading to improved F1 scores.
+\vertSpace
+
+The fraction of non-zero coefficients remaining after applying Logistic Lasso ranged between $3e-05$ to $1.6e-03$.
+Logistic Lasso was very effective in dealing with feature matrix sparsity, and based on what we learned from HW1 question two is the appropriate model choice for our classification problem.
+In order to illustrate the effectiveness, we measured the fraction of non-zero coefficients using a Logistic Regression model and the feature matrix had $\approx 97\%$ non-zero coefficients.
+\vertSpace
+
+Logistic Lasso (and Logistic Regression generally) broke down at the most extreme levels of sparsity $<0.0020$.
+In general, we found that setting the regularization parameters at the extremes ($\alpha=0.0$ or $\alpha > 2.0$) produced inferior results.
+\vertSpace
+
+Whereas Multinomial Naive Bayes with Laplace smoothing $=0$ was the most stable method for producing useful results at the most extreme measures of matrix sparcity.
+In general we found that when using Multinomial Naive Bayes setting the parameters at no smoothing or large smoothing proved to give the best results.
+\vertSpace
+
+Overall our research found that Logistic Lasso with $\alpha = 0.002$ produced the most stable results for predicting FOMC rate decisions from FOMC statements, minutes, and Board of Governors speeches.
 

### 2019-05-14 src/analysis.py
mod analysis

@@ -59,7 +59,9 @@ def ParameterImpact(d1):
 
 def showOrSave(output=None):
     if output is not None:
-        plt.savefig("{}.pdf".format(output), bbox_inches='tight')
+        #plt.savefig("{}.pdf".format(output), bbox_inches='tight')
+        #plt.savefig("{}.jpg".format(output), bbox_inches='tight', rasterized=True, dpi=80)
+        plt.savefig("{}.pdf".format(output), bbox_inches='tight', rasterized=True, dpi=50)
     else:
         plt.show()
     
@@ -329,7 +331,87 @@ def table2(f1, output=None, f2=None):
                    dxns.iloc[j].F1, min(dxns.iloc[j].NonZeroCoeff, 1.0),
                    dxs.iloc[j].F1, min(dxs.iloc[j].NonZeroCoeff, 1.0)))
                   
-    
+
+def table3(f1, output=None, f2=None, limit=None, ngramON=True, plot=True):
+    # python ./analysis.py -i ../output/sparse.csv -r table3 -o ngramlen_nb_ll
+    limit = limit if limit is not None else 1e12
+    d1 = pd.read_csv(f1)
+    if f2 is not None:
+        d2 = pd.read_csv(f2)
+        d1 = d1.append(d2)
+    d1 = d1[d1["Stack"] == False]
+    colC(d1)
+    models = d1["Model Name"].unique()
+    keep = ["Logistic Lasso500.0","Logistic Lasso1.0","MultiNB0.0"]
+    keep = ["Logistic Lasso1.0","MultiNB0.0"]
+    dm = pd.concat([d1[d1["Model Name"] == m] for m in keep])
+    ngram = dm[dm["Model Name"] == "MultiNB0.0"].NGram.unique()
+    scores = []
+    for n in ngram:
+        dn = dm[dm["NGram"] == n]
+        if len(dn) != 3 : continue
+        fv = [dn[dn["Model Name"] == model].iloc[0].F1 for model in keep]
+        fv.append(dn[dn["Model Name"] == keep[-1]].iloc[0].sparcity)
+        fv.append(int(n.split(':')[-1]))
+        scores.append(fv)
+    scores = sorted(scores , key = lambda x : x[-2], reverse=False)
+    for s in scores:
+        sp = s[-2]
+        if sp > limit : break
+        print ("%3d& %8.6f & %5.3f & %5.3f & %5.3f\\\\" % ( s[-1], s[-2], s[2], s[0], s[1]))
+
+    if not plot : return
[…]

### 2019-05-14 presentation/MLPaper.tex
added MLPaper for submission

--- 2019-05-14 presentation/paperv3.tex
@@
 \end{center}
+\vertSpace
+\noindent Below is a plot showing Naive Bayes giving consistent results relative
+to Logistic Lasso .
 
 \begin{figure}[h!]
-  \includegraphics[width=\linewidth]{../output/analysis/unstacked-nb-ll.JPG}
+  \centering
+  \includegraphics[width=100mm]{./ngramlen_nb_ll.pdf}
   \caption{F1 performance of LL and NB - Unstacked Model}
 \end{figure}
+
+\subsubsection{Impact of N-gram sequences on results}
+We varied the N-gram sequences to observe its impact on out of sample prediction.  There is a definite range of N-gram sequences where all of the models greatly improved. 
+All of the models showed great improvement when the n-gram sequences ranged between 4:6 and 10:15.  As the sequences started getting larger than 20 words, the results
+started to fall off as Feature matricies became more sparse.  Below is a graph of various both Logistic Lasso and Naive Bayes plotted for
+different regularizaion coefficients while varying the N-gram sequence.  The interesting part about this is Federal Reserve commentary tends to have sequences
+of hawkish or dovish sentiment which can't be expressed in a few words which might be the reason why smaller n-gram sequences did not perform as well.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=100mm]{./ngram_seq.pdf}
+  \caption{N-gram sequence LL and NB - Stacked Model}
+\end{figure}
+\vfill
+
+\vertSpace
 
@@
 
+We found that n-gram sequences of varying between 4:7 to 10:15 provided the best results.
+Smaller n-gram sequences ($< 4$ words) and larger sequences ($>20$ do to extreme sparsity) did not generate good results.
+
 Whereas Multinomial Naive Bayes with Laplace smoothing $=0$ was the most stable method for producing useful results at the most extreme measures of matrix sparcity.
@@
 
-Overall our research found that Logistic Lasso with $\alpha = 0.002$ produced the most stable results for predicting FOMC rate decisions from FOMC statements, minutes, and Board of Governors speeches.
+Overall our research found that Logistic Lasso with smaller penalty $\alpha < 0.02$ produced the most stable results for predicting FOMC rate decisions from FOMC statements, minutes, and Board of Governors speeches.
+
+The limitation in this study is the size of the data sets.
+While we were able to identify charactersistics that would help predictive power the strength of the conclusions are tempered by the amount of data on hand.
 

### 2019-05-14 presentation/MLPaper.tex
update

--- 2019-05-14 presentation/paperv3.tex
@@
 %----------------------------------------------------------------
-\title{Predicting FOMC Actions using NLP; Assesing the impact of matrix sparsity and regularization}
+\title{Predicting FOMC Actions Using NLP; Assessing the Impact of Matrix Sparsity and Regularization}
 \author{
@@
 
-For this analysis we used 713 separate documents (rougly 1.6 Million Words) and 148 Fed Decisions for our data set.
+For this analysis we used 713 separate documents (roughly 1.6 Million Words) and 148 Fed Decisions for our data set.
 We employ the NLP bag-of-words model for our analysis.
 Bag-of-words models have high dimensionality, meaning the space is extremely sparse with a large amount of features leading to a sparse feature matrix.
-We found in our analysis that some of the feature matricies contained over two billion elements with as little as $0.25\%$ of the elements containing a non-zero value.
+We found in our analysis that some of the feature matrices contained over two billion elements with as little as $0.25\%$ of the elements containing a non-zero value.
 \vertSpace
 
-Due to these modelling challenges, the analysis and techniques we used address the issue of features being magnitudes larger than the label size ($p>>n$), and the extreme sparsity in the feature matrix.
+Due to these modeling challenges, the analysis and techniques we used address the issue of features being magnitudes larger than the label size ($p>>n$), and the extreme sparsity in the feature matrix.
 In order to determine the appropriate model, n-gram size, and model parameters, we created a simulator to detect positive or negative sentiment from randomly generated text.
@@
 \begin{enumerate}
-\item Given the proliferation of robust open-source ML and NLP packages, we were driven to understand the characteristics of the feature matrix output (i.e., document-term matrix) from the text processing functions (i.e., CountVectorizer) analyzing the number of features, matrix sparsity, and matrix norm generated from utilizing packages functions.
-\item Assess the effeiveness of Multinomial Niave Bayes and Logistic Lasso applied to problems where the feature size is orders of magnitues larger than the label size ($p>>n$).
+\item Given the proliferation of robust open-source ML and NLP packages, we were motivated to understand the characteristics of the feature matrix output (i.e., document-term matrix) from the text processing functions (i.e., CountVectorizer) analyzing the number of features, matrix sparsity, and matrix norm generated from utilizing package functions.
+\item Assess the effectiveness of Multinomial Naive Bayes and Logistic Lasso applied to problems where the feature size is orders of magnitudes larger than the label size ($p>>n$).
 \item Determine whether ML and NLP methods can be used to predict FOMC action (no change or a change in the base rate) using FOMC statements, minutes, and Board of Governors speeches.
@@
 The time frame of our study covered 2000 to 2018.
-We primarily utilized three sources for our data, FOMC statements, FOMC meeting minutes, and Boarde of Governors speeches.
-Details on datasources, extraction and scrubbing are left to the appendix to focus this paper on analyzing our methods and results.
+We primarily utilized three sources for our data, FOMC statements, FOMC meeting minutes, and Board of Governors speeches.
+Details on data-sources, extraction and scrubbing are left to the appendix to focus this paper on analyzing our methods and results.
 Preparing the data was a large amount of work and we are not aware of any data sets that combine the three types of documents and mapped the documents to an FOMC Action.
@@
 \subsection{Feature Modeling and Data Label Mapping}
-\noindent Documents are mapped to the first rate decision on or before the document date at time $t_i$, where $j=\text{Statement}$ or $j=\text{Speech}$ or $j=\text{Minutes}$
+\noindent Documents are mapped to the first FOMC rate decision on or before the document date at time $t_i$, where $j=\text{Statement}$ or $j=\text{Speech}$ or $j=\text{Minutes}$
 
@@
 
-\begin{equation*}
-E[D_{t_i}] = f(ngram(n_1, n_2)[\mbox{Document}_{j,t_i-k}])
-\end{equation*}
+$$E[D_{t_i}] = f(ngram(n_1, n_2)[\mbox{Document}_{j,t_i-k}])$$
 
@@
 \textbf{Model 2: Stacked}\\
-The \textbf{Stacked} model maps the set of documents which occurr after the previous decision date but on or before the next decision date to one rate decision.
+The \textbf{Stacked} model maps the set of documents which occur after the previous decision date but on or before the next decision date to one rate decision.
 We effectively concatenated the documents between decisions into one large document.
@@
 
-\begin{equation*}
-E[D_{t_i}] = f(ngram(n_1, n_2)[\mbox{Document}_{j_1,t_i-k_1},{Document}_{j_2,t_i-k_2},...]) \text{, } t_i-1 < t_i-k_i < t_i+1
-\end{equation*}
+$$E[D_{t_i}] = f(ngram(n_1, n_2)[\mbox{Document}_{j_1,t_i-k_1},{Document}_{j_2,t_i-k_2},...]) \text{, } t_i-1 < t_i-k_i < t_i+1$$
 
@@
 
-As we mentioned in our introduction, the classic problem with NLP bag-of-words models is that most of the column entries (n-grams) are zero, resulting in extremly sparse matricies.  
-Sparsity is defined as
-\begin{equation*}
-\mbox{sparsity} = \frac{\mbox{non-zero elements}}{\mbox{total elements}}
-\end{equation*}
+As we mentioned in our introduction, the classic problem with NLP bag-of-words models is that most of the column entries (n-grams) are zero, resulting in extremely sparse matrices.  
+Sparsity is defined as:
+
+$$\mbox{sparsity} = \frac{\mbox{non-zero elements}}{\mbox{total elements}}$$
 
@@
 We empirically observed that the ``stacked'' model reduces the sparsity by a factor of four and the matrix size by a factor of five.
-The L1 matrix norm for all of the matricies ranged between 1200 to 1600.\\
+The L1 matrix norm for all of the matrices ranged between 1200 to 1600.\\
 
@@
 
-\subsection{Apply ML to Sparse Matricies generated from CountVectorizer}
+\subsection{Apply ML to Sparse Matrices generated from CountVectorizer}
 \noindent
@@
 
-For the ``Unstacked'' document case, our research into classification model performance on sparse data, found that Naive Bayes classification models performed particularly well when encountering cases of missing data.
+For the ``Unstacked'' document case, our research into classification model performance on sparse data found that Naive Bayes classification models performed particularly well when encountering cases of missing data.
 Naive Bayes takes advantage of the assumption that the attributes are independent and ignores missing attributes when calculating the probability.
@@
 
-Based on the table above called ``Count Vector Size'', we decided to test Logistic Lasso as we found in our research that Logistic Lasso can handle sparsity well through identifying a set of relevant variables out of the large collection of candidates making it suitable for discovering interactions in regresssion problems (HW1 problem 2).
+Based on the table above called ``Count Vector Size'', we decided to test Logistic Lasso as we found in our research that Logistic Lasso can handle sparsity through identifying a set of relevant variables out of the large collection of candidates making it suitable for discovering interactions in regression problems (HW1 problem 2).
 \vertSpace
 
-\subsubsection{Training, Testing and Determining the efficacy of the Models}
+\subsubsection{Training, Testing, and Determining the Efficacy of the Models}
 For this study we randomly sample 75$\%$ of the corpus for training and then 
-predict Fed action using the ramining 25$\%$ of the data and calculate
+predict Fed action using the remaining 25$\%$ of the data and calculate
 \begin{itemize}
@@
  \hline
- \multicolumn{6}{|c|}{Comparision of Logistic Lasso varying regularization coefficient $\alpha$} \\
+ \multicolumn{6}{|c|}{Comparison of Logistic Lasso varying regularization coefficient $\alpha$} \\
  \hline
@@
 
-\subsubsection{A comparision of Multinomial Naive Bayes to Logistic Regression with Extremely Sparse Feature Matrices}
+\subsubsection{A comparison of Multinomial Naive Bayes to Logistic Regression with Extremely Sparse Feature Matrices}
 \noindent
@@
 
-Logistic Lasso with a larger penalty $>2.0$ does not perform will with extremely sparse matricies. \\
+Logistic Lasso with a larger penalty (i.e., $>2.0$) does not perform well with extremely sparse matrices. \\
 \begin{center}
@@
 
- \multicolumn{5}{|c|}{Deterioration of Logistic Lasso with sparse matricies relative to Naive Bayes} \\
+ \multicolumn{5}{|c|}{Deterioration of Logistic Lasso with sparse matrices relative to Naive Bayes} \\
  \hline
@@
 \end{center}
+\vertSpace
+\noindent Below is a plot showing Naive Bayes giving consistent results relative
+to Logistic Lasso .
 
 \begin{figure}[h!]
-  \includegraphics[width=\linewidth]{../output/analysis/unstacked-nb-ll.JPG}
+  \centering
+  \includegraphics[width=100mm]{./ngramlen_nb_ll.pdf}
   \caption{F1 performance of LL and NB - Unstacked Model}
@@
 
+\subsubsection{Impact of N-gram sequences on results}
+We varied the N-gram sequences to observe its impact on our model predictions.
+Based on our empirical observations there is a definite range of N-gram sequences where all of the models greatly improve (based on F1 scores).
+All of the models showed great improvement when the N-gram sequences ranged between 4:6 and 10:15.
+As the sequences (N-grams) approached 20 words and larger, the results (model performance) started to deteriorate as the feature matrices became more sparse.
+Below is a graph of Logistic Lasso and Naive Bayes plotted with different regularization coefficients and varying N-gram sequence.
+\vertSpace
+
+The interesting part about our findings is that Federal Reserve commentary tends to have sequences of hawkish or dovish sentiment (FOMC action) which can't be expressed in a few words.
+This expression of hawkishness or dovishness in larger N-grams may be the reason why smaller B-gram sequences did not perform as well.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=100mm]{./ngram_seq.pdf}
+  \caption{N-gram sequence LL and NB - Stacked Model}
+\end{figure}
+\vfill
+
+\vertSpace
+
 \section{Conclusion}
-Reducing the sparsity of the matricies generated from CountVectorizer by stacking the documents greatly improved the results.  \vertSpace
+Reducing the sparsity of the matrices generated from CountVectorizer by stacking the documents greatly improved the results.  \vertSpace
 
 We were able to attain maximum test accuracy of $95.9\%$ using a $10:15$ n-gram, producing a recall of $93.4\%$ and an F1 score of $92.5\%$.
-Because of the large number (i.e., millions) of features in the feature matrix, Logistic Lasso with small penatly proved to be the most effective method for reducing the number of coefficients, leading to improved F1 scores.
+Because of the large number (i.e., millions) of features in the feature matrix, Logistic Lasso with small penalty proved to be the most effective method for reducing the number of coefficients, leading to improved F1 scores.
 \vertSpace
@@
 
-Overall our research found that Logistic Lasso with $\alpha = 0.002$ produced the most stable results for predicting FOMC rate decisions from FOMC statements, minutes, and Board of Governors speeches.
+Overall our research found that Logistic Lasso with smaller penalty $\alpha < 0.02$ produced the most stable results for predicting FOMC rate decisions from FOMC statements, minutes, and Board of Governors speeches.\vertSpace
+
+The limitation in this study is the size of the data sets.
+While we were able to identify characteristics that would help predictive power the strength of the conclusions are tempered by the amount of data on hand.
 
@@
 The Federal Funds Target Range is set by the FOMC.
-The Federal Funds Target Range is the range where the Federal Funds Effective rate (calculated as the volumn weighted median of eligible transactions reported on FR 2420) is exepected to fix on a daily basis.
-The Federal Funds rate is the primary monetary policy instrument of the Federal Reserve System, and it influces the level of interest rates domestically and globally.
+The Federal Funds Target Range is the range where the Federal Funds Effective rate (calculated as the volume weighted median of eligible transactions reported on FR 2420) is expected to fix on a daily basis.
+The Federal Funds rate is the primary monetary policy instrument of the Federal Reserve System, and it influences the level of interest rates domestically and globally.
 For example, if the Federal Funds effective rate were 5 percent, then the interest rate on a 30 year mortgage would be 5 percent or greater.
@@
  \hline
- Document Type& Years & Num Documents & Total Words & Avg Words Per Document & StDev\\
+ Document Type& Years & Number Documents & Total Words & Avg Words Per Document & StDev\\
  \hline
@@
 
-We explored latent topic modelling in our research to determine how a machine learning algorithm would classify $k=3$ topics, a proxy for the Federal Reserve's three objectives. \vertSpace
+We explored latent topic modeling in our research to determine how a machine learning algorithm would classify $k=3$ topics, a proxy for the Federal Reserve's three objectives. \vertSpace
 
@@
 
-\bibitem{Cd94} Hansen,Stephen, McMachon, Michael  \emph{Transparency and Deliberation with the FOMC:a Computational Linquistics Approach}, CEPR Discussion Paper, (2014)
+\bibitem{Cd94} Hansen,Stephen, McMachon, Michael  \emph{Transparency and Deliberation with the FOMC:a Computational Linguistics Approach}, CEPR Discussion Paper, (2014)
 
